### 2019-11-10 mstemc/index.tex
let's call it a day

% Intended LaTeX compiler: xelatex
\documentclass[koma,utopia,letterpaper,captions=tableheading,11pt,listings-sv,microtype,paralist,colorlinks=true,urlcolor=blue]{org-article}
\author{Eason}
\date{\today}
\title{my workflow of creating a video}
\hypersetup{
 pdfauthor={Eason},
 pdftitle={my workflow of creating a video},
 pdfkeywords={},
 pdfsubject={This collection of Videos and Posts describes my workflow of creating a video. Usage of some tools and methods are covered.},
 pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
 pdflang={English}}
\begin{document}

\maketitle
\tableofcontents

During the creation of one video, several tools are tuned to fit my workflow. In
this project several videos and posts will be created to make my workflow clear.

Two targets of this project:
\begin{enumerate}
\item remind me of the configuration of several tools;
\item show somebody else who may be interested in how I work.
\end{enumerate}

I am not ready to detail each tool. If you are interested in any one of them,
please refer to tutorials written by experts or given by the official document.

\section{Emacs}
\label{sec:org232de87}

Emacs lies in the center of my workflow. It behaves like a super-IDE which
assists me finish almost all the steps. Using Emacs, I program and debug, GTD,
write the blogs, export and publish them. Many of the Emacs extensions are
awesome. In particular, Emacs Org is the killer app.

How to config Emacs? After more Than ten years of using Emacs, I choose
spacemacs. Most beginners can start their work using spacemacs with only a
little modifications.

\subsection{program and debug}
\label{sec:orgcb33eca}

I program in python, C/C++, Matlab and some other languages. Emacs acts as a
super-IDE for me.

\subsection{Org mode - journalize your work}
\label{sec:orga18221f}

Org mode definitely need a standalone subsection.

\subsection{Org mode - get things done}
\label{sec:org8f6b45e}

\subsection{Org mode - write a diary}
\label{sec:orgd48d496}

\subsection{Org mode - export your Org file}
\label{sec:org94ce70b}

\subsection{program and debug}
\label{sec:org8c82502}

\subsection{writing latex}
\label{sec:org3f6fba5}
\subsection{org-journal}
\label{sec:org9e0dc38}

I write many notes during a post or a project. Most of my journal is maintained
by \href{https://github.com/bastibe/org-journal}{org-journal: A simple org-mode based journaling mode} . And I set the
\texttt{org-journal-file-type} to \texttt{weekly} So that I have around 52 journal file each
year.

The journals can be searched conveniently. Also they can be integrated into Org
agenda.

\subsection{ox-hugo}
\label{sec:orgeefa353}

\href{https://github.com/kaushalmodi/ox-hugo}{kaushalmodi/ox-hugo: A carefully crafted Org exporter back-end for Hugo}

Because hugo supports markdown at first (it also supports org file later), I use
Emacs Org from the very beginning. I am quite familiar with org-mode, so have no
motivation to dig into markdown. Fortunately, ox-hugo meets all my requirement
and definitely worth a try when you want to stay in Org.

Actually, Emacs have extensions to support markdown quite well. However, using
Org, I can integrate the org file into my agenda.

\section{Hugo}
\label{sec:org4e548ff}

As the fastest framework for building websites, Hugo shocks me by its speed and
flexibility. It is enough to prettify your site using the more than 300+
beautiful themes, from which I am in the mode for Academic theme.

Hugo supports Org file but not so good. Ox-hugo, another extension of Emacs, has
my attention. Serving as a bridge between Emacs and Hugo, ox-hugo helps me
staying in Emacs Org. There is no need for me to write markdown file if Org is
available.

I use ox-hugo as a bridge between Emacs and Hugo. So I do not have to care much
about how to leverage Hugo. Ox-hugo helps me do most of the work.

\section{manim}
\label{sec:org74b3895}

\section{blender}
\label{sec:orge510532}
\end{document}

### 2019-11-10 mstemc/mstemc.tex
let's call it a day

--- 2019-11-10 mstemc/index.tex
@@
 \documentclass[koma,utopia,letterpaper,captions=tableheading,11pt,listings-sv,microtype,paralist,colorlinks=true,urlcolor=blue]{org-article}
-\author{Eason}
+\author{Eason Zhang}
 \date{\today}
-\title{my workflow of creating a video}
+\title{make STEM clear}
 \hypersetup{
- pdfauthor={Eason},
- pdftitle={my workflow of creating a video},
+ pdfauthor={Eason Zhang},
+ pdftitle={make STEM clear},
  pdfkeywords={},
- pdfsubject={This collection of Videos and Posts describes my workflow of creating a video. Usage of some tools and methods are covered.},
+ pdfsubject={},
  pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
@@
 
+\section{Videos}
+\label{sec:org998bcda}
+
+\section{Posts}
+\label{sec:org3d17ce5}
+
+\section{Projects}
+\label{sec:orgc54445f}
+
+\subsection{my workflow of creating a video}
+\label{sec:orgf0ee6dd}
 During the creation of one video, several tools are tuned to fit my workflow. In
@@
 
-\section{Emacs}
-\label{sec:org232de87}
+\subsubsection{Emacs}
+\label{sec:org0c108f2}
 
@@
 
-\subsection{program and debug}
-\label{sec:orgcb33eca}
+\begin{enumerate}
+\item program and debug
+\label{sec:org1ff6423}
 
@@
 
-\subsection{Org mode - journalize your work}
-\label{sec:orga18221f}
+\item Org mode - journalize your work
+\label{sec:org12d2f61}
 
@@
 
-\subsection{Org mode - get things done}
-\label{sec:org8f6b45e}
+\item Org mode - get things done
+\label{sec:org5ad0d61}
 
-\subsection{Org mode - write a diary}
-\label{sec:orgd48d496}
+\item Org mode - write a diary
+\label{sec:org32d0506}
 
-\subsection{Org mode - export your Org file}
-\label{sec:org94ce70b}
+\item Org mode - export your Org file
+\label{sec:org4d11418}
 
-\subsection{program and debug}
-\label{sec:org8c82502}
+\item program and debug
+\label{sec:orgeef06a2}
 
-\subsection{writing latex}
-\label{sec:org3f6fba5}
-\subsection{org-journal}
-\label{sec:org9e0dc38}
+\item writing latex
+\label{sec:org9ac1f7a}
+\item org-journal
+\label{sec:orga432c48}
 
@@
 
-\subsection{ox-hugo}
-\label{sec:orgeefa353}
+\item ox-hugo
+\label{sec:orgf65906e}
 
@@
 Org, I can integrate the org file into my agenda.
+\end{enumerate}
 
-\section{Hugo}
-\label{sec:org4e548ff}
+\subsubsection{Hugo}
+\label{sec:orgc828f72}
 
@@
 
-\section{manim}
-\label{sec:org74b3895}
+\subsubsection{manim}
+\label{sec:orgea6a849}
 
-\section{blender}
-\label{sec:orge510532}
+\subsubsection{blender}
+\label{sec:orge06e6d2}
+
+\section{Courses}
+\label{sec:org7e36065}
 \end{document}

### 2019-11-25 Journal/20191118.tex
let's call it a day

% Intended LaTeX compiler: xelatex
\documentclass[koma,utopia,letterpaper,captions=tableheading,11pt,listings-sv,microtype,paralist,colorlinks=true,urlcolor=blue]{org-article}
\author{Eason}
\date{\today}
\title{20191119}
\hypersetup{
 pdfauthor={Eason},
 pdftitle={20191119},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
 pdflang={English}}
\begin{document}

\maketitle
\tableofcontents

\section{Tuesday, 11/19/19}
\label{sec:orgaf7c73e}
\subsection{21:55 this is a new week}
\label{sec:org784f7a1}
STEAM: science, technology, engineering, art and math

Today, I listen to an talk between 3blue1brown and numberphile.

\section{Wednesday, 11/20/19}
\label{sec:org7da6c22}

\section{Sunday, 11/24/19}
\label{sec:org9fb7c83}
\subsection{introduction to signal and system}
\label{sec:org4132682}
\subsubsection{preface}
\label{sec:org30a21fe}

While students studying signals and systems should certainly have a solid
foundation in disciplines based on the laws of physics, they must also have a
solid foundation in disciplines based on the laws of physics, they must also
have a firm grounding in the use of computers for the analysis of phenomena
and the implementation of systems and algorithms. As a consequence, engineering
curricula now reflect a blend of subjects, some involving continuous-time models
and others focusing on the use of computers and discrete representations. For
these reasons, signals and systems courses that bring discrete-time and
continuous-time concepts together in a unified way play an increasingly
important role in the education of engineering students and in their preparation
for current and future developments in their chosen fields.

It has pedagogical advantage by taking both the continuous-time and
discrete-time in mind.

Chapter 1 introduces block diagram representations of interconnections of
systems and discusses several basic system properties such as causality,
linearity and time-invariance.

The concepts of signals and systems arise in a wide variety of fields, and the
ideas and techniques associated with these concepts play an important role in
such diverse areas of science and technology such communications, aeronautics
and astronautics, circuit design, acoustics, seismology, biomedical engineering,
energy generation and distribution systems, chemical process control, and speech
processing. Because of its importance, it worth to take time to digest each
single idea and concept appearing in such course. Also, it will be greatly
helpful for the newbie to have an open course to help them dive into the world
of signals and systems. I tried my best to give the best explanation of the
concept in this course and comprehensive details are given during my creation of
videos and posts. It takes time to produce one piece of work so that sometimes I
think it was a grind. However, for the sake of beautiful result, I pretty enjoy
the process of doing such creation.

The signals, which are functions of one or more independent variables, contains
information about the behavior or nature of some phenomenon, whereas the systems
respond to particular signals by producing other signals or some desired
behavior.

Examples:
\begin{enumerate}
\item Voltages and currents as a function of time in an electrical circuit are
examples of signals. and a circuit is itself an example of a system, which in
this case responds to applied voltages and currents.
\item As another example, when an automobile driver depresses the accelerator
pedal, the automobile responds by increasing the speed of the vehicle.
\item A computer program for the automated diagnosis of electrocardiograms can be
viewed as a system which has as its input a digitized electrocardiogram and
which produces estimates of parameters such as heart rate as outputs.
\item A camera is a system that receives light from different sources and reflected
from objects and produces a photograph.
\item A robot arm is a system whose movements are the response to control inputs.
\end{enumerate}

The purpose of signals ans systems:
\begin{enumerate}
\item characterizing the system in detail to understand how it will respond to
various inputs.
\item design systems to process signals in particular ways. such enhancement and
restoration of certain signals, extraction of specific pieces of information
from signals.
\item modify or control the characteristics of a given system.
\end{enumerate}

\subsubsection{15:39 Basics of signals and systems}
\label{sec:orgf198687}

This section is from \href{http://www.di.univr.it/documenti/OccorrenzaIns/matdid/matdid744681.pdf}{Signals-and-Systems.ppt}  by Gloria Menegaz. The textbook
is : \emph{Signal Processing and Linear Systems} by B.P. Lathi, CRC Press.

\subsubsection{definition of signals and systems}
\label{sec:org9f44052}

A signal is defined as any physical quantity that varies with time, space, or
any other independent variable or variables. Mathematically, we describe a
signal as a function of one or more independent variables. Signals convey
information.

A continuous-time signal is a quantity of interest that
depends on an independent variable, where we usually think of the independent
variable as time. In the real world, physical quantities take on real numerical
values, though it turns out that sometimes it is mathematically convenient to
consider \emph{complex-valued functions of t}. However, the default is real-valued
\(x(t)\), and indeed the type of sketch exhibited about is valid only for
real-valued signals.

Remarks:
\begin{enumerate}
\item A continuous-time signal is not necessarily a continuous function as defined
in calculus. They are two different definition.
\item The independent variable need not to be time, it could has other meaning. But
considering it as time does not affect we study the concepts of signals and
systems.
\end{enumerate}

A discrete-time signal is a sequence of values of interest, where the integer
index can be thought of as a time index, and the values in the sequence
represent some physical quantity of interest. Because many discrete-time signals
arise as equally-spaced samples of a continuous-time signal, it is often more
convenient to think of the index as the "sample number".

Systems process signals to produce a modified or transformed version of the
original signal. For the information and communication technology, signals and
systems helps engineer to analyze and design the signals and systems they meet
in daily life.

\subsubsection{summary of chapter 1}
\label{sec:orgde426c3}

We developed a number of basic concepts related to continuous-time and
discrete-time signals and systems. We have presented both an intuitive picture
of what signals and systems are through several examples and a mathematical
representation for signals and systems that we will use throughout the book.
Specifically, we introduced graphical and mathematical representation of signals
and used these representations in performing transformations of the independent
variable. We also defined and examined several basic signals, both in continuous
time and in discrete time. These included complex exponential signals,
sinusoidal signals, and unit impulse and step functions. In addition, we
investigated the concept of periodicity for continuous-time and discrete-time
signals.

In developing some of the elementary ideas related to systems, we introduced
block diagrams to facilitate our discussions concerning the interconnection of
systems, and we defined a number of important properties of systems, including
causality, stability, time-invariance, and linearity.

The primary focus in most of this book will be on the class of LTI systems, both
in continuous time and discrete time. These systems play a particularly
important role in system analysis and design, in part due to the fact that many
systems encountered in nature can be successfully modeled as linear and time
invariant. Furthermore, as we shall see in the following chapters, the
properties of linearity and time invariance allows us to analyze in detail the
behavior of LTI systems.

\subsubsection{references}
\label{sec:orgbf8c476}

Other references are:
\begin{enumerate}
\item Signals and systems by Richard Baraniuk's lecture
notes.\href{https://web.itu.edu.tr/hulyayalcin/Signal\_Processing\_Books/2003\_Richard\_Baraniuk\_Signals\_and\_Systems.pdf}{2003\_Richard\_Baraniuk\_Signals\_and\_Systems.pdf}
\item Digital Signal Processing by John G. Proakis, Dimitris K Manolakis\href{https://engineering.purdue.edu/\~ee538/DSP\_Text\_3rdEdition.pdf}{Digital Signal Processing: Principles, Algorithms \& Applications}

\item Signal processing and linear systems, Schaun's outline of digital signal
processing.
\item Foundations of Signal Processing.\href{http://fourierandwavelets.org/}{Foundations of Signal Processing and Fourier
and Wavelet Signal Processing}

Together with Fourier and Wavelet Signal Processing (to be published by CUP),
the two books aim to present the essential principles in signal processing
along with mathematical tools and algorithms for signal representation. They
comprehensively cover both classical Fourier techniques and newer basis
constructions from filter banks and multiresolution analysis—wavelets.
Furthermore, they gives a synthetic view from basic mathematical principles,
to construction of bases, all the way to concrete applications.

\item Signal processing for communications, by Palo Prandoni and Martin
Vetterli. \href{https://www.sp4comm.org/index.html}{Signal Processing for Communications}

With a novel, less formal approach to the subject, the authors have written a
book with the conviction that signal processing should be taught to be fun.
The treatment is less focused on the mathematics and more on the conceptual
and practical aspects but the book remains an engineering text, with the goal
of helping students solve real-world problems. In this vein, the last chapter
pulls together all the topics discussed throughout the book into an in-depth
look at the development of an end-to-end communication system, namely, a
modem for communicating digital information over an analog channel.

\item Lecture notes of ELE 301 by \href{https://www.princeton.edu/\~cuff/}{Paul W. Cuff} . The\href{https://www.princeton.edu/\~cuff/ele301/files/lecture1\_2.pdf}{Lecture 1 ELE 301: Signals and
Systems}  process some basic of the signals and systems

\item Signal and system analysis by Jianping Yao\href{http://www.site.uottawa.ca/\~jpyao/courses/E3125B\_Fall\_2019.html}{ELG3120} .

\item Notes for signals and Systems by Wilson J. Rugh\href{https://pages.jh.edu/\~bcooper8/sigma\_files/courses/214/signalsandsystemsnotes.pdf}{Notes for Signals and Systems}
. And in the site\href{https://pages.jh.edu/\~signals/}{Signals, Systems, and Control Demonstrations} has some other
demos about signals and systems.

\item \href{https://ptolemy.berkeley.edu/books/leevaraiya/}{Lee and Varaiya, Structure and Interpretation of Signals and Systems}

Signals convey information. Systems transform signals. This book introduces
the mathematical models used to design and understand both. It is intended
for students interested in developing a deep understanding of how to
digitally create and manipulate signals to measure and control the physical
world and to enhance human experience and communication. This book is based
on several years of successful classroom use at the University of California,
Berkeley. The material starts with an early introduction to applications,
well before students have built up enough theory to fully analyze the
applications. This motivates students to learn the theory and allows students
to master signals and systems at the sophomore level. The material motivates
signals and systems through sound and images. Calculus is the only
prerequisite.

 And the PDF version of the book is \href{https://ptolemy.berkeley.edu/books/leevaraiya/releases/LeeVaraiya\_DigitalV2\_04.pdf}{here}. There is also \href{https://ptolemy.berkeley.edu/books/leevaraiya/releases/LabManualV1\_AddisonWesley.pdf}{an accompanied
laboratory} manual using matlab.

\item Gurdal Arslan has several \href{http://www2.hawaii.edu/\~gurdal/index\_files/Page386.htm}{Courses} about signals and systems.

\item \href{http://www.eas.uccs.edu/\~mwickert/ece2610/}{ECE2610 Introduction to Signals and Systems}

Mathematical representation of signals and systems; spectrum representation;
representation of signals by sample values; discrete-time filter
characterization and response; the z-transform; continuous-time signals and
linear, time-invariant systems; frequency response; continuous-time Fourier
transform and application to signals and systems. Include lectures,
demonstrations, and laboratory assignments.

\item Dr Wickert's website \href{http://www.eas.uccs.edu/\~mwickert/}{Dr. Wickert's Info Center}  has quite a lot resources
for a engineering student.
\end{enumerate}
\end{document}

### 2019-11-26 Journal/20191118.tex
add the section of definition of signals and systems
also, the examples sections are added

@@
 \date{\today}
-\title{20191119}
+\title{introduction to signal and system}
 \hypersetup{
  pdfauthor={Eason},
- pdftitle={20191119},
+ pdftitle={introduction to signal and system},
  pdfkeywords={},
@@
 
-\section{Tuesday, 11/19/19}
-\label{sec:orgaf7c73e}
-\subsection{21:55 this is a new week}
-\label{sec:org784f7a1}
-STEAM: science, technology, engineering, art and math
-
-Today, I listen to an talk between 3blue1brown and numberphile.
-
-\section{Wednesday, 11/20/19}
-\label{sec:org7da6c22}
-
-\section{Sunday, 11/24/19}
-\label{sec:org9fb7c83}
-\subsection{introduction to signal and system}
-\label{sec:org4132682}
-\subsubsection{preface}
-\label{sec:org30a21fe}
+\section{preface}
+\label{sec:orgb73e917}
 
@@
 
-\subsubsection{15:39 Basics of signals and systems}
-\label{sec:orgf198687}
+\section{15:39 Basics of signals and systems}
+\label{sec:org023432e}
 
@@
 
-\subsubsection{definition of signals and systems}
-\label{sec:org9f44052}
+\section{definition of signals and systems}
+\label{sec:org0083078}
+
+Fist give the definition of singal then system.
+\subsection{definition of signals}
+\label{sec:orgc5b8c56}
 
@@
 
-A continuous-time signal is a quantity of interest that
-depends on an independent variable, where we usually think of the independent
-variable as time. In the real world, physical quantities take on real numerical
-values, though it turns out that sometimes it is mathematically convenient to
-consider \emph{complex-valued functions of t}. However, the default is real-valued
-\(x(t)\), and indeed the type of sketch exhibited about is valid only for
-real-valued signals.
+A continuous-time signal is a quantity of interest that depends on an
+independent variable, where we usually think of the independent variable as
+time. In the real world, physical quantities take on real numerical values,
+though it turns out that sometimes it is mathematically convenient to consider
+\emph{complex-valued functions of t}. However, the default is real-valued \(x(t)\),
+and indeed the type of sketch exhibited about is valid only for real-valued
+signals.
 
@@
 convenient to think of the index as the "sample number".
+\subsection{examples of signals}
+\label{sec:org9e7ff00}
+
+\subsubsection{ECG signal}
+\label{sec:org6aa518f}
+
+\subsubsection{Speech signal}
+\label{sec:org4599249}
+
+\subsubsection{Image}
+\label{sec:orgb9ba77a}
+
+\subsection{definition of systems}
+\label{sec:org50a98a3}
 
 Systems process signals to produce a modified or transformed version of the
-original signal. For the information and communication technology, signals and
-systems helps engineer to analyze and design the signals and systems they meet
-in daily life.
+original signal. For the information and communication technology, this series
+of videos and posts help engineers analyze and design the signals and systems
+they meet in daily life.
 
-\subsubsection{summary of chapter 1}
-\label{sec:orgde426c3}
+In general, two types of tools related with continuous-time signals and
+discrete-time signals will be covered. For example, for the continuous-time
+signals we have Fourier Transform and Laplace transform whereas for the
+discrete-time signals we have discrete time Fourier Transforms and Z-transform.
+Living in a digitized world, I use discrete-time signals related tools more
+often than the continuous-time counterpart. Now, it seems that the
+continuous-time signals only exists before analog-digital converter (ADC).
+However, to analyze a signal, the continuous-time related tools provide a more
+mathematical and theoretical way. So during the learning and teaching signals
+and systems, I will cover both continuous-time and discrete-time topics and give
+as many details about both realms as I can. Fortunately, we have sampling theory
+and ADC, we can easily move from continuous-time world to discrete-time world .
+Most of the conclusions we draw from the continuous-time world will apply in the
+discrete-time world with no or only a little modification.
+\subsection{examples of systems}
+\label{sec:org371aacc}
+
+\subsubsection{ECG system}
+\label{sec:orge20180e}
+
+\subsubsection{Voice recording system}
+\label{sec:org4bc4f48}
+
+\subsubsection{Camera Systems}
+\label{sec:org36b0296}
+
+\section{summary of chapter 1}
+\label{sec:org273cc92}
 
@@
 
-\subsubsection{references}
-\label{sec:orgbf8c476}
+\section{references}
+\label{sec:orgc602a8b}
 
@@
 \end{enumerate}
+\section{architecture of each video}
+\label{sec:org64de00f}
+
+\begin{enumerate}
+\item every video will contain several topics but the mathematical derivation will
+not be so all-inclusive. More details will given as posts in this site for whom
+may be interested. So you can grab the overall structure at first then
+reinforce the it with more bricks.
+\item For each video, only several key points will be explained. I don't want the
+video make you feel boring or tired.
+\item A piece of suggestion for the serious learner: watch the video twice or even
+more. Most often, even some concepts which are relatively simple at first
+look hide some deep relation with other concepts. The obscure relation will
+not be illustrated in the video if it does not affect the understanding of
+current object.
+\end{enumerate}
 \end{document}

### 2019-12-01 Journal/20191125.tex
let's call it a day

--- 2019-11-26 Journal/20191118.tex
@@
 
-\section{preface}
-\label{sec:orgb73e917}
+\section{Wednesday, 11/27/19}
+\label{sec:org7ec480d}
+\subsection{19:20 academic theme}
+\label{sec:orgc626325}
+\subsection{use power thesaurus.el}
+\label{sec:orgd065b2d}
+
+\href{https://github.com/SavchenkoValeriy/emacs-powerthesaurus}{SavchenkoValeriy/emacs-powerthesaurus: Powerthesaurus integration for Emacs}
+
+Emacs-powerthesaurus is a simple plugin to integrate Emacs with amazing
+powerthesaurus.org
+
+\section{Saturday, 11/30/19}
+\label{sec:org5c14c91}
+
+\section{Sunday, 12/01/19}
+\label{sec:org4ace420}
+\subsection{introduction to signal and system}
+\label{sec:orgabba3dd}
+\subsubsection{preface}
+\label{sec:org8b47609}
 
@@
 
-\section{15:39 Basics of signals and systems}
-\label{sec:org023432e}
+\subsubsection{15:39 Basics of signals and systems}
+\label{sec:org42860fe}
 
@@
 
-\section{definition of signals and systems}
-\label{sec:org0083078}
+\subsubsection{definition of signals and systems}
+\label{sec:org785eae1}
 
-Fist give the definition of singal then system.
-\subsection{definition of signals}
-\label{sec:orgc5b8c56}
+Fist give the definition of singal than system.
+\begin{enumerate}
+\item definition of signals
+\label{sec:org9e28d14}
 
@@
 convenient to think of the index as the "sample number".
-\subsection{examples of signals}
-\label{sec:org9e7ff00}
+\item examples of signals
+\label{sec:orge975172}
 
-\subsubsection{ECG signal}
-\label{sec:org6aa518f}
+\begin{enumerate}
+\item ECG signal
+\label{sec:orgc8f647d}
 
-\subsubsection{Speech signal}
-\label{sec:org4599249}
+\item Speech signal
+\label{sec:org934f365}
 
-\subsubsection{Image}
-\label{sec:orgb9ba77a}
+\item Image
+\label{sec:org28628c9}
+\end{enumerate}
 
-\subsection{definition of systems}
-\label{sec:org50a98a3}
+\item definition of systems
+\label{sec:orgce71be0}
 
@@
 discrete-time world with no or only a little modification.
-\subsection{examples of systems}
-\label{sec:org371aacc}
+\item examples of systems
+\label{sec:org4f5abb0}
 
-\subsubsection{ECG system}
-\label{sec:orge20180e}
+\begin{enumerate}
+\item ECG system
+\label{sec:org705072e}
 
-\subsubsection{Voice recording system}
-\label{sec:org4bc4f48}
+\item Voice recording system
+\label{sec:orga139225}
 
-\subsubsection{Camera Systems}
-\label{sec:org36b0296}
+\item Camera Systems
+\label{sec:org0ec4a51}
+\end{enumerate}
+\end{enumerate}
 
-\section{summary of chapter 1}
-\label{sec:org273cc92}
+\subsubsection{summary of chapter 1}
+\label{sec:org9c0f4d4}
 
@@
 
-\section{references}
-\label{sec:orgc602a8b}
+\subsubsection{references}
+\label{sec:org63c4515}
 
@@
 \end{enumerate}
-\section{architecture of each video}
-\label{sec:org64de00f}
+\subsubsection{architecture of each video}
+\label{sec:org29e6fbc}
 
@@
 \end{enumerate}
+
+\subsection{08:05 introduction to signal and system (ver2)}
+\label{sec:org0a474bf}
+
+As a basic "language" for engineering students, signals and systems appears in a
+variety of fields which can be communications, aeronautics and astronautics,
+circuit design, acoustics, seismology, biomedical engineering, energy generation
+and distribution systems, chemical process control, and speech processing. The
+tools developed in this course will play an important role in the future for
+engineering students.
+
+Before we give some official definitions of signals and systems, let's dive into
+some examples.
+\begin{center}
+\includegraphics[width=0.6\textwidth]{../../img/icon-512.png}
+\end{center}
 \end{document}

### 2019-12-01 mstemc/mstemc.tex
let's call it a day

@@
 % Intended LaTeX compiler: xelatex
-\documentclass[koma,utopia,letterpaper,captions=tableheading,11pt,listings-sv,microtype,paralist,colorlinks=true,urlcolor=blue]{org-article}
+\documentclass[koma,letterpaper,captions=tableheading,ctex,11pt,listings-sv,microtype,paralist,colorlinks=true,urlcolor=blue]{org-article}
+                  \usepackage{ctex}
+                  \usepackage{tikztheorem}
 \author{Eason Zhang}
 \date{\today}
-\title{make STEM clear}
+\title{make STEAM clear}
 \hypersetup{
  pdfauthor={Eason Zhang},
- pdftitle={make STEM clear},
+ pdftitle={make STEAM clear},
  pdfkeywords={},
@@
 \section{Videos}
-\label{sec:org998bcda}
+\label{sec:orgc58e4f7}
 
 \section{Posts}
-\label{sec:org3d17ce5}
+\label{sec:orgb1332b6}
 
 \section{Projects}
-\label{sec:orgc54445f}
+\label{sec:orgffac4f6}
 
 \subsection{my workflow of creating a video}
-\label{sec:orgf0ee6dd}
+\label{sec:orgb86eaa9}
+ 中文 你好
 During the creation of one video, several tools are tuned to fit my workflow. In
@@
 \subsubsection{Emacs}
-\label{sec:org0c108f2}
+\label{sec:orgadf0dac}
 
@@
 \item program and debug
-\label{sec:org1ff6423}
+\label{sec:org954f607}
 
@@
 \item Org mode - journalize your work
-\label{sec:org12d2f61}
+\label{sec:org0cf6dc5}
 
@@
 \item Org mode - get things done
-\label{sec:org5ad0d61}
+\label{sec:orgd228748}
 
 \item Org mode - write a diary
-\label{sec:org32d0506}
+\label{sec:orgd304635}
 
 \item Org mode - export your Org file
-\label{sec:org4d11418}
+\label{sec:orgf2a7087}
 
 \item program and debug
-\label{sec:orgeef06a2}
+\label{sec:org81e3cf7}
 
 \item writing latex
-\label{sec:org9ac1f7a}
+\label{sec:orgb6b215c}
 \item org-journal
-\label{sec:orga432c48}
+\label{sec:org7fba657}
 
@@
 \item ox-hugo
-\label{sec:orgf65906e}
+\label{sec:org5bd6c0b}
 
@@
 \subsubsection{Hugo}
-\label{sec:orgc828f72}
+\label{sec:org142d742}
 
@@
 \subsubsection{manim}
-\label{sec:orgea6a849}
+\label{sec:orga5a3f16}
 
 \subsubsection{blender}
-\label{sec:orge06e6d2}
+\label{sec:org41eda2c}
 
 \section{Courses}
-\label{sec:org7e36065}
+\label{sec:org7835e17}
 \end{document}

### 2019-12-04 mstemc/mstemc.tex
trivial modification

--- 2019-11-10 mstemc/mstemc.tex
@@
 \documentclass[koma,utopia,letterpaper,captions=tableheading,11pt,listings-sv,microtype,paralist,colorlinks=true,urlcolor=blue]{org-article}
-\author{Eason Zhang}
+               \usepackage{tikz}
+\author{Eason}
 \date{\today}
-\title{make STEM clear}
+\title{make STEAM clear}
 \hypersetup{
- pdfauthor={Eason Zhang},
- pdftitle={make STEM clear},
+ pdfauthor={Eason},
+ pdftitle={make STEAM clear},
  pdfkeywords={},
@@
 \section{Videos}
-\label{sec:org998bcda}
+\label{sec:orgd3ae832}
 
 \section{Posts}
-\label{sec:org3d17ce5}
+\label{sec:org7648261}
 
 \section{Projects}
-\label{sec:orgc54445f}
+\label{sec:orgec1d3eb}
 
 \subsection{my workflow of creating a video}
-\label{sec:orgf0ee6dd}
+\label{sec:org3bbb651}
 During the creation of one video, several tools are tuned to fit my workflow. In
@@
 \subsubsection{Emacs}
-\label{sec:org0c108f2}
+\label{sec:org42d9799}
 
@@
 \item program and debug
-\label{sec:org1ff6423}
+\label{sec:orgb2fe87f}
 
@@
 \item Org mode - journalize your work
-\label{sec:org12d2f61}
+\label{sec:orgeea2f15}
 
@@
 \item Org mode - get things done
-\label{sec:org5ad0d61}
+\label{sec:orgc04d679}
 
 \item Org mode - write a diary
-\label{sec:org32d0506}
+\label{sec:orgfef1783}
 
 \item Org mode - export your Org file
-\label{sec:org4d11418}
+\label{sec:org4bcf25c}
 
 \item program and debug
-\label{sec:orgeef06a2}
+\label{sec:org1802ebb}
 
 \item writing latex
-\label{sec:org9ac1f7a}
+\label{sec:orgbcbd545}
 \item org-journal
-\label{sec:orga432c48}
+\label{sec:orgef55573}
 
@@
 \item ox-hugo
-\label{sec:orgf65906e}
+\label{sec:org5381774}
 
@@
 Org, I can integrate the org file into my agenda.
+
+\item preview tikz picture in Org
+\label{sec:org9189e37}
+
+A minimum working example is shown as below
 \end{enumerate}
@@
 \subsubsection{Hugo}
-\label{sec:orgc828f72}
+\label{sec:org02f26a1}
 
@@
 \subsubsection{manim}
-\label{sec:orgea6a849}
+\label{sec:orge522a09}
 
 \subsubsection{blender}
-\label{sec:orge06e6d2}
+\label{sec:orgcd33ab5}
 
 \section{Courses}
-\label{sec:org7e36065}
+\label{sec:orgcd12774}
 \end{document}

### 2019-12-04 mstemc/mstemc.tex
modify 20191202

@@
 \section{Videos}
-\label{sec:orgd3ae832}
+\label{sec:orgfaf9643}
 
 \section{Posts}
-\label{sec:org7648261}
+\label{sec:org8bd76bc}
 
 \section{Projects}
-\label{sec:orgec1d3eb}
+\label{sec:org9f3dc59}
 
 \subsection{my workflow of creating a video}
-\label{sec:org3bbb651}
+\label{sec:org0f22a5a}
 During the creation of one video, several tools are tuned to fit my workflow. In
@@
 \subsubsection{Emacs}
-\label{sec:org42d9799}
+\label{sec:orge0a91d3}
 
@@
 \item program and debug
-\label{sec:orgb2fe87f}
+\label{sec:orgb4f0839}
 
@@
 \item Org mode - journalize your work
-\label{sec:orgeea2f15}
+\label{sec:org106db98}
 
@@
 \item Org mode - get things done
-\label{sec:orgc04d679}
+\label{sec:org39b4c74}
 
 \item Org mode - write a diary
-\label{sec:orgfef1783}
+\label{sec:org82f34e2}
 
 \item Org mode - export your Org file
-\label{sec:org4bcf25c}
+\label{sec:org060ee3f}
 
 \item program and debug
-\label{sec:org1802ebb}
+\label{sec:orgb408704}
 
 \item writing latex
-\label{sec:orgbcbd545}
+\label{sec:org821d574}
 \item org-journal
-\label{sec:orgef55573}
+\label{sec:org17da77b}
 
@@
 \item ox-hugo
-\label{sec:org5381774}
+\label{sec:orgc0903f5}
 
@@
 \item preview tikz picture in Org
-\label{sec:org9189e37}
+\label{sec:org0703751}
 
 A minimum working example is shown as below
+\begin{center}
+\includegraphics[width=.9\linewidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/tutorial.png}
+\end{center}
 \end{enumerate}
@@
 \subsubsection{Hugo}
-\label{sec:org02f26a1}
+\label{sec:org79ed269}
 
@@
 \subsubsection{manim}
-\label{sec:orge522a09}
+\label{sec:org6ba75eb}
 
 \subsubsection{blender}
-\label{sec:orgcd33ab5}
+\label{sec:org546be21}
 
 \section{Courses}
-\label{sec:orgcd12774}
+\label{sec:orgf7e6e3a}
 \end{document}

### 2019-12-05 mstemc/index.tex
add post:set-up-the-tikz-in-emacs-org-mode.org

@@
 % Intended LaTeX compiler: xelatex
-\documentclass[koma,utopia,letterpaper,captions=tableheading,11pt,listings-sv,microtype,paralist,colorlinks=true,urlcolor=blue]{org-article}
+\documentclass[koma,a4paper,utopia,10pt,listings-color,microtype,paralist,colorlinks]{org-article}
+               \usepackage{tikz}
 \author{Eason}
 \date{\today}
-\title{my workflow of creating a video}
+\title{Set up the TikZ in Emacs Org Mode}
 \hypersetup{
  pdfauthor={Eason},
- pdftitle={my workflow of creating a video},
+ pdftitle={Set up the TikZ in Emacs Org Mode},
  pdfkeywords={},
- pdfsubject={This collection of Videos and Posts describes my workflow of creating a video. Usage of some tools and methods are covered.},
+ pdfsubject={},
  pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
@@
 
-During the creation of one video, several tools are tuned to fit my workflow. In
-this project several videos and posts will be created to make my workflow clear.
+\begin{description}
+An introduction on how to setup the TikZ environment in Emacs Org Mode.So that
+in Org file, you can generate either vector graph of \texttt{pdf} format or raster
+graph of \texttt{png} format. Furthermore, you can export the vector graph when latex
+is called and otherwise raster graph.
+\end{description}
 
-Two targets of this project:
-\begin{enumerate}
-\item remind me of the configuration of several tools;
-\item show somebody else who may be interested in how I work.
-\end{enumerate}
+\section{config the header args}
+\label{sec:orgd6868d4}
 
-I am not ready to detail each tool. If you are interested in any one of them,
-please refer to tutorials written by experts or given by the official document.
+You can embed TiKz (One of \(\LaTeX\) graphic package) code into a Org file. With
+org-babel, you can generate ,insert and export the figure generated from Tikz
+package. At first, you need set up the environment. \href{https://orgmode.org/worg/org-contrib/babel/languages/ob-doc-LaTeX.html}{This Post} serves as a good
+introduction for beginners. Following it you may have a minimum working example
+like below:
 
-\section{Emacs}
-\label{sec:org232de87}
+\begin{verbatim}
+#+name: tutorial
+#+header: :file "~/Dropbox/mstemc_hugo/static/img/tikz/tutorial.png"
+#+header: :results raw :exports none :fit yes :border 0cm
+#+header: :imagemagick t :iminoptions -density 400 :imoutoptions -geometry 400 -flatten
+#+header: :headers '("\\usepackage{tikz} \\usetikzlibrary{positioning, shapes.symbols, calc}")
+#+begin_src latex
+  \begin{tikzpicture}
+    \node [circle, draw, fill=red!20] at (0,0) {1}
+    child { node [circle, draw, fill=blue!30] {2}
+      child { node [circle, draw, fill=green!30] {3} }
+      child { node [circle, draw, fill=yellow!30] {4} }};
+  \end{tikzpicture}
+#+end_src
+#+RESULTS: tutorial
+[[file:../../img/tikz/tutorial.png]]
+\end{verbatim}
 
-Emacs lies in the center of my workflow. It behaves like a super-IDE which
-assists me finish almost all the steps. Using Emacs, I program and debug, GTD,
-write the blogs, export and publish them. Many of the Emacs extensions are
-awesome. In particular, Emacs Org is the killer app.
+The example begins with several lines containing \texttt{\#+header} which is sort of
+clutter. we can put them in a file and include it at the beginning of the Org
+file.
+\section{generate results with different formats}
+\label{sec:org102d2b4}
 
-How to config Emacs? After more Than ten years of using Emacs, I choose
-spacemacs. Most beginners can start their work using spacemacs with only a
-little modifications.
+By changing the extension of \texttt{:file} (which is \texttt{pdf} for
+\texttt{"../../img/tikz/tutorial.pdf"} ), we can generate results with different formats.
+Now, I need \texttt{pdf} and \texttt{png} . You can see the result by just press \texttt{C-c C-c} in the
+body of the tikz code.
+\section{export the results according to the backend}
+\label{sec:org6c2af32}
 
-\subsection{program and debug}
-\label{sec:orgcb33eca}
+You can set \texttt{:exports} to control how the results will be exported. Now I set it
+as \texttt{none} which means the result will not be exported to latex or other format. I
+want to set more options of the exports. So I use:
 
-I program in python, C/C++, Matlab and some other languages. Emacs acts as a
-super-IDE for me.
+\begin{verbatim}
+#+ATTR_HTML:  :width 800 :align center
+#+ATTR_LATEX: :width 0.8\textwidth :align center
+{{{if-latex(tutorial.pdf,tutorial.png)}}}
+\end{verbatim}
 
-\subsection{Org mode - journalize your work}
-\label{sec:orga18221f}
+\texttt{if-latex} is a Org MACRO whose definition is :
+\begin{verbatim}
+#+MACRO: if-latex (eval (if (org-export-derived-backend-p org-export-current-backend 'latex)
+ (concat "[[file:../../img/tikz/"  $1 "]]")
+ (concat "[[file:../../img/tikz/"  $2 "]]") ))
+\end{verbatim}
 
-Org mode definitely need a standalone subsection.
+The \texttt{if-latex} MACRO let you export different formats by the backend. If the
+backend is \texttt{latex} then, \texttt{pdf} format figure will be exported. Otherwise, \texttt{png} format
+figure. Eventually, in the final \texttt{pdf} document, you figure can be zoomed in or
+out without losing any resolution.
 
-\subsection{Org mode - get things done}
-\label{sec:org8f6b45e}
+\section{the final workflow}
+\label{sec:org7d290e8}
 
-\subsection{Org mode - write a diary}
-\label{sec:orgd48d496}
+The minimum working example at the start of this post is simplifed as below.
 
-\subsection{Org mode - export your Org file}
-\label{sec:org94ce70b}
+\begin{verbatim}
+#+header: :file  "../../img/tikz/tutorial.pdf"
+#+begin_src latex
+  \begin{tikzpicture}
+    \node [circle, draw, fill=red!20] at (0,0) {1}
+    child { node [circle, draw, fill=blue!30] {2}
+      child { node [circle, draw, fill=green!30] {3} }
+      child { node [circle, draw, fill=yellow!30] {4} }};
+  \end{tikzpicture}
+#+end_src
 
-\subsection{program and debug}
-\label{sec:org8c82502}
+#+RESULTS:
+[[file:../../img/tikz/tutorial.png]]
 
-\subsection{writing latex}
-\label{sec:org3f6fba5}
-\subsection{org-journal}
-\label{sec:org9e0dc38}
+The following is the generated figure.
+#+ATTR_HTML:  :width 800 :align center
+#+ATTR_LATEX: :width 0.8\textwidth :align center
+{{{if-latex(tutorial.pdf,tutorial.png)}}}
+\end{verbatim}
 
-I write many notes during a post or a project. Most of my journal is maintained
-by \href{https://github.com/bastibe/org-journal}{org-journal: A simple org-mode based journaling mode} . And I set the
-\texttt{org-journal-file-type} to \texttt{weekly} So that I have around 52 journal file each
-year.
+Many settings are grouped into a setup file which is included at the top of this
+post:
+\begin{verbatim}
+#+SETUPFILE: ~/.spacemacs.d/org-templates/math-en.org
+\end{verbatim}
 
-The journals can be searched conveniently. Also they can be integrated into Org
-agenda.
-
-\subsection{ox-hugo}
-\label{sec:orgeefa353}
-
-\href{https://github.com/kaushalmodi/ox-hugo}{kaushalmodi/ox-hugo: A carefully crafted Org exporter back-end for Hugo}
-
-Because hugo supports markdown at first (it also supports org file later), I use
-Emacs Org from the very beginning. I am quite familiar with org-mode, so have no
-motivation to dig into markdown. Fortunately, ox-hugo meets all my requirement
-and definitely worth a try when you want to stay in Org.
-
-Actually, Emacs have extensions to support markdown quite well. However, using
-Org, I can integrate the org file into my agenda.
-
-\section{Hugo}
-\label{sec:org4e548ff}
-
-As the fastest framework for building websites, Hugo shocks me by its speed and
-flexibility. It is enough to prettify your site using the more than 300+
-beautiful themes, from which I am in the mode for Academic theme.
-
-Hugo supports Org file but not so good. Ox-hugo, another extension of Emacs, has
-my attention. Serving as a bridge between Emacs and Hugo, ox-hugo helps me
-staying in Emacs Org. There is no need for me to write markdown file if Org is
-available.
-
-I use ox-hugo as a bridge between Emacs and Hugo. So I do not have to care much
-about how to leverage Hugo. Ox-hugo helps me do most of the work.
-
-\section{manim}
-\label{sec:org74b3895}
-
-\section{blender}
-\label{sec:orge510532}
+Now, If you set the extension of the target file in the first line either \texttt{pdf} or
+\texttt{png} , a corresponding \texttt{pdf} or \texttt{png} figure will be generated. If execute \texttt{M-x
+org-toggle-inline-images}  , you can preview the result. If export the org-file
+as latex file then the \texttt{pdf} file, the image of \texttt{pdf} format will be inserted. If
+export to other format, \texttt{png} image will be used.
 \end{document}

### 2019-12-05 mstemc/mstemc.tex
add post:set-up-the-tikz-in-emacs-org-mode.org

--- 2019-12-04 mstemc/mstemc.tex
@@
 % Intended LaTeX compiler: xelatex
-\documentclass[koma,utopia,letterpaper,captions=tableheading,11pt,listings-sv,microtype,paralist,colorlinks=true,urlcolor=blue]{org-article}
+\documentclass[koma,a4paper,utopia,10pt,listings-color,microtype,paralist,colorlinks]{org-article}
                \usepackage{tikz}
@@
 \section{Videos}
-\label{sec:orgd3ae832}
+\label{sec:org23819b1}
 
 \section{Posts}
-\label{sec:org7648261}
+\label{sec:orgb1ab608}
 
 \section{Projects}
-\label{sec:orgec1d3eb}
+\label{sec:orge8d1fc9}
 
 \subsection{my workflow of creating a video}
-\label{sec:org3bbb651}
+\label{sec:org8223223}
 During the creation of one video, several tools are tuned to fit my workflow. In
@@
 \subsubsection{Emacs}
-\label{sec:org42d9799}
+\label{sec:orgc041d09}
 
@@
 \item program and debug
-\label{sec:orgb2fe87f}
+\label{sec:orgafa531d}
 
@@
 \item Org mode - journalize your work
-\label{sec:orgeea2f15}
+\label{sec:orge1afdea}
 
@@
 \item Org mode - get things done
-\label{sec:orgc04d679}
+\label{sec:org11a73ef}
 
 \item Org mode - write a diary
-\label{sec:orgfef1783}
+\label{sec:org58bfcb8}
 
 \item Org mode - export your Org file
-\label{sec:org4bcf25c}
+\label{sec:org4cc5d5b}
 
 \item program and debug
-\label{sec:org1802ebb}
+\label{sec:org0a78023}
 
 \item writing latex
-\label{sec:orgbcbd545}
+\label{sec:orgdcebfa5}
 \item org-journal
-\label{sec:orgef55573}
+\label{sec:orgdb006ce}
 
@@
 \item ox-hugo
-\label{sec:org5381774}
+\label{sec:orgefe2fb2}
 
@@
 \item preview tikz picture in Org
-\label{sec:org9189e37}
+\label{sec:org9816573}
 
-A minimum working example is shown as below
+\href{http://www.texample.net/tikz/}{TikZ and PGF} are \TeX{} packages for creating graphics programmatically. TikZ is
+build on top of PGF and allows you to create sophisticated graphics in a rather
+intuitive and easy manner.
+
+You can integrated TikZ code into the Org mode as a source block.A minimum
+working example is shown as below.
+
+[[file:~/Dropbox/mstemc_hugo/static/img/tikz/tutorial.png]]
+
+\begin{center}
+\includegraphics[width=0.4\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/tutorial.pdf}
+\end{center}
 \end{enumerate}
@@
 \subsubsection{Hugo}
-\label{sec:org02f26a1}
+\label{sec:org65579c9}
 
@@
 \subsubsection{manim}
-\label{sec:orge522a09}
+\label{sec:orgbb047b1}
 
 \subsubsection{blender}
-\label{sec:orgcd33ab5}
+\label{sec:orge8838d0}
 
 \section{Courses}
-\label{sec:orgcd12774}
+\label{sec:orgfc25921}
 \end{document}

### 2019-12-06 mstemc/index.tex
trivial modify the mstemc

@@
 \date{\today}
-\title{Set up the TikZ in Emacs Org Mode}
+\title{Set up the TikZ in Emacs Org File}
 \hypersetup{
  pdfauthor={Eason},
- pdftitle={Set up the TikZ in Emacs Org Mode},
+ pdftitle={Set up the TikZ in Emacs Org File},
  pdfkeywords={},
- pdfsubject={},
+ pdfsubject={An introduction to setup the TikZ environment in Emacs Org File.So that in Org file, you can generate either vector graph of \texttt{pdf}  format or raster graph of \texttt{png} format.
+Furthermore, you can export the vector graph when latex is called and otherwise raster graph.},
  pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
@@
 
-\begin{description}
-An introduction on how to setup the TikZ environment in Emacs Org Mode.So that
-in Org file, you can generate either vector graph of \texttt{pdf} format or raster
-graph of \texttt{png} format. Furthermore, you can export the vector graph when latex
-is called and otherwise raster graph.
-\end{description}
+\hspace{0pt}\\
+
+An introduction to setup the TikZ environment in Emacs Org File.So that in Org file, you can generate either vector graph of \texttt{pdf}  format or raster graph of \texttt{png} format.
+Furthermore, you can export the vector graph when latex is called and otherwise raster graph.
 
 \section{config the header args}
-\label{sec:orgd6868d4}
+\label{sec:org1e65b28}
 
@@
 \section{generate results with different formats}
-\label{sec:org102d2b4}
+\label{sec:org92aa971}
 
@@
 \section{export the results according to the backend}
-\label{sec:org6c2af32}
+\label{sec:org8166ca3}
 
@@
 \section{the final workflow}
-\label{sec:org7d290e8}
+\label{sec:org6fc731d}
 

### 2019-12-06 mstemc/mstemc.tex
trivial modify the mstemc

@@
 \section{Videos}
-\label{sec:org23819b1}
+\label{sec:org002a437}
 
 \section{Posts}
-\label{sec:orgb1ab608}
+\label{sec:org2d95323}
+
+\subsection{Set up the TikZ in Emacs Org File}
+\label{sec:org64c90ff}
+\begin{summary}
+Why is this in \textbf{green}?
+\end{summary}
+
+\subsubsection{config the header args}
+\label{sec:org825d7de}
+
+You can embed TiKz (One of \(\LaTeX\) graphic package) code into a Org file. With
+org-babel, you can generate ,insert and export the figure generated from Tikz
+package. At first, you need set up the environment. \href{https://orgmode.org/worg/org-contrib/babel/languages/ob-doc-LaTeX.html}{This Post} serves as a good
+introduction for beginners. Following it you may have a minimum working example
+like below:
+
+\begin{verbatim}
+#+name: tutorial
+#+header: :file "~/Dropbox/mstemc_hugo/static/img/tikz/tutorial.png"
+#+header: :results raw :exports none :fit yes :border 0cm
+#+header: :imagemagick t :iminoptions -density 400 :imoutoptions -geometry 400 -flatten
+#+header: :headers '("\\usepackage{tikz} \\usetikzlibrary{positioning, shapes.symbols, calc}")
+#+begin_src latex
+  \begin{tikzpicture}
+    \node [circle, draw, fill=red!20] at (0,0) {1}
+    child { node [circle, draw, fill=blue!30] {2}
+      child { node [circle, draw, fill=green!30] {3} }
+      child { node [circle, draw, fill=yellow!30] {4} }};
+  \end{tikzpicture}
+#+end_src
+#+RESULTS: tutorial
+[[file:../../img/tikz/tutorial.png]]
+\end{verbatim}
+
+The example begins with several lines containing \texttt{\#+header} which is sort of
+clutter. we can put them in a file and include it at the beginning of the Org
+file.
+\subsubsection{generate results with different formats}
+\label{sec:org75935d2}
+
+By changing the extension of \texttt{:file} (which is \texttt{pdf} for
+\texttt{"../../img/tikz/tutorial.pdf"} ), we can generate results with different formats.
+Now, I need \texttt{pdf} and \texttt{png} . You can see the result by just press \texttt{C-c C-c} in the
+body of the tikz code.
+\subsubsection{export the results according to the backend}
+\label{sec:org59da2c2}
+
+You can set \texttt{:exports} to control how the results will be exported. Now I set it
+as \texttt{none} which means the result will not be exported to latex or other format. I
+want to set more options of the exports. So I use:
+
+\begin{verbatim}
+#+ATTR_HTML:  :width 800 :align center
+#+ATTR_LATEX: :width 0.8\textwidth :align center
+{{{if-latex(tutorial.pdf,tutorial.png)}}}
+\end{verbatim}
+
+\texttt{if-latex} is a Org MACRO whose definition is :
+\begin{verbatim}
+#+MACRO: if-latex (eval (if (org-export-derived-backend-p org-export-current-backend 'latex)
+ (concat "[[file:../../img/tikz/"  $1 "]]")
+ (concat "[[file:../../img/tikz/"  $2 "]]") ))
+\end{verbatim}
+
+The \texttt{if-latex} MACRO let you export different formats by the backend. If the
+backend is \texttt{latex} then, \texttt{pdf} format figure will be exported. Otherwise, \texttt{png} format
+figure. Eventually, in the final \texttt{pdf} document, you figure can be zoomed in or
+out without losing any resolution.
+
+\subsubsection{the final workflow}
+\label{sec:orgc0cd8cc}
+
+The minimum working example at the start of this post is simplifed as below.
+
+\begin{verbatim}
+#+header: :file  "../../img/tikz/tutorial.pdf"
+#+begin_src latex
+  \begin{tikzpicture}
+    \node [circle, draw, fill=red!20] at (0,0) {1}
+    child { node [circle, draw, fill=blue!30] {2}
+      child { node [circle, draw, fill=green!30] {3} }
+      child { node [circle, draw, fill=yellow!30] {4} }};
+  \end{tikzpicture}
+#+end_src
+
+#+RESULTS:
+[[file:../../img/tikz/tutorial.png]]
+
+The following is the generated figure.
+#+ATTR_HTML:  :width 800 :align center
+#+ATTR_LATEX: :width 0.8\textwidth :align center
+{{{if-latex(tutorial.pdf,tutorial.png)}}}
+\end{verbatim}
+
+Many settings are grouped into a setup file which is included at the top of this
+post:
+\begin{verbatim}
+#+SETUPFILE: ~/.spacemacs.d/org-templates/math-en.org
+\end{verbatim}
+
+Now, If you set the extension of the target file in the first line either \texttt{pdf} or
+\texttt{png} , a corresponding \texttt{pdf} or \texttt{png} figure will be generated. If execute \texttt{M-x
+org-toggle-inline-images}  , you can preview the result. If export the org-file
+as latex file then the \texttt{pdf} file, the image of \texttt{pdf} format will be inserted. If
+export to other format, \texttt{png} image will be used.
 
 \section{Projects}
-\label{sec:orge8d1fc9}
+\label{sec:org8f61cb8}
 
 \subsection{my workflow of creating a video}
-\label{sec:org8223223}
+\label{sec:org597f5bb}
 During the creation of one video, several tools are tuned to fit my workflow. In
@@
 \subsubsection{Emacs}
-\label{sec:orgc041d09}
+\label{sec:org76d34e1}
 
@@
 \item program and debug
-\label{sec:orgafa531d}
+\label{sec:orgd2ab070}
 
@@
 \item Org mode - journalize your work
-\label{sec:orge1afdea}
+\label{sec:org75ff6e1}
 
@@
 \item Org mode - get things done
-\label{sec:org11a73ef}
+\label{sec:org4df4183}
 
 \item Org mode - write a diary
-\label{sec:org58bfcb8}
+\label{sec:org266bdcc}
 
 \item Org mode - export your Org file
-\label{sec:org4cc5d5b}
+\label{sec:orge9ee370}
 
 \item program and debug
-\label{sec:org0a78023}
+\label{sec:orgcf10226}
 
 \item writing latex
-\label{sec:orgdcebfa5}
+\label{sec:org69631c2}
 \item org-journal
-\label{sec:orgdb006ce}
+\label{sec:org06a8ebe}
 
@@
 \item ox-hugo
-\label{sec:orgefe2fb2}
+\label{sec:orgde97df4}
 
@@
 \item preview tikz picture in Org
-\label{sec:org9816573}
+\label{sec:org2bcb08b}
 
@@
 
-You can integrated TikZ code into the Org mode as a source block.A minimum
-working example is shown as below.
-
-[[file:~/Dropbox/mstemc_hugo/static/img/tikz/tutorial.png]]
-
-\begin{center}
-\includegraphics[width=0.4\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/tutorial.pdf}
-\end{center}
+You can integrated TikZ code into the Org mode as a source block. I have a
+not-so-detailed post on how to set up the tikz environment in Org.
 \end{enumerate}
@@
 \subsubsection{Hugo}
-\label{sec:org65579c9}
+\label{sec:org79f095e}
 
@@
 \subsubsection{manim}
-\label{sec:orgbb047b1}
+\label{sec:orga490cc3}
 
 \subsubsection{blender}
-\label{sec:orge8838d0}
+\label{sec:org362635d}
 
 \section{Courses}
-\label{sec:orgfc25921}
+\label{sec:orgc9e6ff6}
 \end{document}

### 2019-12-07 mstemc/index.tex
modify export-markdown-and-latex-using-emacs-org.org

@@
 % Intended LaTeX compiler: xelatex
-\documentclass[koma,a4paper,utopia,10pt,listings-color,microtype,paralist,colorlinks]{org-article}
+\documentclass[koma,utopia,letterpaper,captions=tableheading,11pt,listings-sv,microtype,paralist,colorlinks=true,urlcolor=blue]{org-article}
                \usepackage{tikz}
@@
 \date{\today}
-\title{Set up the TikZ in Emacs Org File}
+\title{Set up the TikZ in Emacs Org}
 \hypersetup{
  pdfauthor={Eason},
- pdftitle={Set up the TikZ in Emacs Org File},
+ pdftitle={Set up the TikZ in Emacs Org},
  pdfkeywords={},
- pdfsubject={An introduction to setup the TikZ environment in Emacs Org File.So that in Org file, you can generate either vector graph of \texttt{pdf}  format or raster graph of \texttt{png} format.
+ pdfsubject={An introduction to setup the TikZ environment in Emacs Org File.
+So that in Org file, you can generate either vector graph of \texttt{pdf}  format or raster graph of \texttt{png} format.
 Furthermore, you can export the vector graph when latex is called and otherwise raster graph.},
@@
 
-An introduction to setup the TikZ environment in Emacs Org File.So that in Org file, you can generate either vector graph of \texttt{pdf}  format or raster graph of \texttt{png} format.
+An introduction to setup the TikZ environment in Emacs Org File.
+So that in Org file, you can generate either vector graph of \texttt{pdf}  format or raster graph of \texttt{png} format.
 Furthermore, you can export the vector graph when latex is called and otherwise raster graph.
@@
 \section{config the header args}
-\label{sec:org1e65b28}
+\label{sec:orgb7646ae}
 
@@
 #+header: :results raw :exports none :fit yes :border 0cm
-#+header: :imagemagick t :iminoptions -density 400 :imoutoptions -geometry 400 -flatten
-#+header: :headers '("\\usepackage{tikz} \\usetikzlibrary{positioning, shapes.symbols, calc}")
+#+header: :imagemagick t :iminoptions -density 400
+#+header: :imoutoptions -geometry 400 -flatten
+#+header: :headers '("\\usepackage{tikz} \\usetikzlibrary{positioning,
+           shapes.symbols, calc}")
 #+begin_src latex
@@
 \section{generate results with different formats}
-\label{sec:org92aa971}
+\label{sec:orgfa49106}
 
@@
 \section{export the results according to the backend}
-\label{sec:org8166ca3}
+\label{sec:org6e31306}
 
@@
 \begin{verbatim}
-#+MACRO: if-latex (eval (if (org-export-derived-backend-p org-export-current-backend 'latex)
+#+MACRO: if-latex (eval (if
+(org-export-derived-backend-p org-export-current-backend 'latex)
  (concat "[[file:../../img/tikz/"  $1 "]]")
@@
 \section{the final workflow}
-\label{sec:org6fc731d}
+\label{sec:orgdf6c076}
 

### 2019-12-10 mstemc/index.tex
add a post: drawing-graphs-using-tikz-in-emacs-org
trivial modification

@@
 \date{\today}
-\title{Set up the TikZ in Emacs Org}
+\title{Drawing Graphs Using TikZ in Emacs Org}
 \hypersetup{
  pdfauthor={Eason},
- pdftitle={Set up the TikZ in Emacs Org},
+ pdftitle={Drawing Graphs Using TikZ in Emacs Org},
  pdfkeywords={},
- pdfsubject={An introduction to setup the TikZ environment in Emacs Org File.
-So that in Org file, you can generate either vector graph of \texttt{pdf}  format or raster graph of \texttt{png} format.
-Furthermore, you can export the vector graph when latex is called and otherwise raster graph.},
+ pdfsubject={This post collects working examples of drawing graphs using TikZ in Emacs Org},
  pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
@@
 
-\hspace{0pt}\\
+\begin{center}
+\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/example.pdf}
+\end{center}
 
-An introduction to setup the TikZ environment in Emacs Org File.
-So that in Org file, you can generate either vector graph of \texttt{pdf}  format or raster graph of \texttt{png} format.
-Furthermore, you can export the vector graph when latex is called and otherwise raster graph.
+\begin{center}
+\includegraphics[width=0.7\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/example1.pdf}
+\end{center}
 
-\section{config the header args}
-\label{sec:orgb7646ae}
-
-You can embed TiKz (One of \(\LaTeX\) graphic package) code into a Org file. With
-org-babel, you can generate ,insert and export the figure generated from Tikz
-package. At first, you need set up the environment. \href{https://orgmode.org/worg/org-contrib/babel/languages/ob-doc-LaTeX.html}{This Post} serves as a good
-introduction for beginners. Following it you may have a minimum working example
-like below:
-
-\begin{verbatim}
-#+name: tutorial
-#+header: :file "~/Dropbox/mstemc_hugo/static/img/tikz/tutorial.png"
-#+header: :results raw :exports none :fit yes :border 0cm
-#+header: :imagemagick t :iminoptions -density 400
-#+header: :imoutoptions -geometry 400 -flatten
-#+header: :headers '("\\usepackage{tikz} \\usetikzlibrary{positioning,
-           shapes.symbols, calc}")
-#+begin_src latex
-  \begin{tikzpicture}
-    \node [circle, draw, fill=red!20] at (0,0) {1}
-    child { node [circle, draw, fill=blue!30] {2}
-      child { node [circle, draw, fill=green!30] {3} }
-      child { node [circle, draw, fill=yellow!30] {4} }};
-  \end{tikzpicture}
-#+end_src
-#+RESULTS: tutorial
-[[file:../../img/tikz/tutorial.png]]
-\end{verbatim}
-
-The example begins with several lines containing \texttt{\#+header} which is sort of
-clutter. we can put them in a file and include it at the beginning of the Org
-file.
-\section{generate results with different formats}
-\label{sec:orgfa49106}
-
-By changing the extension of \texttt{:file} (which is \texttt{pdf} for
-\texttt{"../../img/tikz/tutorial.pdf"} ), we can generate results with different formats.
-Now, I need \texttt{pdf} and \texttt{png} . You can see the result by just press \texttt{C-c C-c} in the
-body of the tikz code.
-\section{export the results according to the backend}
-\label{sec:org6e31306}
-
-You can set \texttt{:exports} to control how the results will be exported. Now I set it
-as \texttt{none} which means the result will not be exported to latex or other format. I
-want to set more options of the exports. So I use:
-
-\begin{verbatim}
-#+ATTR_HTML:  :width 800 :align center
-#+ATTR_LATEX: :width 0.8\textwidth :align center
-{{{if-latex(tutorial.pdf,tutorial.png)}}}
-\end{verbatim}
-
-\texttt{if-latex} is a Org MACRO whose definition is :
-\begin{verbatim}
-#+MACRO: if-latex (eval (if
-(org-export-derived-backend-p org-export-current-backend 'latex)
- (concat "[[file:../../img/tikz/"  $1 "]]")
- (concat "[[file:../../img/tikz/"  $2 "]]") ))
-\end{verbatim}
-
-The \texttt{if-latex} MACRO let you export different formats by the backend. If the
-backend is \texttt{latex} then, \texttt{pdf} format figure will be exported. Otherwise, \texttt{png} format
-figure. Eventually, in the final \texttt{pdf} document, you figure can be zoomed in or
-out without losing any resolution.
-
-\section{the final workflow}
-\label{sec:orgdf6c076}
-
-The minimum working example at the start of this post is simplifed as below.
-
-\begin{verbatim}
-#+header: :file  "../../img/tikz/tutorial.pdf"
-#+begin_src latex
-  \begin{tikzpicture}
-    \node [circle, draw, fill=red!20] at (0,0) {1}
-    child { node [circle, draw, fill=blue!30] {2}
-      child { node [circle, draw, fill=green!30] {3} }
-      child { node [circle, draw, fill=yellow!30] {4} }};
-  \end{tikzpicture}
-#+end_src
-
-#+RESULTS:
-[[file:../../img/tikz/tutorial.png]]
-
-The following is the generated figure.
-#+ATTR_HTML:  :width 800 :align center
-#+ATTR_LATEX: :width 0.8\textwidth :align center
-{{{if-latex(tutorial.pdf,tutorial.png)}}}
-\end{verbatim}
-
-Many settings are grouped into a setup file which is included at the top of this
-post:
-\begin{verbatim}
-#+SETUPFILE: ~/.spacemacs.d/org-templates/math-en.org
-\end{verbatim}
-
-Now, If you set the extension of the target file in the first line either \texttt{pdf} or
-\texttt{png} , a corresponding \texttt{pdf} or \texttt{png} figure will be generated. If execute \texttt{M-x
-org-toggle-inline-images}  , you can preview the result. If export the org-file
-as latex file then the \texttt{pdf} file, the image of \texttt{pdf} format will be inserted. If
-export to other format, \texttt{png} image will be used.
+\begin{center}
+\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/basiclayer.pdf}
+\end{center}
 \end{document}

### 2019-12-11 mstemc/index.tex
an important commit: the drawing in tikz post works well

@@
 % Intended LaTeX compiler: xelatex
-\documentclass[koma,utopia,letterpaper,captions=tableheading,11pt,listings-sv,microtype,paralist,colorlinks=true,urlcolor=blue]{org-article}
+\documentclass[koma,utopia,a4paper,captions=tableheading,11pt,listings-sv,microtype,paralist,colorlinks=true,urlcolor=blue]{org-article}
                \usepackage{tikz}
@@
 
+Draw a graph using TikZ
+
+[[file:~/Dropbox/mstemc_hugo/static/img/tikz/example.pdf]]
+
 \begin{center}

### 2019-12-11 mstemc/mstemc.tex
an important commit: the drawing in tikz post works well

@@
 % Intended LaTeX compiler: xelatex
-\documentclass[koma,a4paper,utopia,10pt,listings-color,microtype,paralist,colorlinks]{org-article}
+\documentclass[koma,a4paper,captions=tableheading,11pt,listings-sv,microtype,paralist,colorlinks=true,urlcolor=blue,palatino]{org-article}
                \usepackage{tikz}
@@
 \section{Videos}
-\label{sec:org002a437}
+\label{sec:org80ec581}
 
 \section{Posts}
-\label{sec:org2d95323}
+\label{sec:org275e087}
 
-\subsection{Set up the TikZ in Emacs Org File}
-\label{sec:org64c90ff}
-\begin{summary}
-Why is this in \textbf{green}?
-\end{summary}
+\subsection{Set up the TikZ in Emacs Org}
+\label{sec:org5387454}
+\hspace{0pt}\\
+
+An introduction to setup the TikZ environment in Emacs Org File.
+So that in Org file, you can generate either vector graph of \texttt{pdf}  format or raster graph of \texttt{png} format.
+Furthermore, you can export the vector graph when latex is called and otherwise raster graph.
 
 \subsubsection{config the header args}
-\label{sec:org825d7de}
+\label{sec:org3f3612a}
 
@@
 \subsubsection{generate results with different formats}
-\label{sec:org75935d2}
+\label{sec:orgac277d3}
 
@@
 \subsubsection{export the results according to the backend}
-\label{sec:org59da2c2}
+\label{sec:org864fe62}
 
@@
 \subsubsection{the final workflow}
-\label{sec:orgc0cd8cc}
+\label{sec:orgc26c788}
 
@@
 
+\subsection{Export Markdown and latex using Emacs Org}
+\label{sec:orgb25f912}
+
+\hspace{0pt}\\
+
+set up the Emacs org and ox-hugo to export the org files in markdown and latex format.
+
+\subsubsection{Introduction}
+\label{sec:org1a16d6f}
+
+I use hugo before it support Emacs org file. Then I use an Emacs extension
+called \href{https://github.com/kaushalmodi/ox-hugo}{ox-hugo} which is a carefully crafted Org exporter back-end for Hugo.
+Ox-hugo meets all my requirement and definitely worth a try when you are an
+advanced user of Emacs Org. By the way, if you are quite familiar with Emacs
+Org, there is no need to take time to learn markdown. Emacs Org, I think, is
+more elegant than markdown.
+
+\subsubsection{set up ox-hugo}
+\label{sec:org11a7de8}
+
+I use Spacemacs and integrate ox-hugo into my config is easy. You can add it
+into your private layer or just add it in your \texttt{user-config} . Please refer to
+\href{https://github.com/kaushalmodi/ox-hugo}{the repo.} and read the document for more information.
+
+The first time you want to export an Org file or a subtree of an Org file, use
+\texttt{M-x org-hugo-export-to-md} . There will be a hugo-related section in the
+\texttt{org-dispatcher} whenever you use \texttt{C-c C-e} .
+\subsubsection{use Org Macro replacement}
+\label{sec:orgf79a086}
+
+Often, you want different actions when you export the Org file to
+hugo-compatible markdown and latex file. For example, hugo or hugo theme supports
+summary and shortcodes such as \texttt{alert note} and \texttt{alert warning} (see  \href{https://sourcethemes.com/academic/docs/writing-markdown-latex/}{Writing
+content with Markdown, \LaTeX{}, and Shortcodes | Academic} )
+
+When you export the snippet to markdown then hugo will display the content
+according to the css. However, latex does not recognize the shortcodes. So latex
+will display \texttt{\{ \{\% alert note \%\} \}} literally which is clutter. The Org Macro may
+help. For more information please refer to \href{https://orgmode.org/manual/Macro-replacement.html}{The Org Manual: Macro replacement} and
+\href{https://github.com/fniessen/org-macros}{fniessen/org-macros: Shared macros for Org mode} . I also define my own Org Macro
+in \href{https://github.com/msteamc/.spacemacs.d/blob/master/org-templates/enpost.org}{my setup file for every .org file}. With Org Macro, I control some contents
+and options exist only for certain backend.
+
+Once you are familiar with Org Macro, It behaves beyond your imagination.
+\subsubsection{use the setupfile for each Org file}
+\label{sec:org66edc24}
+
+Often, you options for a org file grows more and more. If you think it kind of
+clutter at the top of your Org files, you can group them in a setupfile then
+include it at the top of your Org file.
+
+For my setupfiles, please refer to \href{https://github.com/msteamc/.spacemacs.d/tree/master/org-templates}{my org-templates}. As you can see, I have
+several setupfiles for different aims. To include one of them in my Org file, I
+use:
+
+\texttt{\#+SETUPFILE: <path+name of the setup files>}
+
+By using \texttt{\#+SETUPFILE} ,I only have to option lines at the top of my org file.
+So it looks clean.
+
+Also, you can notice that in \href{https://github.com/msteamc/.spacemacs.d/blob/master/org-templates/enpost.org}{my setupfile named enpost.org} exists options for
+different export targets.
+
+\subsection{Drawing Graphs Using TikZ in Emacs Org}
+\label{sec:org171ea2a}
+
+Draw a graph using TikZ
+
+\begin{center}
+\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/example.pdf}
+\end{center}
+
+\begin{center}
+\includegraphics[width=0.7\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/example1.pdf}
+\end{center}
+
+\begin{center}
+\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/basiclayer.pdf}
+\end{center}
+
 \section{Projects}
-\label{sec:org8f61cb8}
+\label{sec:org91fe676}
 
 \subsection{my workflow of creating a video}
-\label{sec:org597f5bb}
+\label{sec:org7aa4f8b}
+\hspace{0pt}\\
+
+This collection of Videos and Posts describes my workflow of creating a video. Usage of some tools and methods are covered.
+
 During the creation of one video, several tools are tuned to fit my workflow. In
@@
 \subsubsection{Emacs}
-\label{sec:org76d34e1}
+\label{sec:org2fbd9b9}
 
@@
 \item program and debug
-\label{sec:orgd2ab070}
+\label{sec:org2090515}
 
@@
 \item Org mode - journalize your work
-\label{sec:org75ff6e1}
+\label{sec:org68fd51b}
 
@@
 \item Org mode - get things done
-\label{sec:org4df4183}
+\label{sec:orgc649c82}
 
 \item Org mode - write a diary
-\label{sec:org266bdcc}
+\label{sec:orgc5ee9f2}
 
 \item Org mode - export your Org file
-\label{sec:orge9ee370}
+\label{sec:orgec750d0}
 
 \item program and debug
-\label{sec:orgcf10226}
+\label{sec:org78ee2a9}
 
 \item writing latex
-\label{sec:org69631c2}
+\label{sec:org5309ad9}
 \item org-journal
-\label{sec:org06a8ebe}
+\label{sec:orgb4dcd6b}
 
@@
 \item ox-hugo
-\label{sec:orgde97df4}
+\label{sec:org5a96636}
 
@@
 \item preview tikz picture in Org
-\label{sec:org2bcb08b}
+\label{sec:org8bf8be5}
 
@@
 \subsubsection{Hugo}
-\label{sec:org79f095e}
+\label{sec:orgaed3855}
 
@@
 about how to leverage Hugo. Ox-hugo helps me do most of the work.
+\subsubsection{Hugo Academic Theme}
+\label{sec:org7ca124e}
+
+\href{https://github.com/gcushen/hugo-academic}{Hugo Academic Theme} is a beautiful and flexible theme developed for Hugo. This
+site is built based on this theme.
+
+If you want attach a pdf version of your post, two steps are needed:
+\begin{enumerate}
+\item add a line:
+\begin{verbatim}
+url_pdf = "#"
+\end{verbatim}
+in the front matter of your markdown file.
+\item add a PDF file with the same name as your post’s own folder to your post’s
+folder.
+\end{enumerate}
+
+A PDF link will be automatically generated just like the \texttt{pdf} link appears in
+the top of each post in my site. Because I use Emacs Org with ox-hugo, I add one
+line in the property:
+
+\begin{verbatim}
+:EXPORT_HUGO_CUSTOM_FRONT_MATTER+: :url_pdf "#"
+\end{verbatim}
+
+Hugo academic theme provide some front matters that hugo does not support by
+default. Fortunately, \href{https://github.com/kaushalmodi/ox-hugo}{ox-hugo} handles this effectively. For more information.
+you can read:
+\begin{enumerate}
+\item \href{https://ox-hugo.scripter.co/doc/org-meta-data-to-hugo-front-matter/}{Org meta-data to Hugo front-matter}
+\item \href{https://ox-hugo.scripter.co/doc/custom-front-matter/}{Custom Front-matter Parameters}
+\end{enumerate}
 
 \subsubsection{manim}
-\label{sec:orga490cc3}
+\label{sec:org12e9ea1}
 
 \subsubsection{blender}
-\label{sec:org362635d}
+\label{sec:orgb3042c1}
 
 \section{Courses}
-\label{sec:orgc9e6ff6}
+\label{sec:org92abef5}
 \end{document}

### 2019-12-13 mstemc/index.tex
trivial modification
exported latex(pdf) file with no line number

@@
-% Intended LaTeX compiler: xelatex
+% Intended LaTeX compiler: pdflatex
 \documentclass[koma,utopia,a4paper,captions=tableheading,11pt,listings-sv,microtype,paralist,colorlinks=true,urlcolor=blue]{org-article}
@@
 
-\maketitle
+\newcommand*{\titleCM}{\begingroup
+\vspace*{\drop}
+\begin{center}
+\vspace{\baselineskip}
+{\Huge \textbf{Drawing Graphs Using TikZ in Emacs Org} \par}
+\vspace{2\baselineskip}   \newline
+{\large Eason Zhang with www.makesteamclear.com \par}
+\vspace{\baselineskip}          \newline
+{\large \today \par}
+\vspace{\baselineskip}
+\vfill
+\setlength{\unitlength}{3pt}
+\makebox[\textwidth][c]{\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/example3.pdf}}
+\vfill
+\vspace{\baselineskip}
+{\Large WWW.MAKESTEAMCLEAR.COM \par}\newline
+\vspace{\baselineskip}
+{\texttt www.makesteamclear.com is a free project, supported by Eason Zhang, to make videos about STEAM in a more approachable and different way.
+If you found the contents in this post or the site or the youtube channel helpful, please consider support me, thanks \par}
+\end{center}
+\vspace*{\drop}
+\endgroup}
+\begin{titlepage}
+\titleCM
+\end{titlepage}
 \tableofcontents
 
-Draw a graph using TikZ
+\section{Drawing a TikZ picture in Emacs Org Mode}
+\label{sec:org8d51a0b}
 
-[[file:~/Dropbox/mstemc_hugo/static/img/tikz/example.pdf]]
+\lstset{language=[LaTeX]TeX,label=a-minimum-working-example,caption={a minimum working example},captionpos=b,firstnumber=1,numbers=left}
+\begin{lstlisting}
+\usetikzlibrary{intersections,arrows.meta}
+\begin{tikzpicture}[thin]
+\draw (-1.5,0) -- (1.5,0);
+\draw (0,-1.5) -- (0,1.5);
+\filldraw[fill = green!20, draw = green!50!black] (0,0) circle[radius = 1cm];
+\draw (0,0) rectangle (.5,.5);
+\draw (0,0) rectangle (-0.5,-0.5);
+\draw[help lines,very thin,step=.5cm,color=gray] (-1.5,-1.5) grid (1.5,1.5);
+% relative coordinate
+\draw[blue, very thick] (30:1) ++ (0,-0.5) --(0,0);
+% name a path without drawing it
+\path[name path = upward line] (1,0) -- (1,1);
+\path[name path = sloped line] (0,0) -- (30:1.5cm);
+% use intersection of two path
+\draw[name intersections={of = upward line and sloped line, by=x}]
+     [very thick, orange] (1,0) -- (x);
+% use arrow
+\draw[<->>] (0,0) -- (145:1);
+\draw[<-{Triangle[fill=red]}] (0,0) -- (30:1);
+% use scope
+\begin{scope}[very thick]
+\draw (-0.4,0.4) -- (0.4,0.4);
+\draw (-0.4,-0.4) -- (0.4,-0.4);
+\end{scope}
+% use foreach
+\foreach \x in {-1cm,-0.5cm,1cm}
+    \draw[red] (\x,-3pt) -- (\x,3pt);
+\foreach \y in {-1cm,-0.5cm,1cm}
+    \draw[red](-3pt,\y) -- (3pt,\y);
+% using node
+\draw (0,0)+(0.2,-0.2) node {\tiny $(0,0)$ };
+\end{tikzpicture}
+\end{lstlisting}
 
+\hspace{0pt}\\
+The generated figure is shown as:
 \begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/example.pdf}
+\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/example3.pdf}
 \end{center}
 
+\begin{enumerate}
+\item In \hyperref[a-minimum-working-example]{the minimum working example} line 12 , a path is named  without drawing
+it.
+\item Line 16 gives an example of using library \texttt{intersections}. Note
+that you need to add the library using \texttt{\textbackslash{}usetikzlibrary\{intersections\}}
+otherwise an error occurs during \LaTeX compiling.
+\item Line 18 and 19 gives an example of using arrow. To make it work,
+\texttt{\textbackslash{}usetikzlibrary\{arrows.meta\}} is needed. The library \texttt{arrows.meta} provides tons
+of types of arrows whick shock me when I see them the first time.
+\item Line 21 to 24 gives an example of \texttt{scope} . In the environment, all
+the lines are drawn in the \texttt{very thick} style.
+\item Line 26 to 29 gives an examplt of \texttt{foreach} . \texttt{foreach} is handy
+when you want to draw a list of objects. In \hyperref[a-minimum-working-example]{the minimum working example} , I
+draw a list of short red sticks along with the x-axis and y-axis.
+\item Line 31 is an example of \texttt{node}. The keyword \texttt{node} is typically followed by
+some options between \texttt{[]} and then some text between \texttt{\{\}}. Every node has flexible
+anchor options to decide where the text should be placed.
+\end{enumerate}
+\section{Another Example}
+\label{sec:orgc5e5c7a}
+
+The code is shown as:
+\lstset{language=[LaTeX]TeX,label=another-minimum-working-example,caption={another minimum working example},captionpos=b,firstnumber=1,numbers=left}
+\begin{lstlisting}
+\usetikzlibrary{intersections,arrows.meta}
+\begin{tikzpicture}[scale=3]
+  \clip (-0.6,-0.2) rectangle (0.6,1.51);
+  \draw[step = .5cm, help lines] (-1.4,-1.4) grid (1.4,1.4);
+  \filldraw[fill=green!20,draw = green!50!black] (0,0) -- (3mm,0mm)
+  arc [start angle = 0, end angle = 30,radius = 3mm] -- cycle;
+  \draw[->] (-1.5,0) -- (1.5,0);
+  \draw[->] (0,-1.5) -- (0,1.5);
+  \draw (0,0) circle [radius=1cm];
+  \foreach \x in {-1,-0.5,1}
+  \draw(\x cm, 1pt) -- (\x cm, -1 pt) node [anchor = north] {$\x$};
+  \foreach \y in {-1,-0.5,1}
+  \draw(1pt,\y cm) -- (-1pt, \y cm) node[anchor = east] {$\y$};
+\end{tikzpicture}
+\end{lstlisting}
+
+The generated figure is shown as:
 \begin{center}
-\includegraphics[width=0.7\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/example1.pdf}
+\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/example4.pdf}
 \end{center}
 
-\begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/basiclayer.pdf}
-\end{center}
+\section{Some Basic Rules in TikZ}
+\label{sec:org171b856}
+
+\begin{enumerate}
+\item The options appear in \texttt{[]}. No matter it is an object or an operation, the
+contents in the following  \texttt{[]} serve as options.
+
+Options \texttt{[]} can be at the very beginning of the environment \texttt{tikzpicture}
+following the operation, following the object.
+
+\item \texttt{\textbackslash{}filldraw} is a good command. It draws a closed loop and fill it with color or
+pattern. The colors for filling and drawing can be different.
+
+\item Coordinates can be specified in x-y format, polar format.
+\begin{itemize}
+\item The easiest way is \texttt{(x,y)} which means \texttt{x} cm in the x-axis and \texttt{y} cm in the
+y-axis;
+\item \texttt{(a:x)} is the polar format which means \texttt{x} cm in direction \texttt{a} degree.
+\end{itemize}
+\item \texttt{(<p> |- <q>)} is another way to specify coordinates for example \texttt{(30:1 |- 0,0)}
+which means the interaction of a vertical line through \texttt{(30:1)} and a
+horizontal line through \texttt{(0,0)} .
+\item Relative coordinates are possible with \texttt{+} and \texttt{++} in front of \texttt{(x,y)} and \texttt{(a:x)} .
+\texttt{+} is relative to the closest coordinate whereas \texttt{++} is relative to the very
+first coordinate of current path.
+\end{enumerate}
+
+\section{Some tips for in TikZ}
+\label{sec:org46592f8}
+
+\begin{enumerate}
+\item To use \texttt{intersections} to specify a coordinate, you need to include the
+library, i.e. \texttt{\textbackslash{}usetikzlibrary\{intersections\}} is a must.
+\end{enumerate}
+
+\lstset{language=C,label= ,caption= ,captionpos=b,firstnumber=1,numbers=left}
+\begin{lstlisting}
+int main()
+{
+  int i=0;
+  printf();
+}
+\end{lstlisting}
+
+\bibliography{../../research_library/zcl}
+\bibliographystyle{unsrt}
 \end{document}

### 2019-12-13 mstemc/mstemc.tex
exported latex(pdf) file with no line number

@@
-% Intended LaTeX compiler: xelatex
-\documentclass[koma,a4paper,captions=tableheading,11pt,listings-sv,microtype,paralist,colorlinks=true,urlcolor=blue,palatino]{org-article}
+% Intended LaTeX compiler: pdflatex
+\documentclass[koma,utopia,a4paper,captions=tableheading,11pt,listings-sv,microtype,paralist,colorlinks=true,urlcolor=blue]{org-article}
                \usepackage{tikz}
@@
 
-\maketitle
+\newcommand*{\titleCM}{\begingroup
+\vspace*{\drop}
+\begin{center}
+\vspace{\baselineskip}
+{\Huge \textbf{make STEAM clear} \par}
+\vspace{2\baselineskip}   \newline
+{\large Eason Zhang with www.makesteamclear.com \par}
+\vspace{\baselineskip}          \newline
+{\large \today \par}
+\vspace{\baselineskip}
+\vfill
+\setlength{\unitlength}{3pt}
+\makebox[\textwidth][c]{\includegraphics[width=0.2\textwidth]{\~/Dropbox/mstemc_hugo/static/img/tikz/example3.pdf}}
+\vfill
+\vspace{\baselineskip}
+{\Large WWW.MAKESTEAMCLEAR.COM \par}\newline
+\vspace{\baselineskip}
+{\texttt www.makesteamclear.com is a free project, supported by Eason Zhang, to make videos about STEAM in a more approachable and different way.
+If you found the contents in this post or the site or the youtube channel helpful, please consider support me, thanks \par}
+\end{center}
+\vspace*{\drop}
+\endgroup}
+\begin{titlepage}
+\titleCM
+\end{titlepage}
 \tableofcontents
@@
 \section{Videos}
-\label{sec:org80ec581}
+\label{sec:orge61aa3c}
 
 \section{Posts}
-\label{sec:org275e087}
+\label{sec:orgcd8829e}
 
 \subsection{Set up the TikZ in Emacs Org}
-\label{sec:org5387454}
+\label{sec:org7c6689e}
 \hspace{0pt}\\
@@
 \subsubsection{config the header args}
-\label{sec:org3f3612a}
+\label{sec:org8a24a77}
 
@@
 \subsubsection{generate results with different formats}
-\label{sec:orgac277d3}
+\label{sec:org05b6333}
 
@@
 \subsubsection{export the results according to the backend}
-\label{sec:org864fe62}
+\label{sec:orgff78033}
 
@@
 \subsubsection{the final workflow}
-\label{sec:orgc26c788}
+\label{sec:orga6d2484}
 
@@
 \subsection{Export Markdown and latex using Emacs Org}
-\label{sec:orgb25f912}
+\label{sec:orgd6fe22f}
 
@@
 \subsubsection{Introduction}
-\label{sec:org1a16d6f}
+\label{sec:orgd478c4d}
 
@@
 \subsubsection{set up ox-hugo}
-\label{sec:org11a7de8}
+\label{sec:org76b6cf4}
 
@@
 \subsubsection{use Org Macro replacement}
-\label{sec:orgf79a086}
+\label{sec:orga32c0f1}
 
@@
 \subsubsection{use the setupfile for each Org file}
-\label{sec:org66edc24}
+\label{sec:org589cab1}
 
@@
 \subsection{Drawing Graphs Using TikZ in Emacs Org}
-\label{sec:org171ea2a}
+\label{sec:org220de70}
 
-Draw a graph using TikZ
+\subsubsection{Drawing a TikZ picture in Emacs Org Mode}
+\label{sec:orgd491791}
 
+\lstset{language=[LaTeX]TeX,label=a-minimum-working-example,caption={a minimum working example},captionpos=b,firstnumber=1,numbers=left}
+\begin{lstlisting}
+\usetikzlibrary{intersections,arrows.meta}
+\begin{tikzpicture}[thin]
+\draw (-1.5,0) -- (1.5,0);
+\draw (0,-1.5) -- (0,1.5);
+\filldraw[fill = green!20, draw = green!50!black] (0,0) circle[radius = 1cm];
+\draw (0,0) rectangle (.5,.5);
+\draw (0,0) rectangle (-0.5,-0.5);
+\draw[help lines,very thin,step=.5cm,color=gray] (-1.5,-1.5) grid (1.5,1.5);
+% relative coordinate
+\draw[blue, very thick] (30:1) ++ (0,-0.5) --(0,0);
+% name a path without drawing it
+\path[name path = upward line] (1,0) -- (1,1);
+\path[name path = sloped line] (0,0) -- (30:1.5cm);
+% use intersection of two path
+\draw[name intersections={of = upward line and sloped line, by=x}]
+     [very thick, orange] (1,0) -- (x);
+% use arrow
+\draw[<->>] (0,0) -- (145:1);
+\draw[<-{Triangle[fill=red]}] (0,0) -- (30:1);
+% use scope
+\begin{scope}[very thick]
+\draw (-0.4,0.4) -- (0.4,0.4);
+\draw (-0.4,-0.4) -- (0.4,-0.4);
+\end{scope}
+% use foreach
+\foreach \x in {-1cm,-0.5cm,1cm}
+    \draw[red] (\x,-3pt) -- (\x,3pt);
+\foreach \y in {-1cm,-0.5cm,1cm}
+    \draw[red](-3pt,\y) -- (3pt,\y);
+% using node
+\draw (0,0)+(0.2,-0.2) node {\tiny $(0,0)$ };
+\end{tikzpicture}
+\end{lstlisting}
+
+\hspace{0pt}\\
+The generated figure is shown as:
 \begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/example.pdf}
+\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/example3.pdf}
 \end{center}
 
+\begin{enumerate}
+\item In \hyperref[a-minimum-working-example]{the minimum working example} line 12 , a path is named  without drawing
+it.
+\item Line 16 gives an example of using library \texttt{intersections}. Note
+that you need to add the library using \texttt{\textbackslash{}usetikzlibrary\{intersections\}}
+otherwise an error occurs during \LaTeX compiling.
+\item Line 18 and 19 gives an example of using arrow. To make it work,
+\texttt{\textbackslash{}usetikzlibrary\{arrows.meta\}} is needed. The library \texttt{arrows.meta} provides tons
+of types of arrows whick shock me when I see them the first time.
+\item Line 21 to 24 gives an example of \texttt{scope} . In the environment, all
+the lines are drawn in the \texttt{very thick} style.
+\item Line 26 to 29 gives an examplt of \texttt{foreach} . \texttt{foreach} is handy
+when you want to draw a list of objects. In \hyperref[a-minimum-working-example]{the minimum working example} , I
+draw a list of short red sticks along with the x-axis and y-axis.
+\item Line 31 is an example of \texttt{node}. The keyword \texttt{node} is typically followed by
+some options between \texttt{[]} and then some text between \texttt{\{\}}. Every node has flexible
+anchor options to decide where the text should be placed.
+\end{enumerate}
+\subsubsection{Another Example}
+\label{sec:orgbc1168b}
+
+The code is shown as:
+\lstset{language=[LaTeX]TeX,label=another-minimum-working-example,caption={another minimum working example},captionpos=b,firstnumber=1,numbers=left}
+\begin{lstlisting}
+\usetikzlibrary{intersections,arrows.meta}
+\begin{tikzpicture}[scale=3]
+  \clip (-0.6,-0.2) rectangle (0.6,1.51);
+  \draw[step = .5cm, help lines] (-1.4,-1.4) grid (1.4,1.4);
+  \filldraw[fill=green!20,draw = green!50!black] (0,0) -- (3mm,0mm)
+  arc [start angle = 0, end angle = 30,radius = 3mm] -- cycle;
+  \draw[->] (-1.5,0) -- (1.5,0);
+  \draw[->] (0,-1.5) -- (0,1.5);
+  \draw (0,0) circle [radius=1cm];
+  \foreach \x in {-1,-0.5,1}
+  \draw(\x cm, 1pt) -- (\x cm, -1 pt) node [anchor = north] {$\x$};
+  \foreach \y in {-1,-0.5,1}
+  \draw(1pt,\y cm) -- (-1pt, \y cm) node[anchor = east] {$\y$};
+\end{tikzpicture}
+\end{lstlisting}
+
+The generated figure is shown as:
 \begin{center}
-\includegraphics[width=0.7\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/example1.pdf}
+\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/example4.pdf}
 \end{center}
 
-\begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/basiclayer.pdf}
-\end{center}
+\subsubsection{Some Basic Rules in TikZ}
+\label{sec:orgdb48b38}
+
+\begin{enumerate}
+\item The options appear in \texttt{[]}. No matter it is an object or an operation, the
+contents in the following  \texttt{[]} serve as options.
+
+Options \texttt{[]} can be at the very beginning of the environment \texttt{tikzpicture}
+following the operation, following the object.
+
+\item \texttt{\textbackslash{}filldraw} is a good command. It draws a closed loop and fill it with color or
+pattern. The colors for filling and drawing can be different.
+
+\item Coordinates can be specified in x-y format, polar format.
+\begin{itemize}
+\item The easiest way is \texttt{(x,y)} which means \texttt{x} cm in the x-axis and \texttt{y} cm in the
+y-axis;
+\item \texttt{(a:x)} is the polar format which means \texttt{x} cm in direction \texttt{a} degree.
+\end{itemize}
+\item \texttt{(<p> |- <q>)} is another way to specify coordinates for example \texttt{(30:1 |- 0,0)}
+which means the interaction of a vertical line through \texttt{(30:1)} and a
+horizontal line through \texttt{(0,0)} .
+\item Relative coordinates are possible with \texttt{+} and \texttt{++} in front of \texttt{(x,y)} and \texttt{(a:x)} .
+\texttt{+} is relative to the closest coordinate whereas \texttt{++} is relative to the very
+first coordinate of current path.
+\end{enumerate}
+
+\subsubsection{Some tips for in TikZ}
+\label{sec:org8e92c4c}
+
+\begin{enumerate}
+\item To use \texttt{intersections} to specify a coordinate, you need to include the
+library, i.e. \texttt{\textbackslash{}usetikzlibrary\{intersections\}} is a must.
+\end{enumerate}
+
+\lstset{language=C,label= ,caption= ,captionpos=b,numbers=none}
+\begin{lstlisting}
+int main()
+{
+  int i=0;
+  printf();
+}
+\end{lstlisting}
+
+\bibliography{../../research_library/zcl}
+\bibliographystyle{unsrt}
 
 \section{Projects}
-\label{sec:org91fe676}
+\label{sec:org92a94e0}
 
 \subsection{my workflow of creating a video}
-\label{sec:org7aa4f8b}
+\label{sec:orga6b7968}
 \hspace{0pt}\\
@@
 \subsubsection{Emacs}
-\label{sec:org2fbd9b9}
+\label{sec:org9c05b58}
 
@@
 \item program and debug
-\label{sec:org2090515}
+\label{sec:orge66ddd0}
 
@@
 \item Org mode - journalize your work
-\label{sec:org68fd51b}
+\label{sec:org108dfd7}
 
@@
 \item Org mode - get things done
-\label{sec:orgc649c82}
+\label{sec:orgb5f62bc}
 
 \item Org mode - write a diary
-\label{sec:orgc5ee9f2}
+\label{sec:org168bbcf}
 
 \item Org mode - export your Org file
-\label{sec:orgec750d0}
+\label{sec:orgce77f24}
 
 \item program and debug
-\label{sec:org78ee2a9}
+\label{sec:org6b73797}
 
 \item writing latex
-\label{sec:org5309ad9}
+\label{sec:orgf96355a}
 \item org-journal
-\label{sec:orgb4dcd6b}
+\label{sec:orgc17cd60}
 
@@
 \item ox-hugo
-\label{sec:org5a96636}
+\label{sec:org9e07d00}
 
@@
 \item preview tikz picture in Org
-\label{sec:org8bf8be5}
+\label{sec:orgab2630d}
 
@@
 \subsubsection{Hugo}
-\label{sec:orgaed3855}
+\label{sec:org3f30c08}
 
@@
 \subsubsection{Hugo Academic Theme}
-\label{sec:org7ca124e}
+\label{sec:orgad8a7d5}
 
@@
 \subsubsection{manim}
-\label{sec:org12e9ea1}
+\label{sec:org022fb8d}
 
 \subsubsection{blender}
-\label{sec:orgb3042c1}
+\label{sec:org7659274}
 
 \section{Courses}
-\label{sec:org92abef5}
+\label{sec:org85ca59f}
 \end{document}

### 2019-12-13 mstemc/index.tex
highlight c code in html is OK

@@
 % Intended LaTeX compiler: pdflatex
-\documentclass[koma,utopia,a4paper,captions=tableheading,11pt,listings-sv,microtype,paralist,colorlinks=true,urlcolor=blue]{org-article}
+\documentclass[koma,a4paper,utopia,12pt,listings-color,microtype,paralist,colorlinks,urlcolor=red]{org-article}
                \usepackage{tikz}
@@
 \newcommand*{\titleCM}{\begingroup
-\vspace*{\drop}
 \begin{center}
 \vspace{\baselineskip}
-{\Huge \textbf{Drawing Graphs Using TikZ in Emacs Org} \par}
+{\Huge \textbf {Drawing Graphs Using TikZ in Emacs Org} \par}
 \vspace{2\baselineskip}   \newline
@@
 \vspace{\baselineskip}
-{\Large WWW.MAKESTEAMCLEAR.COM \par}\newline
+{\Large \href{WWW.MAKESTEAMCLEAR.COM}{WWW.MAKESTEAMCLEAR.COM} \par}\newline
 \vspace{\baselineskip}
 {\texttt www.makesteamclear.com is a free project, supported by Eason Zhang, to make videos about STEAM in a more approachable and different way.
-If you found the contents in this post or the site or the youtube channel helpful, please consider support me, thanks \par}
+If you found the contents in this post or the site or the youtube channel helpful, please consider \href{www.makesteamclear.com}{support me}, thanks \par}
 \end{center}
-\vspace*{\drop}
 \endgroup}
@@
 \section{Drawing a TikZ picture in Emacs Org Mode}
-\label{sec:org8d51a0b}
+\label{sec:org9b89783}
 
@@
 \draw (0,-1.5) -- (0,1.5);
-\filldraw[fill = green!20, draw = green!50!black] (0,0) circle[radius = 1cm];
+\filldraw[fill = green!20, draw = green!50!black]
+                       (0,0) circle[radius = 1cm];
+\draw[help lines,very thin,step=.5cm,color=gray]
+                       (-1.5,-1.5) grid (1.5,1.5);
 \draw (0,0) rectangle (.5,.5);
 \draw (0,0) rectangle (-0.5,-0.5);
-\draw[help lines,very thin,step=.5cm,color=gray] (-1.5,-1.5) grid (1.5,1.5);
 % relative coordinate
@@
 \begin{enumerate}
-\item In \hyperref[a-minimum-working-example]{the minimum working example} line 12 , a path is named  without drawing
+\item In \hyperref[a-minimum-working-example]{the minimum working example} line 14 , a path is named  without drawing
 it.
-\item Line 16 gives an example of using library \texttt{intersections}. Note
+\item Line 18 gives an example of using library \texttt{intersections}. Note
 that you need to add the library using \texttt{\textbackslash{}usetikzlibrary\{intersections\}}
 otherwise an error occurs during \LaTeX compiling.
-\item Line 18 and 19 gives an example of using arrow. To make it work,
+\item Line 20 and 21 gives an example of using arrow. To make it work,
 \texttt{\textbackslash{}usetikzlibrary\{arrows.meta\}} is needed. The library \texttt{arrows.meta} provides tons
 of types of arrows whick shock me when I see them the first time.
-\item Line 21 to 24 gives an example of \texttt{scope} . In the environment, all
+\item Line 23 to 26 gives an example of \texttt{scope} . In the environment, all
 the lines are drawn in the \texttt{very thick} style.
-\item Line 26 to 29 gives an examplt of \texttt{foreach} . \texttt{foreach} is handy
+\item Line 28 to 31 gives an examplt of \texttt{foreach} . \texttt{foreach} is handy
 when you want to draw a list of objects. In \hyperref[a-minimum-working-example]{the minimum working example} , I
 draw a list of short red sticks along with the x-axis and y-axis.
-\item Line 31 is an example of \texttt{node}. The keyword \texttt{node} is typically followed by
+\item Line 33 is an example of \texttt{node}. The keyword \texttt{node} is typically followed by
 some options between \texttt{[]} and then some text between \texttt{\{\}}. Every node has flexible
@@
 \section{Another Example}
-\label{sec:orgc5e5c7a}
+\label{sec:org9260ef3}
 
@@
 \section{Some Basic Rules in TikZ}
-\label{sec:org171b856}
+\label{sec:org628b561}
 
@@
 \section{Some tips for in TikZ}
-\label{sec:org46592f8}
+\label{sec:org924da02}
 

### 2019-12-14 mstemc/index.tex
add one post

--- 2019-12-11 mstemc/index.tex
@@
-% Intended LaTeX compiler: xelatex
-\documentclass[koma,utopia,a4paper,captions=tableheading,11pt,listings-sv,microtype,paralist,colorlinks=true,urlcolor=blue]{org-article}
+% Intended LaTeX compiler: pdflatex
+\documentclass[koma,a4paper,utopia,12pt,listings-color,microtype,paralist,colorlinks,urlcolor=red]{org-article}
+                  \usetikzlibrary{arrows,decorations.pathmorphing}
+                  \usetikzlibrary{backgrounds,positioning,fit,petri}
                \usepackage{tikz}
@@
 \date{\today}
-\title{Drawing Graphs Using TikZ in Emacs Org}
+\title{Walk Through the Petri-Net In TiKZ Tutorial}
 \hypersetup{
  pdfauthor={Eason},
- pdftitle={Drawing Graphs Using TikZ in Emacs Org},
+ pdftitle={Walk Through the Petri-Net In TiKZ Tutorial},
  pdfkeywords={},
- pdfsubject={This post collects working examples of drawing graphs using TikZ in Emacs Org},
+ pdfsubject={Analyze the Petri-Net tutorial in Chapter 3 of the TikZ manual line by line.},
  pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
@@
 
-\maketitle
+\newcommand*{\titleCM}{\begingroup
+\begin{center}
+\vspace{\baselineskip}
+{\Huge \textbf {Walk Through the Petri-Net In TiKZ Tutorial} \par}
+\vspace{2\baselineskip}   \newline
+{\large Eason Zhang with www.makesteamclear.com \par}
+\vspace{\baselineskip}          \newline
+{\large \today \par}
+\vspace{\baselineskip}
+\vfill
+\setlength{\unitlength}{3pt}
+\makebox[\textwidth][c]{\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/example3.pdf}}
+\vfill
+\vspace{\baselineskip}
+{\Large \href{WWW.MAKESTEAMCLEAR.COM}{WWW.MAKESTEAMCLEAR.COM} \par}\newline
+\vspace{\baselineskip}
+{\texttt www.makesteamclear.com is a free project, supported by Eason Zhang, to make videos about STEAM in a more approachable and different way.
+If you found the contents in this post or the site or the youtube channel helpful, please consider \href{www.makesteamclear.com}{support me}, thanks \par}
+\end{center}
+\endgroup}
+\begin{titlepage}
+\titleCM
+\end{titlepage}
 \tableofcontents
 
-Draw a graph using TikZ
-
-[[file:~/Dropbox/mstemc_hugo/static/img/tikz/example.pdf]]
+Chapter 3 of the TikZ tutorial gives an example of Petri net. In this post, let
+me work through the code line by line. During this example, more tikz libraries
+are used, such as \texttt{arrows} , \texttt{decorations.pathmorphing} , \texttt{backgrounds} ,
+\texttt{positioning} , \texttt{fit}, \texttt{petri} . These libraries should be added before the
+\texttt{tikzpicture} environment.
 
 \begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/example.pdf}
-\end{center}
-
-\begin{center}
-\includegraphics[width=0.7\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/example1.pdf}
-\end{center}
-
-\begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/basiclayer.pdf}
+\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/petrinet.pdf}
 \end{center}

### 2019-12-15 mstemc/index.tex
use the org-macro to add the titlepage
which is handy to set the image in the front page. Also use the org macro I also
can set the copyright page.

@@
 \documentclass[koma,a4paper,utopia,12pt,listings-color,microtype,paralist,colorlinks,urlcolor=red]{org-article}
+       \usepackage{tikz}
        \usetikzlibrary{arrows,decorations.pathmorphing}
@@
 \date{\today}
-\title{Walk Through the Petri-Net In TiKZ Tutorial}
+\title{Set up the TikZ in Emacs Org}
 \hypersetup{
  pdfauthor={Eason},
- pdftitle={Walk Through the Petri-Net In TiKZ Tutorial},
+ pdftitle={Set up the TikZ in Emacs Org},
  pdfkeywords={},
- pdfsubject={Analyze the Petri-Net tutorial in Chapter 3 of the TikZ manual line by line.},
+ pdfsubject={An introduction to setup the TikZ environment in Emacs Org File.
+So that in Org file, you can generate either vector graph of \texttt{pdf}  format or raster graph of \texttt{png} format.
+Furthermore, you can export the vector graph when latex is called and otherwise raster graph.},
  pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
@@
 
-\newcommand*{\titleCM}{\begingroup
+ \begingroup
 \begin{center}
  \vspace{\baselineskip}
-{\Huge \textbf {Walk Through the Petri-Net In TiKZ Tutorial} \par}
+ \textbf{\Huge Walk Through the Petri-Net In TiKZ Tutorial} \par
  \vspace{2\baselineskip}  \newline
-{\large Eason Zhang with www.makesteamclear.com \par}
+ \textbf{\large Eason Zhang with www.makesteamclear.com \par}
  \vspace{\baselineskip} \newline
-{\large \today \par}
+  \today \par
  \vspace{\baselineskip}
@@
  \setlength{\unitlength}{3pt}
-\makebox[\textwidth][c]{\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/example3.pdf}}
-\vfill
-\vspace{\baselineskip}
-{\Large \href{WWW.MAKESTEAMCLEAR.COM}{WWW.MAKESTEAMCLEAR.COM} \par}\newline
-\vspace{\baselineskip}
-{\texttt www.makesteamclear.com is a free project, supported by Eason Zhang, to make videos about STEAM in a more approachable and different way.
-If you found the contents in this post or the site or the youtube channel helpful, please consider \href{www.makesteamclear.com}{support me}, thanks \par}
+ \includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/petrinetfinal.pdf}
+ \vfill \vspace{\baselineskip}
+ \href{WWW.MAKESTEAMCLEAR.COM}{\Large WWW.MAKESTEAMCLEAR.COM} \par\newline
+  makesteamclear is a free project, run by Eason Zhang, to make videos about STEAM in a more approachable way.
+If you find the contents in this article or the site or the youtube channel helpful, please consider \href{www.makesteamclear.com}{support me}, thanks \par
  \end{center}
-\endgroup}
-\begin{titlepage}
-\titleCM
-\end{titlepage}
-\tableofcontents
+ \endgroup
 
-Chapter 3 of the TikZ tutorial gives an example of Petri net. In this post, let
-me work through the code line by line. During this example, more tikz libraries
-are used, such as \texttt{arrows} , \texttt{decorations.pathmorphing} , \texttt{backgrounds} ,
-\texttt{positioning} , \texttt{fit}, \texttt{petri} . These libraries should be added before the
-\texttt{tikzpicture} environment.
+ \newpage \textbf{copyright page} \newpage \tableofcontents \newpage
 
-\begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/petrinet.pdf}
-\end{center}
+\hspace{0pt}\\
+
+An introduction to setup the TikZ environment in Emacs Org File.
+So that in Org file, you can generate either vector graph of \texttt{pdf}  format or raster graph of \texttt{png} format.
+Furthermore, you can export the vector graph when latex is called and otherwise raster graph.
+
+\section{config the header args}
+\label{sec:orga783c72}
+
+You can embed TiKz (One of \(\LaTeX\) graphic package) code into a Org file. With
+org-babel, you can generate ,insert and export the figure generated from Tikz
+package. At first, you need set up the environment. \href{https://orgmode.org/worg/org-contrib/babel/languages/ob-doc-LaTeX.html}{This Post} serves as a good
+introduction for beginners. Following it you may have a minimum working example
+like below:
+
+\begin{verbatim}
+#+name: tutorial
+#+header: :file "~/Dropbox/mstemc_hugo/static/img/tikz/tutorial.png"
+#+header: :results raw :exports none :fit yes :border 0cm
+#+header: :imagemagick t :iminoptions -density 400
+#+header: :imoutoptions -geometry 400 -flatten
+#+header: :headers '("\\usepackage{tikz} \\usetikzlibrary{positioning,
+           shapes.symbols, calc}")
+#+begin_src latex
+  \begin{tikzpicture}
+    \node [circle, draw, fill=red!20] at (0,0) {1}
+    child { node [circle, draw, fill=blue!30] {2}
+      child { node [circle, draw, fill=green!30] {3} }
+      child { node [circle, draw, fill=yellow!30] {4} }};
+  \end{tikzpicture}
+#+end_src
+#+RESULTS: tutorial
+[[file:../../img/tikz/tutorial.png]]
+\end{verbatim}
+
+The example begins with several lines containing \texttt{\#+header} which is sort of
+clutter. we can put them in a file and include it at the beginning of the Org
+file.
+\section{generate results with different formats}
+\label{sec:org39c9b75}
+
+By changing the extension of \texttt{:file} (which is \texttt{pdf} for
+\texttt{"../../img/tikz/tutorial.pdf"} ), we can generate results with different formats.
+Now, I need \texttt{pdf} and \texttt{png} . You can see the result by just press \texttt{C-c C-c} in the
+body of the tikz code.
+\section{export the results according to the backend}
+\label{sec:org58238bf}
+
+You can set \texttt{:exports} to control how the results will be exported. Now I set it
+as \texttt{none} which means the result will not be exported to latex or other format. I
+want to set more options of the exports. So I use:
+
+\begin{verbatim}
+#+ATTR_HTML:  :width 800 :align center
+#+ATTR_LATEX: :width 0.8\textwidth :align center
+{{{if-latex(tutorial.pdf,tutorial.png)}}}
+\end{verbatim}
+
+\texttt{if-latex} is a Org MACRO whose definition is :
+\begin{verbatim}
+#+MACRO: if-latex (eval (if
+(org-export-derived-backend-p org-export-current-backend 'latex)
+ (concat "[[file:../../img/tikz/"  $1 "]]")
+ (concat "[[file:../../img/tikz/"  $2 "]]") ))
+\end{verbatim}
+
+The \texttt{if-latex} MACRO let you export different formats by the backend. If the
+backend is \texttt{latex} then, \texttt{pdf} format figure will be exported. Otherwise, \texttt{png} format
+figure. Eventually, in the final \texttt{pdf} document, you figure can be zoomed in or
+out without losing any resolution.
+
+\section{the final workflow}
+\label{sec:org0400fae}
+
+The minimum working example at the start of this post is simplifed as below.
+
+\begin{verbatim}
+#+header: :file  "../../img/tikz/tutorial.pdf"
+#+begin_src latex
+  \begin{tikzpicture}
+    \node [circle, draw, fill=red!20] at (0,0) {1}
+    child { node [circle, draw, fill=blue!30] {2}
+      child { node [circle, draw, fill=green!30] {3} }
+      child { node [circle, draw, fill=yellow!30] {4} }};
+  \end{tikzpicture}
+#+end_src
+
+#+RESULTS:
+[[file:../../img/tikz/tutorial.png]]
+
+The following is the generated figure.
+#+ATTR_HTML:  :width 800 :align center
+#+ATTR_LATEX: :width 0.8\textwidth :align center
+{{{if-latex(tutorial.pdf,tutorial.png)}}}
+\end{verbatim}
+
+Many settings are grouped into a setup file which is included at the top of this
+post:
+\begin{verbatim}
+#+SETUPFILE: ~/.spacemacs.d/org-templates/math-en.org
+\end{verbatim}
+
+Now, If you set the extension of the target file in the first line either \texttt{pdf} or
+\texttt{png} , a corresponding \texttt{pdf} or \texttt{png} figure will be generated. If execute \texttt{M-x
+org-toggle-inline-images}  , you can preview the result. If export the org-file
+as latex file then the \texttt{pdf} file, the image of \texttt{pdf} format will be inserted. If
+export to other format, \texttt{png} image will be used.
 \end{document}

### 2019-12-15 mstemc/mstemc.tex
use the org-macro to add the titlepage
which is handy to set the image in the front page. Also use the org macro I also
can set the copyright page.

@@
-% Intended LaTeX compiler: pdflatex
-\documentclass[koma,utopia,a4paper,captions=tableheading,11pt,listings-sv,microtype,paralist,colorlinks=true,urlcolor=blue]{org-article}
-               \usepackage{tikz}
-\author{Eason}
-\date{\today}
-\title{make STEAM clear}
-\hypersetup{
- pdfauthor={Eason},
- pdftitle={make STEAM clear},
- pdfkeywords={},
- pdfsubject={},
- pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
- pdflang={English}}
-\begin{document}
-
-\newcommand*{\titleCM}{\begingroup
-\vspace*{\drop}
-\begin{center}
-\vspace{\baselineskip}
-{\Huge \textbf{make STEAM clear} \par}
-\vspace{2\baselineskip}   \newline
-{\large Eason Zhang with www.makesteamclear.com \par}
-\vspace{\baselineskip}          \newline
-{\large \today \par}
-\vspace{\baselineskip}
-\vfill
-\setlength{\unitlength}{3pt}
-\makebox[\textwidth][c]{\includegraphics[width=0.2\textwidth]{\~/Dropbox/mstemc_hugo/static/img/tikz/example3.pdf}}
-\vfill
-\vspace{\baselineskip}
-{\Large WWW.MAKESTEAMCLEAR.COM \par}\newline
-\vspace{\baselineskip}
-{\texttt www.makesteamclear.com is a free project, supported by Eason Zhang, to make videos about STEAM in a more approachable and different way.
-If you found the contents in this post or the site or the youtube channel helpful, please consider support me, thanks \par}
-\end{center}
-\vspace*{\drop}
-\endgroup}
-\begin{titlepage}
-\titleCM
-\end{titlepage}
-\tableofcontents
-
 \section{Videos}
-\label{sec:orge61aa3c}
+\label{sec:org1f1f886}
 
 \section{Posts}
-\label{sec:orgcd8829e}
+\label{sec:org33c9a58}
 
 \subsection{Set up the TikZ in Emacs Org}
-\label{sec:org7c6689e}
+\label{sec:org9a1a1dd}
 \hspace{0pt}\\
@@
 \subsubsection{config the header args}
-\label{sec:org8a24a77}
+\label{sec:orgf59efeb}
 
@@
 \subsubsection{generate results with different formats}
-\label{sec:org05b6333}
+\label{sec:orgebb7e4e}
 
@@
 \subsubsection{export the results according to the backend}
-\label{sec:orgff78033}
+\label{sec:org3858655}
 
@@
 \subsubsection{the final workflow}
-\label{sec:orga6d2484}
+\label{sec:org2af511e}
 
@@
 \subsection{Export Markdown and latex using Emacs Org}
-\label{sec:orgd6fe22f}
+\label{sec:orgf87a4ad}
 
@@
 \subsubsection{Introduction}
-\label{sec:orgd478c4d}
+\label{sec:orgb9aacc7}
 
@@
 \subsubsection{set up ox-hugo}
-\label{sec:org76b6cf4}
+\label{sec:org0a52bcd}
 
@@
 \subsubsection{use Org Macro replacement}
-\label{sec:orga32c0f1}
+\label{sec:orgaa4e7a2}
 
@@
 \subsubsection{use the setupfile for each Org file}
-\label{sec:org589cab1}
+\label{sec:orgd15a7e2}
 
@@
 \subsection{Drawing Graphs Using TikZ in Emacs Org}
-\label{sec:org220de70}
+\label{sec:org5bc49d6}
 
 \subsubsection{Drawing a TikZ picture in Emacs Org Mode}
-\label{sec:orgd491791}
+\label{sec:org8506b3a}
 
@@
 \filldraw[fill = green!20, draw = green!50!black] (0,0) circle[radius = 1cm];
+\draw[help lines,very thin,step=.5cm,color=gray] (-1.5,-1.5) grid (1.5,1.5);
 \draw (0,0) rectangle (.5,.5);
 \draw (0,0) rectangle (-0.5,-0.5);
-\draw[help lines,very thin,step=.5cm,color=gray] (-1.5,-1.5) grid (1.5,1.5);
 % relative coordinate
@@
 \subsubsection{Another Example}
-\label{sec:orgbc1168b}
+\label{sec:org85bdcaf}
 
@@
 \subsubsection{Some Basic Rules in TikZ}
-\label{sec:orgdb48b38}
+\label{sec:orge995912}
 
@@
 \subsubsection{Some tips for in TikZ}
-\label{sec:org8e92c4c}
+\label{sec:org742f086}
 
@@
 
-\lstset{language=C,label= ,caption= ,captionpos=b,numbers=none}
+\lstset{language=C,label= ,caption= ,captionpos=b,firstnumber=1,numbers=left}
 \begin{lstlisting}
@@
 
+\subsection{Walk Through the Petri-Net In TiKZ Tutorial}
+\label{sec:orgfaa8657}
+
+\bigin{titlepage}
+ \begingroup
+\begin{center}
+ \vspace{\baselineskip}
+ \textbf{\Huge Walk Through the Petri-Net In TiKZ Tutorial} \par
+ \vspace{2\baselineskip}  \newline
+ \textbf{\large Eason Zhang with www.makesteamclear.com \par}
+ \vspace{\baselineskip}          \newline
+  \today \par
+ \vspace{\baselineskip}
+  \vfill
+ \setlength{\unitlength}{3pt}
+ \includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/example3.pdf}
+ \vfill \vspace{\baselineskip}
+ \href{WWW.MAKESTEAMCLEAR.COM}{\Large WWW.MAKESTEAMCLEAR.COM} \par\newline
+  www.makesteamclear.com is a free project, supported by Eason Zhang, to make videos about STEAM in a more approachable and different way.
+If you found the contents in this post or the site or the youtube channel helpful, please consider \href{www.makesteamclear.com}{support me}, thanks \par
+ \end{center}
+\endgroup
+\end{titlepage}
+\newpage
+
+Chapter 3 of the TikZ tutorial gives an example of Petri net. In this post, let
+me work through the code line by line. During this example, more tikz libraries
+are used, such as \texttt{arrows} , \texttt{decorations.pathmorphing} , \texttt{backgrounds} ,
+\texttt{positioning} , \texttt{fit}, \texttt{petri} . These libraries should be added before the
+\texttt{tikzpicture} environment.
+
+\begin{center}
+\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/petrinet.pdf}
+\end{center}
+
 \section{Projects}
-\label{sec:org92a94e0}
+\label{sec:orgaf97de2}
 
 \subsection{my workflow of creating a video}
-\label{sec:orga6b7968}
+\label{sec:org45aac98}
 \hspace{0pt}\\
@@
 \subsubsection{Emacs}
-\label{sec:org9c05b58}
+\label{sec:orgcb16fe3}
 
@@
 \item program and debug
-\label{sec:orge66ddd0}
+\label{sec:orgbe5b8cf}
 
@@
 \item Org mode - journalize your work
-\label{sec:org108dfd7}
+\label{sec:org5077380}
 
@@
 \item Org mode - get things done
-\label{sec:orgb5f62bc}
+\label{sec:org0286871}
 
 \item Org mode - write a diary
-\label{sec:org168bbcf}
+\label{sec:org2d64073}
 
 \item Org mode - export your Org file
-\label{sec:orgce77f24}
+\label{sec:orgbd13d0c}
 
 \item program and debug
-\label{sec:org6b73797}
+\label{sec:org53b4991}
 
 \item writing latex
-\label{sec:orgf96355a}
+\label{sec:orgce5ad4a}
 \item org-journal
-\label{sec:orgc17cd60}
+\label{sec:orgb58b60d}
 
@@
 \item ox-hugo
-\label{sec:org9e07d00}
+\label{sec:org7fc8972}
 
@@
 \item preview tikz picture in Org
-\label{sec:orgab2630d}
+\label{sec:org697542b}
 
@@
 \subsubsection{Hugo}
-\label{sec:org3f30c08}
+\label{sec:org7cb7cf9}
 
@@
 \subsubsection{Hugo Academic Theme}
-\label{sec:orgad8a7d5}
+\label{sec:org8323bc3}
 
@@
 \subsubsection{manim}
-\label{sec:org022fb8d}
+\label{sec:org00574e3}
 
 \subsubsection{blender}
-\label{sec:org7659274}
+\label{sec:orgbef2b43}
 
 \section{Courses}
-\label{sec:org85ca59f}
-\end{document}
+\label{sec:orgeb1cbcd}

### 2019-12-16 mstemc/index.tex
trivial udpate

--- 2019-12-14 mstemc/index.tex
@@
 
-\newcommand*{\titleCM}{\begingroup
+ \thispagestyle{empty}
+ \begingroup
 \begin{center}
  \vspace{\baselineskip}
-{\Huge \textbf {Walk Through the Petri-Net In TiKZ Tutorial} \par}
+ \textbf{\Huge Walk Through the Petri-Net In TiKZ Tutorial} \par
  \vspace{2\baselineskip}  \newline
-{\large Eason Zhang with www.makesteamclear.com \par}
+ \textbf{\large Eason Zhang with www.makesteamclear.com \par}
  \vspace{\baselineskip} \newline
-{\large \today \par}
+  \today \par
  \vspace{\baselineskip}
@@
  \setlength{\unitlength}{3pt}
-\makebox[\textwidth][c]{\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/example3.pdf}}
-\vfill
-\vspace{\baselineskip}
-{\Large \href{WWW.MAKESTEAMCLEAR.COM}{WWW.MAKESTEAMCLEAR.COM} \par}\newline
-\vspace{\baselineskip}
-{\texttt www.makesteamclear.com is a free project, supported by Eason Zhang, to make videos about STEAM in a more approachable and different way.
-If you found the contents in this post or the site or the youtube channel helpful, please consider \href{www.makesteamclear.com}{support me}, thanks \par}
+ \includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/petrinetfinal.pdf}
+ \vfill \vspace{\baselineskip}
+ \href{WWW.MAKESTEAMCLEAR.COM}{\Large WWW.MAKESTEAMCLEAR.COM} \par\newline
+  makesteamclear is a free project, run by Eason Zhang, to make videos about STEAM in a more approachable way.
+If you find the contents in this article or the site or the youtube channel helpful, please consider \href{www.makesteamclear.com}{\ensuremath \heartsuit support me\ensuremath\heartsuit }, thanks \par
  \end{center}
-\endgroup}
-\begin{titlepage}
-\titleCM
-\end{titlepage}
-\tableofcontents
+ \endgroup
+
+ \newpage \thispagestyle{empty} \textbf{copyright page} \newpage \tableofcontents \newpage
+\hspace{0pt}\\
+
+Analyze the Petri-Net tutorial in Chapter 3 of the TikZ manual line by line.
 
@@
 \end{center}
+
+The code is shown as
+\lstset{language=[LaTeX]TeX,label= ,caption= ,captionpos=b,firstnumber=1,numbers=left}
+\begin{lstlisting}
+\begin{tikzpicture}
+  [node distance=1.3cm,on grid,>=stealth',bend angle=45,auto,
+  every place/.style= {minimum size=6mm,thick,draw=blue!75,fill=blue!20},
+  every transition/.style={thick,draw=black!75,fill=black!20},
+  red place/.style= {place,draw=red!75,fill=red!20},
+  every label/.style= {blue}]
+  \node [place,tokens=1] (w1) {};
+  \node [place] (c1) [below=of w1] {};
+  \node [place] (s) [below=of c1,label=above:$s\le 3$] {};
+  \node [place] (c2) [below=of s] {};
+  \node [place,tokens=1] (w2) [below=of c2] {};
+  \node [transition] (e1) [left=of c1] {}
+  edge [pre,bend left] (w1)
+  edge [post,bend right] (s)
+  edge [post] (c1);
+  \node [transition] (e2) [left=of c2] {}
+  edge [pre,bend right] (w2)
+  edge [post,bend left] (s)
+  edge [post] (c2);
+  \node [transition] (l1) [right=of c1] {}
+  edge [pre] (c1)
+  edge [pre,bend left] (s)
+  edge [post,bend right] node[swap] {2} (w1);
+  \node [transition] (l2) [right=of c2] {}
+  edge [pre] (c2)
+  edge [pre,bend right] (s)
+  edge [post,bend left] node {2} (w2);
+
+  \begin{scope}[xshift=6cm]
+    \node [place,tokens=1] (w1') {};
+    \node [place] (c1') [below=of w1'] {};
+    \node [red place] (s1') [below=of c1',xshift=-5mm]
+    [label=left:$s$] {};
+    \node [red place,tokens=3] (s2') [below=of c1',xshift=5mm]
+    [label=right:$\bar s$] {};
+    \node [place] (c2') [below=of s1',xshift=5mm] {};
+    \node [place,tokens=1] (w2') [below=of c2'] {};
+    \node [transition] (e1') [left=of c1'] {}
+    edge [pre,bend left] (w1')
+    edge [post] (s1')
+    edge [pre] (s2')
+    edge [post] (c1');
+    \node [transition] (e2') [left=of c2'] {}
+    edge [pre,bend right] (w2')
+    edge [post] (s1')
+    edge [pre] (s2')
+    edge [post] (c2');
+    \node [transition] (l1') [right=of c1'] {}
+    edge [pre] (c1')
+    edge [pre] (s1')
+    edge [post] (s2')
+    edge [post,bend right] node[swap] {2} (w1');
+    \node [transition] (l2') [right=of c2'] {}
+    edge [pre] (c2')
+    edge [pre] (s1')
+    edge [post] (s2')
+    edge [post,bend left] node {2} (w2');
+  \end{scope}
+  \begin{scope}[on background layer]
+    \node (r1) [fill=black!10,rounded corners,fit=(w1)(w2)(e1)(e2)(l1)(l2)] {};
+    \node (r2) [fill=black!10,rounded corners,fit=(w1')(w2')(e1')(e2')(l1')(l2')] {};
+  \end{scope}
+  \draw [shorten >=1mm,-to,thick,decorate,
+  decoration={snake,amplitude=.4mm,segment length=2mm,
+    pre=moveto,pre length=1mm,post length=2mm}]
+  (r1) -- (r2) node [above=1mm,midway,text width=3cm,align=center]
+  {replacement of the \textcolor{red}{capacity} by \textcolor{red}{two places}};
+\end{tikzpicture}
+\end{lstlisting}
 \end{document}

### 2019-12-18 mstemc/index.tex
trivial update

--- 2019-12-14 mstemc/index.tex
@@
 \end{center}
+
+\begin{theo}
+\label{thm1} \ref{thm1}
+  this is a theorem.
+\end{theo}
+
+This is \ref{thm1}
 \end{document}

### 2019-12-19 mstemc/index.tex
trivial modifications about mstemc.org

@@
 \date{\today}
-\title{Walk Through the Petri-Net In TiKZ Tutorial}
+\title{Walk Through the Tutorial 4 of TikZ Manual}
 \hypersetup{
  pdfauthor={Eason},
- pdftitle={Walk Through the Petri-Net In TiKZ Tutorial},
+ pdftitle={Walk Through the Tutorial 4 of TikZ Manual},
  pdfkeywords={},
- pdfsubject={Analyze the Petri-Net tutorial in Chapter 3 of the TikZ manual line by line.},
+ pdfsubject={Analyze the Elements Example in Chapter 3 of the TikZ manual line by line.},
  pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
@@
  \vspace{\baselineskip}
- \textbf{\Huge Walk Through the Petri-Net In TiKZ Tutorial} \par
+ \textbf{\Huge Walk Through the Tutorial 4 of TikZ Manual} \par
  \vspace{2\baselineskip}  \newline
@@
  \setlength{\unitlength}{3pt}
- \includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/petrinetfinal.pdf}
+ \includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/elements.pdf}
  \vfill \vspace{\baselineskip}
@@
 
-Analyze the Petri-Net tutorial in Chapter 3 of the TikZ manual line by line.
+Analyze the Elements Example in Chapter 3 of the TikZ manual line by line.
 
-Chapter 3 of the TikZ tutorial gives an example of Petri net. In this post, let
-me work through the code line by line. During this example, more tikz libraries
-are used, such as \texttt{arrows} , \texttt{decorations.pathmorphing} , \texttt{backgrounds} ,
-\texttt{positioning} , \texttt{fit}, \texttt{petri} . These libraries should be added before the
-\texttt{tikzpicture} environment.
+\lstset{language=[LaTeX]TeX,label=Euclid Amber version of the Elements,caption={Euclid Amber version of the Elements},captionpos=b,firstnumber=1,numbers=left}
+\begin{lstlisting}
+\begin{tikzpicture}
+  [thick,help lines/.style={thin,draw=black!50}]
+  \def\A{\textcolor{input}{$A$}}
+  \def\B{\textcolor{input}{$B$}}
+  \def\C{\textcolor{output}{$C$}}
+  \def\D{$D$}
+  \def\E{$E$}
+
+  \colorlet{input}{blue!80!black}
+  \colorlet{output}{red!70!black}
+  \colorlet{triangle}{orange}
+
+  \coordinate [label=left:\A] (A) at ($(0,0) + .0*(rand,rand)$);
+  \coordinate [label=right:\B] (B) at ($(1.25,0.25) + .0*(rand,rand)$);
+
+  \draw [input] (A) -- (B);
+
+  \node [name path=D,help lines,draw,label=left:\D] (D) at (A) [circle through = (B)] {};
+  \node [name path=E,help lines,draw,label=right:\E] (E) at (B) [circle through = (A)] {};
+
+  \path [name intersections = {of =D and E, by={[label=above:\C]C}}];
+  \draw [output] (A) -- (C) -- (B);
+
+  \foreach \point in {A,B,C}
+  \fill[black,opacity=.5] (\point) circle (2pt);
+  \begin{pgfonlayer}{background}
+    \fill[triangle!80] (A) -- (C) -- (B) -- cycle;
+  \end{pgfonlayer}
+
+  % \node [below right, text width = 10cm,align = justify] at (4,3) {
+  %   \small\textbf{Proposition I} \par
+  %   \emph{To construct an \textcolor{triangle}{equilateral triangle}
+  %     on a given \textcolor{input}{finite straight line.}}
+  %   \par \vskip 1em
+  %   Let \A\B\ be the given \textcolor{input}{finite straight line}. \dots
+  % };
+
+\end{tikzpicture}
+\end{lstlisting}
 
 \begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/petrinet.pdf}
+\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/elements.pdf}
 \end{center}
-
-\begin{theo}
-\label{thm1} \ref{thm1}
-  this is a theorem.
-\end{theo}
-
-This is \ref{thm1}
 \end{document}

### 2019-12-22 mstemc/index.tex
trivial modification

--- 2019-12-18 mstemc/index.tex
@@
 \date{\today}
-\title{Walk Through the Petri-Net In TiKZ Tutorial}
+\title{Walk Through the Tutorial 5 of TikZ Manual}
 \hypersetup{
  pdfauthor={Eason},
- pdftitle={Walk Through the Petri-Net In TiKZ Tutorial},
+ pdftitle={Walk Through the Tutorial 5 of TikZ Manual},
  pdfkeywords={},
- pdfsubject={Analyze the Petri-Net tutorial in Chapter 3 of the TikZ manual line by line.},
+ pdfsubject={summary of this post},
  pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
@@
  \vspace{\baselineskip}
- \textbf{\Huge Walk Through the Petri-Net In TiKZ Tutorial} \par
+ \textbf{\Huge Walk Through the Tutorial 5 of TikZ Manual} \par
  \vspace{2\baselineskip}  \newline
@@
  \setlength{\unitlength}{3pt}
- \includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/petrinetfinal.pdf}
+ \includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/propositionII.pdf}
  \vfill \vspace{\baselineskip}
@@
 
-Analyze the Petri-Net tutorial in Chapter 3 of the TikZ manual line by line.
+summary of this post
 
-Chapter 3 of the TikZ tutorial gives an example of Petri net. In this post, let
-me work through the code line by line. During this example, more tikz libraries
-are used, such as \texttt{arrows} , \texttt{decorations.pathmorphing} , \texttt{backgrounds} ,
-\texttt{positioning} , \texttt{fit}, \texttt{petri} . These libraries should be added before the
-\texttt{tikzpicture} environment.
-
-\begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/petrinet.pdf}
-\end{center}
-
-\begin{theo}
-\label{thm1} \ref{thm1}
-  this is a theorem.
-\end{theo}
-
-This is \ref{thm1}
+This is the tutorial 5 from chapter 5 of the TikZ manual.
 \end{document}

### 2019-12-22 mstemc/index.tex
the lecture map is OK and I am pretty satisfied with it

--- 2019-12-19 mstemc/index.tex
@@
-% Intended LaTeX compiler: pdflatex
+% Intended LaTeX compiler: lualatex
 \documentclass[koma,a4paper,utopia,12pt,listings-color,microtype,paralist,colorlinks,urlcolor=red]{org-article}
 \usepackage{tikz}
-       \usetikzlibrary{arrows,decorations.pathmorphing}
-       \usetikzlibrary{backgrounds,positioning,fit,petri}
+\usetikzlibrary{arrows,decorations.pathmorphing,,backgrounds,positioning,fit,petri,calc,intersections,through,shapes.misc,mindmap,calendar,shadows,mindmap,calendar,graphdrawing,trees}
                \usepackage{tikz}
@@
 \end{center}
+\section{Proposition II}
+\label{sec:org3b99d67}
+
+\begin{center}
+\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/propositionII.pdf}
+\end{center}
+\section{A Lecture Map Tutorial}
+\label{sec:orgfae8e2b}
+
+\begin{center}
+\includegraphics[width=0.9\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/lecturemap.pdf}
+\end{center}
 \end{document}

### 2019-12-23 mstemc/index.tex
trivial modification

--- 2019-12-22 mstemc/index.tex
@@
  \setlength{\unitlength}{3pt}
- \includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/propositionII.pdf}
+ \includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/diagram.pdf}
  \vfill \vspace{\baselineskip}
@@
 
-This is the tutorial 5 from chapter 5 of the TikZ manual.
+\begin{center}
+\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/diagram.pdf}
+\end{center}
 \end{document}

### 2020-01-08 mstemc/index.tex
latex enviroment: theo, lem, prf, prob, solu work well
add the problem 1.1 and problem 1.2

@@
 \date{\today}
-\title{Walk Through the Tutorial 5 of TikZ Manual}
+\title{signals and systems chapter 1 problems}
 \hypersetup{
  pdfauthor={Eason},
- pdftitle={Walk Through the Tutorial 5 of TikZ Manual},
+ pdftitle={signals and systems chapter 1 problems},
  pdfkeywords={},
@@
  \vspace{\baselineskip}
- \textbf{\Huge Walk Through the Tutorial 5 of TikZ Manual} \par
+ \textbf{\Huge signal and system chapter 1 problems} \par
  \vspace{2\baselineskip}  \newline
@@
  \setlength{\unitlength}{3pt}
- \includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/diagram.pdf}
+ \includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/eulerEquation.pdf}
  \vfill \vspace{\baselineskip}
@@
 summary of this post
+\section{Basic Problems With Answers}
+\label{sec:org8f261cc}
+
+\begin{prob}[]{prob:1.1}
+Express each of the following complex numbers in \emph{Cartesian} form \(x+iy\):
+\begin{equation*}
+\begin{array}
+\quad \frac{1}{2}e^{i\pi}  & \frac{1}{2}e^{-i\pi}  & e^{i\pi/2}  \\
+ e^{-i\pi/2}         & e^{i5\pi/2}  & \sqrt{2}e^{i\pi/4}  \\
+ \sqrt{2}e^{i9\pi/4} & \sqrt{2}e^{-9i\pi/4}  & \sqrt{2} e^{-i\pi/4}
+\end{array}
+\end{equation*}
+\label{prob:1.1}
+\end{prob}
+
+\begin{prob}[]{prob:1.2}
+Express each of the following complex numbers in \emph{polar} form (\(re^{i\theta},
+-\pi < \theta \leq -\pi\)): \(5\),\(-2\),\(-3i\),\(\frac{1}{2} -
+i\frac{\sqrt{3}}{2}\), \(1 + i\), \((1-i)^{2}\), \(i(1-i)\), \((1+i)/(1-i)\), \((\sqrt{2} +i\sqrt{2})/ (1 +i\sqrt{3})\)
+\label{prob:1.2}
+\end{prob}
+
+Every complex number \(a+ib\) can be visualized in the complex plane
+\(\mathbb{C}\). It can be viewed as the point with the coordinate \((a,b)\) in
+the plane or as a vector starting from \(0,0\) to the point \((a,b)\).
+
+Also every complex number \(a+ib\) can be represented in the exponential form
+conveniently through the Euler's formula \(e^{i\alpha} = \cos\alpha +
+i\sin\alpha\).
 
 \begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/diagram.pdf}
+\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/eulerEquation.pdf}
 \end{center}

### 2020-01-08 mstemc/mstemc.tex
add the problem 1.1 and problem 1.2

--- 2019-12-11 mstemc/mstemc.tex
@@
-% Intended LaTeX compiler: xelatex
-\documentclass[koma,a4paper,captions=tableheading,11pt,listings-sv,microtype,paralist,colorlinks=true,urlcolor=blue,palatino]{org-article}
+% Intended LaTeX compiler: lualatex
+\documentclass[koma,a4paper,utopia,12pt,listings-color,microtype,paralist,colorlinks,urlcolor=red]{org-article}
+\usepackage{tikz}
+\usetikzlibrary{arrows,decorations.pathmorphing,,backgrounds,positioning,fit,petri,calc,intersections,through,shapes.misc,mindmap,calendar,shadows,mindmap,calendar,graphdrawing,trees}
                \usepackage{tikz}
@@
 \date{\today}
-\title{make STEAM clear}
+\title{Basic Problems With Answers}
 \hypersetup{
  pdfauthor={Eason},
- pdftitle={make STEAM clear},
+ pdftitle={Basic Problems With Answers},
  pdfkeywords={},
@@
 
-\maketitle
-\tableofcontents
+\begin{prob}[]{prob:1.1}
+Express each of the following complex numbers in \emph{Cartesian} form \(x+iy\):
+\begin{equation*}
+\begin{array}{ccc}
+ \frac{1}{2}e^{i\pi}  & \frac{1}{2}e^{-i\pi}  & e^{i\pi/2}  \\
+ e^{-i\pi/2}         & e^{i5\pi/2}  & \sqrt{2}e^{i\pi/4}  \\
+ \sqrt{2}e^{i9\pi/4} & \sqrt{2}e^{-9i\pi/4}  & \sqrt{2} e^{-i\pi/4}
+\end{array}
+\end{equation*}
+\label{prob:1.1}
+\end{prob}
 
-\section{Videos}
-\label{sec:org80ec581}
+\begin{prob}[]{prob:1.2}
+Express each of the following complex numbers in \emph{polar} form (\(re^{i\theta},
+-\pi < \theta \leq -\pi\)):
+\begin{equation*}
+\begin{array}{c{3cm}c{3cm}c{3cm}}
+5 & -2 & -3i \\
+\frac{1}{2} - i \frac{\sqrt{3}}{2} & 1+i & (1-i)^{2} \\
+i(1-i)  & \frac{1+i}{1-i}  & \frac{\sqrt{2} + i \sqrt{2}}{1+i\sqrt{3}}
+\end{array}
+\end{equation*}
+\label{prob:1.2}
+\end{prob}
 
-\section{Posts}
-\label{sec:org275e087}
+Every complex number \(a+ib\) can be visualized in the complex plane
+\(\mathbb{C}\). It can be viewed as the point with the coordinate \((a,b)\) in
+the plane or as a vector starting from \(0,0\) to the point \((a,b)\).
 
-\subsection{Set up the TikZ in Emacs Org}
-\label{sec:org5387454}
-\hspace{0pt}\\
-
-An introduction to setup the TikZ environment in Emacs Org File.
-So that in Org file, you can generate either vector graph of \texttt{pdf}  format or raster graph of \texttt{png} format.
-Furthermore, you can export the vector graph when latex is called and otherwise raster graph.
-
-\subsubsection{config the header args}
-\label{sec:org3f3612a}
-
-You can embed TiKz (One of \(\LaTeX\) graphic package) code into a Org file. With
-org-babel, you can generate ,insert and export the figure generated from Tikz
-package. At first, you need set up the environment. \href{https://orgmode.org/worg/org-contrib/babel/languages/ob-doc-LaTeX.html}{This Post} serves as a good
-introduction for beginners. Following it you may have a minimum working example
-like below:
-
-\begin{verbatim}
-#+name: tutorial
-#+header: :file "~/Dropbox/mstemc_hugo/static/img/tikz/tutorial.png"
-#+header: :results raw :exports none :fit yes :border 0cm
-#+header: :imagemagick t :iminoptions -density 400
-#+header: :imoutoptions -geometry 400 -flatten
-#+header: :headers '("\\usepackage{tikz} \\usetikzlibrary{positioning,
-           shapes.symbols, calc}")
-#+begin_src latex
-  \begin{tikzpicture}
-    \node [circle, draw, fill=red!20] at (0,0) {1}
-    child { node [circle, draw, fill=blue!30] {2}
-      child { node [circle, draw, fill=green!30] {3} }
-      child { node [circle, draw, fill=yellow!30] {4} }};
-  \end{tikzpicture}
-#+end_src
-#+RESULTS: tutorial
-[[file:../../img/tikz/tutorial.png]]
-\end{verbatim}
-
-The example begins with several lines containing \texttt{\#+header} which is sort of
-clutter. we can put them in a file and include it at the beginning of the Org
-file.
-\subsubsection{generate results with different formats}
-\label{sec:orgac277d3}
-
-By changing the extension of \texttt{:file} (which is \texttt{pdf} for
-\texttt{"../../img/tikz/tutorial.pdf"} ), we can generate results with different formats.
-Now, I need \texttt{pdf} and \texttt{png} . You can see the result by just press \texttt{C-c C-c} in the
-body of the tikz code.
-\subsubsection{export the results according to the backend}
-\label{sec:org864fe62}
-
-You can set \texttt{:exports} to control how the results will be exported. Now I set it
-as \texttt{none} which means the result will not be exported to latex or other format. I
-want to set more options of the exports. So I use:
-
-\begin{verbatim}
-#+ATTR_HTML:  :width 800 :align center
-#+ATTR_LATEX: :width 0.8\textwidth :align center
-{{{if-latex(tutorial.pdf,tutorial.png)}}}
-\end{verbatim}
-
-\texttt{if-latex} is a Org MACRO whose definition is :
-\begin{verbatim}
-#+MACRO: if-latex (eval (if
-(org-export-derived-backend-p org-export-current-backend 'latex)
- (concat "[[file:../../img/tikz/"  $1 "]]")
- (concat "[[file:../../img/tikz/"  $2 "]]") ))
-\end{verbatim}
-
-The \texttt{if-latex} MACRO let you export different formats by the backend. If the
-backend is \texttt{latex} then, \texttt{pdf} format figure will be exported. Otherwise, \texttt{png} format
-figure. Eventually, in the final \texttt{pdf} document, you figure can be zoomed in or
-out without losing any resolution.
-
-\subsubsection{the final workflow}
-\label{sec:orgc26c788}
-
-The minimum working example at the start of this post is simplifed as below.
-
-\begin{verbatim}
-#+header: :file  "../../img/tikz/tutorial.pdf"
-#+begin_src latex
-  \begin{tikzpicture}
-    \node [circle, draw, fill=red!20] at (0,0) {1}
-    child { node [circle, draw, fill=blue!30] {2}
-      child { node [circle, draw, fill=green!30] {3} }
-      child { node [circle, draw, fill=yellow!30] {4} }};
-  \end{tikzpicture}
-#+end_src
-
-#+RESULTS:
-[[file:../../img/tikz/tutorial.png]]
-
-The following is the generated figure.
-#+ATTR_HTML:  :width 800 :align center
-#+ATTR_LATEX: :width 0.8\textwidth :align center
-{{{if-latex(tutorial.pdf,tutorial.png)}}}
-\end{verbatim}
-
-Many settings are grouped into a setup file which is included at the top of this
-post:
-\begin{verbatim}
-#+SETUPFILE: ~/.spacemacs.d/org-templates/math-en.org
-\end{verbatim}
-
-Now, If you set the extension of the target file in the first line either \texttt{pdf} or
-\texttt{png} , a corresponding \texttt{pdf} or \texttt{png} figure will be generated. If execute \texttt{M-x
-org-toggle-inline-images}  , you can preview the result. If export the org-file
-as latex file then the \texttt{pdf} file, the image of \texttt{pdf} format will be inserted. If
-export to other format, \texttt{png} image will be used.
-
-\subsection{Export Markdown and latex using Emacs Org}
-\label{sec:orgb25f912}
-
-\hspace{0pt}\\
-
-set up the Emacs org and ox-hugo to export the org files in markdown and latex format.
-
-\subsubsection{Introduction}
-\label{sec:org1a16d6f}
-
-I use hugo before it support Emacs org file. Then I use an Emacs extension
-called \href{https://github.com/kaushalmodi/ox-hugo}{ox-hugo} which is a carefully crafted Org exporter back-end for Hugo.
-Ox-hugo meets all my requirement and definitely worth a try when you are an
-advanced user of Emacs Org. By the way, if you are quite familiar with Emacs
-Org, there is no need to take time to learn markdown. Emacs Org, I think, is
-more elegant than markdown.
-
-\subsubsection{set up ox-hugo}
-\label{sec:org11a7de8}
-
-I use Spacemacs and integrate ox-hugo into my config is easy. You can add it
-into your private layer or just add it in your \texttt{user-config} . Please refer to
-\href{https://github.com/kaushalmodi/ox-hugo}{the repo.} and read the document for more information.
-
-The first time you want to export an Org file or a subtree of an Org file, use
-\texttt{M-x org-hugo-export-to-md} . There will be a hugo-related section in the
-\texttt{org-dispatcher} whenever you use \texttt{C-c C-e} .
-\subsubsection{use Org Macro replacement}
-\label{sec:orgf79a086}
-
-Often, you want different actions when you export the Org file to
-hugo-compatible markdown and latex file. For example, hugo or hugo theme supports
-summary and shortcodes such as \texttt{alert note} and \texttt{alert warning} (see  \href{https://sourcethemes.com/academic/docs/writing-markdown-latex/}{Writing
-content with Markdown, \LaTeX{}, and Shortcodes | Academic} )
-
-When you export the snippet to markdown then hugo will display the content
-according to the css. However, latex does not recognize the shortcodes. So latex
-will display \texttt{\{ \{\% alert note \%\} \}} literally which is clutter. The Org Macro may
-help. For more information please refer to \href{https://orgmode.org/manual/Macro-replacement.html}{The Org Manual: Macro replacement} and
-\href{https://github.com/fniessen/org-macros}{fniessen/org-macros: Shared macros for Org mode} . I also define my own Org Macro
-in \href{https://github.com/msteamc/.spacemacs.d/blob/master/org-templates/enpost.org}{my setup file for every .org file}. With Org Macro, I control some contents
-and options exist only for certain backend.
-
-Once you are familiar with Org Macro, It behaves beyond your imagination.
-\subsubsection{use the setupfile for each Org file}
-\label{sec:org66edc24}
-
-Often, you options for a org file grows more and more. If you think it kind of
-clutter at the top of your Org files, you can group them in a setupfile then
-include it at the top of your Org file.
-
-For my setupfiles, please refer to \href{https://github.com/msteamc/.spacemacs.d/tree/master/org-templates}{my org-templates}. As you can see, I have
-several setupfiles for different aims. To include one of them in my Org file, I
-use:
-
-\texttt{\#+SETUPFILE: <path+name of the setup files>}
-
-By using \texttt{\#+SETUPFILE} ,I only have to option lines at the top of my org file.
-So it looks clean.
-
-Also, you can notice that in \href{https://github.com/msteamc/.spacemacs.d/blob/master/org-templates/enpost.org}{my setupfile named enpost.org} exists options for
-different export targets.
-
-\subsection{Drawing Graphs Using TikZ in Emacs Org}
-\label{sec:org171ea2a}
-
-Draw a graph using TikZ
+Also every complex number \(a+ib\) can be represented in the exponential form
+conveniently through the Euler's formula \(e^{i\alpha} = \cos\alpha +
+i\sin\alpha\).
 
 \begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/example.pdf}
+\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/eulerEquation.pdf}
 \end{center}
-
-\begin{center}
-\includegraphics[width=0.7\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/example1.pdf}
-\end{center}
-
-\begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/basiclayer.pdf}
-\end{center}
-
-\section{Projects}
-\label{sec:org91fe676}
-
-\subsection{my workflow of creating a video}
-\label{sec:org7aa4f8b}
-\hspace{0pt}\\
-
-This collection of Videos and Posts describes my workflow of creating a video. Usage of some tools and methods are covered.
-
-During the creation of one video, several tools are tuned to fit my workflow. In
-this project several videos and posts will be created to make my workflow clear.
-
-Two targets of this project:
-\begin{enumerate}
-\item remind me of the configuration of several tools;
-\item show somebody else who may be interested in how I work.
-\end{enumerate}
-
-I am not ready to detail each tool. If you are interested in any one of them,
-please refer to tutorials written by experts or given by the official document.
-
-\subsubsection{Emacs}
-\label{sec:org2fbd9b9}
-
-Emacs lies in the center of my workflow. It behaves like a super-IDE which
-assists me finish almost all the steps. Using Emacs, I program and debug, GTD,
-write the blogs, export and publish them. Many of the Emacs extensions are
-awesome. In particular, Emacs Org is the killer app.
-
-How to config Emacs? After more Than ten years of using Emacs, I choose
-spacemacs. Most beginners can start their work using spacemacs with only a
-little modifications.
-
-\begin{enumerate}
-\item program and debug
-\label{sec:org2090515}
-
-I program in python, C/C++, Matlab and some other languages. Emacs acts as a
-super-IDE for me.
-
-\item Org mode - journalize your work
-\label{sec:org68fd51b}
-
-Org mode definitely need a standalone subsection.
-
-\item Org mode - get things done
-\label{sec:orgc649c82}
-
-\item Org mode - write a diary
-\label{sec:orgc5ee9f2}
-
-\item Org mode - export your Org file
-\label{sec:orgec750d0}
-
-\item program and debug
-\label{sec:org78ee2a9}
-
-\item writing latex
-\label{sec:org5309ad9}
-\item org-journal
-\label{sec:orgb4dcd6b}
-
-I write many notes during a post or a project. Most of my journal is maintained
-by \href{https://github.com/bastibe/org-journal}{org-journal: A simple org-mode based journaling mode} . And I set the
-\texttt{org-journal-file-type} to \texttt{weekly} So that I have around 52 journal file each
-year.
-
-The journals can be searched conveniently. Also they can be integrated into Org
-agenda.
-
-\item ox-hugo
-\label{sec:org5a96636}
-
-\href{https://github.com/kaushalmodi/ox-hugo}{kaushalmodi/ox-hugo: A carefully crafted Org exporter back-end for Hugo}
-
-Because hugo supports markdown at first (it also supports org file later), I use
-Emacs Org from the very beginning. I am quite familiar with org-mode, so have no
-motivation to dig into markdown. Fortunately, ox-hugo meets all my requirement
-and definitely worth a try when you want to stay in Org.
-
-Actually, Emacs have extensions to support markdown quite well. However, using
-Org, I can integrate the org file into my agenda.
-
-\item preview tikz picture in Org
-\label{sec:org8bf8be5}
-
-\href{http://www.texample.net/tikz/}{TikZ and PGF} are \TeX{} packages for creating graphics programmatically. TikZ is
-build on top of PGF and allows you to create sophisticated graphics in a rather
-intuitive and easy manner.
-
-You can integrated TikZ code into the Org mode as a source block. I have a
-not-so-detailed post on how to set up the tikz environment in Org.
-\end{enumerate}
-
-\subsubsection{Hugo}
-\label{sec:orgaed3855}
-
-As the fastest framework for building websites, Hugo shocks me by its speed and
-flexibility. It is enough to prettify your site using the more than 300+
-beautiful themes, from which I am in the mode for Academic theme.
-
-Hugo supports Org file but not so good. Ox-hugo, another extension of Emacs, has
-my attention. Serving as a bridge between Emacs and Hugo, ox-hugo helps me
-staying in Emacs Org. There is no need for me to write markdown file if Org is
-available.
-
-I use ox-hugo as a bridge between Emacs and Hugo. So I do not have to care much
-about how to leverage Hugo. Ox-hugo helps me do most of the work.
-\subsubsection{Hugo Academic Theme}
-\label{sec:org7ca124e}
-
-\href{https://github.com/gcushen/hugo-academic}{Hugo Academic Theme} is a beautiful and flexible theme developed for Hugo. This
-site is built based on this theme.
-
-If you want attach a pdf version of your post, two steps are needed:
-\begin{enumerate}
-\item add a line:
-\begin{verbatim}
-url_pdf = "#"
-\end{verbatim}
-in the front matter of your markdown file.
-\item add a PDF file with the same name as your post’s own folder to your post’s
-folder.
-\end{enumerate}
-
-A PDF link will be automatically generated just like the \texttt{pdf} link appears in
-the top of each post in my site. Because I use Emacs Org with ox-hugo, I add one
-line in the property:
-
-\begin{verbatim}
-:EXPORT_HUGO_CUSTOM_FRONT_MATTER+: :url_pdf "#"
-\end{verbatim}
-
-Hugo academic theme provide some front matters that hugo does not support by
-default. Fortunately, \href{https://github.com/kaushalmodi/ox-hugo}{ox-hugo} handles this effectively. For more information.
-you can read:
-\begin{enumerate}
-\item \href{https://ox-hugo.scripter.co/doc/org-meta-data-to-hugo-front-matter/}{Org meta-data to Hugo front-matter}
-\item \href{https://ox-hugo.scripter.co/doc/custom-front-matter/}{Custom Front-matter Parameters}
-\end{enumerate}
-
-\subsubsection{manim}
-\label{sec:org12e9ea1}
-
-\subsubsection{blender}
-\label{sec:orgb3042c1}
-
-\section{Courses}
-\label{sec:org92abef5}
 \end{document}

### 2020-01-10 mstemc/index.tex
add problem 1.3

@@
 \usetikzlibrary{arrows,decorations.pathmorphing,,backgrounds,positioning,fit,petri,calc,intersections,through,shapes.misc,mindmap,calendar,shadows,mindmap,calendar,graphdrawing,trees}
-               \usepackage{tikz}
 \author{Eason}
@@
 summary of this post
+
 \section{Basic Problems With Answers}
-\label{sec:org8f261cc}
+\label{sec:orgf4c241b}
 
-\begin{prob}[]{prob:1.1}
-Express each of the following complex numbers in \emph{Cartesian} form \(x+iy\):
+\begin{prob}
+Problem 1.1: Express each of the following complex numbers in \emph{Cartesian} form \(x+iy\):
 \begin{equation*}
-\begin{array}
-\quad \frac{1}{2}e^{i\pi}  & \frac{1}{2}e^{-i\pi}  & e^{i\pi/2}  \\
+\begin{array}{ccc}
+ \frac{1}{2}e^{i\pi}  & \frac{1}{2}e^{-i\pi}  & e^{i\pi/2}  \\
  e^{-i\pi/2}         & e^{i5\pi/2}  & \sqrt{2}e^{i\pi/4}  \\
- \sqrt{2}e^{i9\pi/4} & \sqrt{2}e^{-9i\pi/4}  & \sqrt{2} e^{-i\pi/4}
+ \sqrt{2}e^{i9\pi/4} & \sqrt{2}e^{-i9\pi/4}  & \sqrt{2} e^{-i\pi/4}
 \end{array}
 \end{equation*}
-\label{prob:1.1}
+\label{prob11}
 \end{prob}
 
-\begin{prob}[]{prob:1.2}
-Express each of the following complex numbers in \emph{polar} form (\(re^{i\theta},
--\pi < \theta \leq -\pi\)): \(5\),\(-2\),\(-3i\),\(\frac{1}{2} -
-i\frac{\sqrt{3}}{2}\), \(1 + i\), \((1-i)^{2}\), \(i(1-i)\), \((1+i)/(1-i)\), \((\sqrt{2} +i\sqrt{2})/ (1 +i\sqrt{3})\)
-\label{prob:1.2}
+\begin{prob}
+Problem 1.2: Express each of the following complex numbers in \emph{polar} form (\(re^{i\theta},
+-\pi < \theta \leq \pi\)):
+\begin{equation*}
+\begin{array}{c{3cm}c{3cm}c{3cm}}
+5 & -2 & -3i \\
+\frac{1}{2} - i \frac{\sqrt{3}}{2} & 1+i & (1-i)^{2} \\
+i(1-i)  & \frac{1+i}{1-i}  & \frac{\sqrt{2} + i \sqrt{2}}{1+i\sqrt{3}}
+\end{array}
+\end{equation*}
+\label{prob12}
 \end{prob}
 
+First, let's figure them out using the Euler's formula. For the nine complex
+numbers in  \hyperref[prob11]{Problem 1.1}, we have:
+\begin{eqnarray*}
+\tfrac{1}{2} e^{i\pi } &=&  \tfrac{1}{2} (\cos(\pi) + i\sin(\pi) ) = \tfrac{1}{2} \cos(\pi) = -\tfrac{1}{2} \\
+\tfrac{1}{2} e^{-i\pi} &=& \tfrac{1}{2}  (\cos(-\pi) + i\sin(-\pi) ) = \tfrac{1}{2} \cos(-\pi) = -\tfrac{1}{2} \\
+e^{i\pi/2} &=& \cos(\pi/2) + i \sin(\pi/2) = i \\
+e^{-i\pi/2} &=& \cos(-\pi/2) + i \sin(-\pi/2) = -i \\
+e^{i5\pi/2} &=& \cos(5\pi/2) + i \sin(5\pi/2) = \cos(2\pi + \pi/2) + i \sin(2\pi + \pi/2) = i \sin(\pi/2) = i \\
+\sqrt{2}e^{i\pi/4} &=& \sqrt{2} ( \cos(\pi/4) + i \sin(\pi/4) ) = \sqrt{2} ( \tfrac{\sqrt{2}}{2} + i\tfrac{\sqrt{2}}{2}  ) = 1 + i \\
+ \sqrt{2} e^{i9 \pi/4} &=& \sqrt{2} ( \cos(9\pi/4) + i \sin(9\pi/4) ) = 1 + i \\
+ \sqrt{2} e^{-i9 \pi/4} &=& \sqrt{2} ( \cos(-9\pi/4) + i \sin(-9\pi/4) ) = 1 - i \\
+ \sqrt{2} e^{-i \pi/4} &=& \sqrt{2} ( \cos(-\pi/4) + i \sin(-\pi/4) ) = 1 - i
+\end{eqnarray*}
+
+For the nine complex numbers in  \hyperref[prob12]{Problem 1.2} , we have:
+
+\begin{eqnarray*}
+ 5 &=& 5 e^{i0} = 5 e^{i(2\pi n)}, n\in \{\ldots, -2,-1,0,1,2,\ldots \} \\
+ -2 &=& 2 e^{i\pi} = -2 e^{i0} \\
+ -3i &=& 3 e^{-i\pi} \\
+ \tfrac{1}{2} - i \tfrac{\sqrt{3}}{2}  &=& e^{-i\pi/3} \\
+ 1+i &=& \sqrt{2} e^{i\pi/4} \\
+ (1-i)^{2} &=& ( \sqrt{2} e^{-i\pi/4} )^{2} = 2 e^{-i\pi/2} \\
+ i(1-i) &=& 1 - i = \sqrt{2} e^{-i\pi/4} \\
+ \tfrac{1+i}{1-i} &=& \tfrac{ \sqrt{2}e^{i\pi/4} } { \sqrt{2}e^{-i\pi/4} } = e^{i\pi/2} \\
+ \tfrac{\sqrt{2} + i \sqrt{2}}{1+i\sqrt{3}} &=& \tfrac{ 2e^{i\pi/4} }{ 2 e^{i\pi/3} } = e^{-i\pi/12}
+\end{eqnarray*}
+
 Every complex number \(a+ib\) can be visualized in the complex plane
-\(\mathbb{C}\). It can be viewed as the point with the coordinate \((a,b)\) in
-the plane or as a vector starting from \(0,0\) to the point \((a,b)\).
+\(\mathbb{C}\). It can be viewed either as the point with the coordinate
+\((a,b)\) or as a vector starting from \(0,0\) to the point \((a,b)\).
 
 Also every complex number \(a+ib\) can be represented in the exponential form
-conveniently through the Euler's formula \(e^{i\alpha} = \cos\alpha +
-i\sin\alpha\).
+conveniently by using the Euler's formula \(e^{i\alpha} = \cos\alpha +
+i\sin\alpha\). One complex number have unique Cartesian form but do not have a
+unique expoential form. Taking \(1+i\) for example, its expoential form can be
+\(\sqrt{2}e^{i(\pi/4 + 2n\pi)}, n\in \{ \ldots, -2,-1,0,1,2,\ldots \}\). When we
+express a complex number in expoential form, it helps to keep a concept of
+rotation in mind. In the complex plane \(\mathbb{C}\), a complex number will
+return to itself if it rotates a multiple of \(2\pi\) around the origin point
+with radius equal to its modulus. please keep the concept of roatation in mind
+and it will become increasingly important during our later study.
+
+In the development of complex analysis, \(a+ib\) has another form \(r\angle
+\theta\), where \(r\) is the modulus and \(\theta\) the argument (or the angle).
+Obviously, this notation is not as good as the expoential form, espacialy when
+we want to do complex analysis such as differentiation and integration. We just
+mention it here for the sake of completion. The expoential form will be deployed
+from now on.
 
@@
 \end{center}
+
+Now, let's go back to \hyperref[prob11]{Problem 1.1} and Problem \hyperref[prob12]{Problem
+1.2}. It's easy to figure the answers out using the Euler's formula. Let's do
+more to show them on the complex plane keeping the concept of rotation in mind.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/problem1_1.pdf}
+\caption{\label{problem1-1}
+visualized the complex numbers from Problem \hyperref[prob11]{Problem 1.1} in the complex plan}
+\end{figure}
+
+From Figure \ref{problem1-1} , taking \(\color{green}{\tfrac{1}{2}e^{i\pi}}\) and
+\(\color{red}{\tfrac{1}{2}e^{-i\pi}}\) for example, in the complex plane, they
+are the same point \(-\tfrac{1}{2}\) which means \(-\tfrac{1}{2}\) can be
+reached by rotating \(\tfrac{1}{2}\) with angle \(\pi\) clockwise or with angle
+\(-\pi\) anti-clockwise. Essentially, this is because that \(e^{i\theta} =
+e^{i(\theta + 2n\pi)}, n\in \{\ldots,-2,-1,0,1,2,\ldots\}\). It's
+straightforward that \(e^{i\pi} = e^{i(\pi + 2(-1)\pi)} = e^{-i\pi}\).
+
+In the end of \hyperref[prob11]{Problem 1.1} and \hyperref[prob11]{Problem 1.1}, I want to say
+more about expressing \(\tfrac{1+i}{1-i}\) in its polar form. There are two
+methods to get the polar form:
+\begin{enumerate}
+\item multiply the fraction's numerator and denominator by \(( 1 + i )\)
+
+So we have:
+\begin{eqnarray*}
+\frac{1+i}{1-i}& = & \frac{(1+i)(1+i)}{(1-i)(1+i)} \\
+&=& \frac{2i}{2} = i
+\end{eqnarray*}
+
+\item express the numerator and denominator in expoential form first, then do the
+following calculation.
+
+\begin{eqnarray*}
+\frac{1+i}{1-i} &=& \frac{\sqrt{2}e^{i\pi/4}}{\sqrt{2}e^{-i\pi/4}}  \\
+&=& e^{i2\pi/4} = e^{i\pi/2} = i
+\end{eqnarray*}
+\end{enumerate}
 \end{document}

### 2020-01-10 mstemc/mstemc.tex
add problem 1.3

@@
 
-\begin{prob}[]{prob:1.1}
-Express each of the following complex numbers in \emph{Cartesian} form \(x+iy\):
+\begin{prob}
+Problem 1.1: Express each of the following complex numbers in \emph{Cartesian} form \(x+iy\):
 \begin{equation*}
@@
  e^{-i\pi/2}         & e^{i5\pi/2}  & \sqrt{2}e^{i\pi/4}  \\
- \sqrt{2}e^{i9\pi/4} & \sqrt{2}e^{-9i\pi/4}  & \sqrt{2} e^{-i\pi/4}
+ \sqrt{2}e^{i9\pi/4} & \sqrt{2}e^{-i9\pi/4}  & \sqrt{2} e^{-i\pi/4}
 \end{array}
 \end{equation*}
-\label{prob:1.1}
+\label{prob11}
 \end{prob}
 
-\begin{prob}[]{prob:1.2}
-Express each of the following complex numbers in \emph{polar} form (\(re^{i\theta},
--\pi < \theta \leq -\pi\)):
+\begin{prob}
+Problem 1.2: Express each of the following complex numbers in \emph{polar} form (\(re^{i\theta},
+-\pi < \theta \leq \pi\)):
 \begin{equation*}
@@
 \end{equation*}
-\label{prob:1.2}
+\label{prob12}
 \end{prob}
 
+First, let's figure them out using the Euler's formula. For the nine complex
+numbers in  \hyperref[prob11]{Problem 1.1}, we have:
+\begin{eqnarray*}
+\tfrac{1}{2} e^{i\pi } &=&  \tfrac{1}{2} (\cos(\pi) + i\sin(\pi) ) = \tfrac{1}{2} \cos(\pi) = -\tfrac{1}{2} \\
+\tfrac{1}{2} e^{-i\pi} &=& \tfrac{1}{2}  (\cos(-\pi) + i\sin(-\pi) ) = \tfrac{1}{2} \cos(-\pi) = -\tfrac{1}{2} \\
+e^{i\pi/2} &=& \cos(\pi/2) + i \sin(\pi/2) = i \\
+e^{-i\pi/2} &=& \cos(-\pi/2) + i \sin(-\pi/2) = -i \\
+e^{i5\pi/2} &=& \cos(5\pi/2) + i \sin(5\pi/2) = \cos(2\pi + \pi/2) + i \sin(2\pi + \pi/2) = i \sin(\pi/2) = i \\
+\sqrt{2}e^{i\pi/4} &=& \sqrt{2} ( \cos(\pi/4) + i \sin(\pi/4) ) = \sqrt{2} ( \tfrac{\sqrt{2}}{2} + i\tfrac{\sqrt{2}}{2}  ) = 1 + i \\
+ \sqrt{2} e^{i9 \pi/4} &=& \sqrt{2} ( \cos(9\pi/4) + i \sin(9\pi/4) ) = 1 + i \\
+ \sqrt{2} e^{-i9 \pi/4} &=& \sqrt{2} ( \cos(-9\pi/4) + i \sin(-9\pi/4) ) = 1 - i \\
+ \sqrt{2} e^{-i \pi/4} &=& \sqrt{2} ( \cos(-\pi/4) + i \sin(-\pi/4) ) = 1 - i
+\end{eqnarray*}
+
+For the nine complex numbers in  \hyperref[prob12]{Problem 1.2} , we have:
+
+\begin{eqnarray*}
+ 5 &=& 5 e^{i0} = 5 e^{i(2\pi n)}, n\in \{\ldots, -2,-1,0,1,2,\ldots \} \\
+ -2 &=& 2 e^{i\pi} = -2 e^{i0} \\
+ -3i &=& 3 e^{-i\pi} \\
+ \tfrac{1}{2} - i \tfrac{\sqrt{3}}{2}  &=& e^{-i\pi/3} \\
+ 1+i &=& \sqrt{2} e^{i\pi/4} \\
+ (1-i)^{2} &=& ( \sqrt{2} e^{-i\pi/4} )^{2} = 2 e^{-i\pi/2} \\
+ i(1-i) &=& 1 - i = \sqrt{2} e^{-i\pi/4} \\
+ \tfrac{1+i}{1-i} &=& \tfrac{ \sqrt{2}e^{i\pi/4} } { \sqrt{2}e^{-i\pi/4} } = e^{i\pi/2} \\
+ \tfrac{\sqrt{2} + i \sqrt{2}}{1+i\sqrt{3}} &=& \tfrac{ 2e^{i\pi/4} }{ 2 e^{i\pi/3} } = e^{-i\pi/12}
+\end{eqnarray*}
+
 Every complex number \(a+ib\) can be visualized in the complex plane
-\(\mathbb{C}\). It can be viewed as the point with the coordinate \((a,b)\) in
-the plane or as a vector starting from \(0,0\) to the point \((a,b)\).
+\(\mathbb{C}\). It can be viewed either as the point with the coordinate
+\((a,b)\) or as a vector starting from \(0,0\) to the point \((a,b)\).
 
 Also every complex number \(a+ib\) can be represented in the exponential form
-conveniently through the Euler's formula \(e^{i\alpha} = \cos\alpha +
-i\sin\alpha\).
+conveniently by using the Euler's formula \(e^{i\alpha} = \cos\alpha +
+i\sin\alpha\). One complex number have unique Cartesian form but do not have a
+unique expoential form. Taking \(1+i\) for example, its expoential form can be
+\(\sqrt{2}e^{i(\pi/4 + 2n\pi)}, n\in \{ \ldots, -2,-1,0,1,2,\ldots \}\). When we
+express a complex number in expoential form, it helps to keep a concept of
+rotation in mind. In the complex plane \(\mathbb{C}\), a complex number will
+return to itself if it rotates a multiple of \(2\pi\) around the origin point
+with radius equal to its modulus. please keep the concept of roatation in mind
+and it will become increasingly important during our later study.
+
+In the development of complex analysis, \(a+ib\) has another form \(r\angle
+\theta\), where \(r\) is the modulus and \(\theta\) the argument (or the angle).
+Obviously, this notation is not as good as the expoential form, espacialy when
+we want to do complex analysis such as differentiation and integration. We just
+mention it here for the sake of completion. The expoential form will be deployed
+from now on.
 
@@
 \end{center}
+
+Now, let's go back to \hyperref[prob11]{Problem 1.1} and Problem \hyperref[prob12]{Problem
+1.2}. It's easy to figure the answers out using the Euler's formula. Let's do
+more to show them on the complex plane keeping the concept of rotation in mind.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/problem1_1.pdf}
+\caption{\label{problem1-1}
+visualized the complex numbers from Problem \hyperref[prob11]{Problem 1.1} in the complex plan}
+\end{figure}
+
+From Figure \ref{problem1-1} , taking \(\color{green}{\tfrac{1}{2}e^{i\pi}}\) and
+\(\color{red}{\tfrac{1}{2}e^{-i\pi}}\) for example, in the complex plane, they
+are the same point \(-\tfrac{1}{2}\) which means \(-\tfrac{1}{2}\) can be
+reached by rotating \(\tfrac{1}{2}\) with angle \(\pi\) clockwise or with angle
+\(-\pi\) anti-clockwise. Essentially, this is because that \(e^{i\theta} =
+e^{i(\theta + 2n\pi)}, n\in \{\ldots,-2,-1,0,1,2,\ldots\}\). It's
+straightforward that \(e^{i\pi} = e^{i(\pi + 2(-1)\pi)} = e^{-i\pi}\).
+
+In the end of \hyperref[prob11]{Problem 1.1} and \hyperref[prob11]{Problem 1.1}, I want to say
+more about expressing \(\tfrac{1+i}{1-i}\) in its polar form. There are two
+methods to get the polar form:
+\begin{enumerate}
+\item multiply the fraction's numerator and denominator by \(( 1 + i )\)
+
+So we have:
+\begin{eqnarray*}
+\frac{1+i}{1-i}& = & \frac{(1+i)(1+i)}{(1-i)(1+i)} \\
+&=& \frac{2i}{2} = i
+\end{eqnarray*}
+
+\item express the numerator and denominator in expoential form first, then do the
+following calculation.
+
+\begin{eqnarray*}
+\frac{1+i}{1-i} &=& \frac{\sqrt{2}e^{i\pi/4}}{\sqrt{2}e^{-i\pi/4}}  \\
+&=& e^{i2\pi/4} = e^{i\pi/2} = i
+\end{eqnarray*}
+\end{enumerate}
+
+\begin{prob}[]{prob:1.3}
+Problem 1.3: Determine the values of \(P_{\infty}\) and \(E_{\infty}\) for each
+of the following signals:
+\begin{equation*}
+
+\begin{array}{lll}
+\mathrm{(a)} \quad x_{1}(t) = e^{-2t}u(t) & \mathrm{(b)} \quad x_{2}(t) = e^{i(2t + \pi/4)} & \mathrm{(c)} \quad x_{3}(t) = \cos(t) \\
+\mathrm{(d)} \quad x_{1}[n] = (\tfrac{1}{2})^{n} u[n] & \mathrm{e} \quad x_{2}[n] = e^{i(\pi/2n + \pi/8)} & \mathrm{f} \quad x_{3}[n] = \cos(\tfrac{\pi}{4}n)
+\end{array}
+\end{equation*}
+\label{prob:1.3}
+\end{prob}
 \end{document}

### 2020-01-18 mstemc/index.tex
finish the figures in prob1.4

@@
 \date{\today}
-\title{signals and systems chapter 1 problems}
+\title{Signals and Systems Chapter 1 Problems}
 \hypersetup{
  pdfauthor={Eason},
- pdftitle={signals and systems chapter 1 problems},
+ pdftitle={Signals and Systems Chapter 1 Problems},
  pdfkeywords={},
@@
  \vspace{\baselineskip}
- \textbf{\Huge signal and system chapter 1 problems} \par
+ \textbf{\Huge Signal and System Chapter 1 Problems} \par
  \vspace{2\baselineskip}  \newline
@@
 \section{Basic Problems With Answers}
-\label{sec:orgf4c241b}
+\label{sec:org66bb87c}
 
-\begin{prob}
+\subsection{Problem 1.1 and Problem 1.2}
+\label{sec:org2a3de1e}
+
+\begin{prob}[]{prob:1.3}
 Problem 1.1: Express each of the following complex numbers in \emph{Cartesian} form \(x+iy\):
@@
 
-\begin{prob}
+\begin{prob}[]{prob:1.3}
 Problem 1.2: Express each of the following complex numbers in \emph{polar} form (\(re^{i\theta},
@@
 
-In the end of \hyperref[prob11]{Problem 1.1} and \hyperref[prob11]{Problem 1.1}, I want to say
+In the end of \hyperref[prob11]{Problem 1.1} and \hyperref[prob12]{Problem 1.2}, I want to say
 more about expressing \(\tfrac{1+i}{1-i}\) in its polar form. There are two
@@
 \end{enumerate}
+\subsection{Problem 1.3}
+\label{sec:orge16e8d1}
+
+\begin{prob}[]{prob:1.3}
+Problem 1.3: Determine the values of \(P_{\infty}\) and \(E_{\infty}\) for each
+of the following signals:
+\begin{equation*}
+\begin{array}{ll}
+\mathrm{(a)} \quad x_{1}(t) = e^{-2t}u(t) & \mathrm{(b)} \quad x_{2}(t) = e^{i(2t + \pi/4)} \\
+ \mathrm{(c)} \quad x_{3}(t) = \cos(t) & \mathrm{(d)} \quad x_{1}[n] = (\tfrac{1}{2})^{n} u[n] \\
+ \mathrm{( e )} \quad x_{2}[n] = e^{i(\pi/2n + \pi/8)} & \mathrm{(f)} \quad x_{3}[n] = \cos(\tfrac{\pi}{4}n)
+\end{array}
+\end{equation*}
+\label{prob13}
+\end{prob}
+
+Before solving this problem, let's review the definition of \(P_{\infty}\) and
+\(E_{\infty}\). For a continuous time signal \(x(t)\), we have
+\begin{eqnarray}
+\label{eq:2}
+E_{\infty}&=& \lim_{T\to \infty} \int_{-T}^{T} |x(t)|^{2}\mathrm{d}t \\
+P_{\infty}&=& \lim_{T\to \infty} \frac{1}{2T}\int_{-T}^{T} |x(t)|^{2}\mathrm{d}t = \lim_{T\to\infty} \frac{E_{\infty}}{2T}
+\end{eqnarray}
+For a discrete time signal \(x[n]\), we have:
+\begin{eqnarray}
+\label{eq:3}
+E_{\infty}&=& \lim_{N\to \infty} \sum_{n=-N}^{+N} |x[n]|^{2} \\
+P_{\infty}&=& \lim_{N\to \infty} \frac{1}{2N+1} \sum_{n=-N}^{+N} |x[n]|^{2} = \lim_{N\to\infty} \frac{E_{\infty}}{2N+1}
+\end{eqnarray}
+
+Equation (\ref{eq:2})(\ref{eq:3}) are not only mathmatical definitions but also
+related to physical quantities such as power and energy in a physical system.
+For an electric circuit, taking the voltage \(v(t)\) and current \(i(t)\) across
+a resistor for example, the power at time \(t\) can be calculated by:
+\begin{equation}
+\label{eq:4}
+p(t) = v(t)i(t) = \frac{v^{2}(t)}{R}
+\end{equation}
+Let's go back to equation (\ref{eq:2}) and equation(\ref{eq:3}), if
+\(E_{\infty}< \infty\) we say that the signal has finite energy otherwise
+infinite energy. If \(P_{\infty} <\infty\) we say that the signal has finite
+power otherwise infinite power.
+
+Next let's determine the values of \(P_{\infty}\) and \(E_{\infty}\) for the
+given signals.
+
+\(\mathbf{(a)}: x_{1}(t)= e^{-2t}u(t)\) :
+
+\begin{eqnarray*}
+E_{\infty}  & =  & \int_{\infty}^{\infty} |e^{-2t}u(t)|^{2} \mathrm{d}t \\
+&=& \int_{0}^{\infty} e^{-4t} \mathrm{d}t \\
+&=& \frac{1}{4}
+\end{eqnarray*}
+So, it's straightforward that:
+\begin{equation}
+\label{eq:5}
+P_{\infty} = \lim_{T\to \infty} \frac{E_{\infty}}{2T}  = 0
+\end{equation}
+
+\begin{center}
+\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figprob1-3.pdf}
+\end{center}
+
+\(\mathbf{(b)}: x_{2}(t)= e^{i(2t+\pi/4)}\)
+
+We have \(|e^{i(2t+\pi/4)}| = 1\) , therefore
+\begin{eqnarray*}
+E_{\infty}&=& \int_{\infty}^{\infty} |x_{2}(t)= e^{i(2t+\pi/4)}|^{2} \mathrm{d}t \\
+&=& \infty
+\end{eqnarray*}
+
+For power \(P_{\infty}\), we have:
+\begin{eqnarray*}
+P_{\infty}&= &\lim_{T\to\infty} \frac{1}{2T}\int_{-T}^{T} |x_{2}(t)|^{2} \mathrm{d}t  \\
+&=& 1
+\end{eqnarray*}
+
+This signal has constant power. If you keep the concept of rotation mentioned in
+Problem \ref{prob11}, you will notice immediately that all the points generated by
+\(x_{2}(t)\) lies on the unit circle.
+
+\(\mathbf{(c)}:x_{3}(t)=\cos(t)\)
+
+\begin{eqnarray*}
+E_{\infty}&=& \lim_{T\to\infty} \int_{-\infty}^{\infty} |x_{3}(t)|^{2} \mathrm{d}t \\
+&=& \int_{\infty}^{\infty} \cos(t)^{2} \mathrm{d}t = \infty
+\end{eqnarray*}
+
+\begin{eqnarray*}
+P_{\infty}&=& \lim_{T\to\infty} \frac{1}{2T}\int_{-T}^{T} |x_{3}(t)|^{2} \mathrm{d}t  \\
+&=& \lim_{T\to\infty} \int_{-T}^{T} \cos(t)^{2} \mathrm{d}t \\
+&=& \lim_{T\to\infty}  \int_{-T}^{T} \frac{1+\cos(2t)}{2} \mathrm{d}t = \frac{1}{2}
+\end{eqnarray*}
+
+\subsection{Problem 1.4}
+\label{sec:org719025d}
+
+\begin{prob}[]{prob:1-4}
+ Problem 1.4: Let \(x[n]\) be a signal with \(x[n]=0\) for\(n< -2\) and \(n>4\),
+for each signal given below, determine the values of \(n\) for which it is
+guaranteed to be zero.
+\begin{eqnarray*}
+\mathbf{ (a) } & & x[n-3] \\
+\mathbf{ (b) } & & x[n+4] \\
+\mathbf{ (c) } & & x[-n]  \\
+\mathbf{ (d) } & & x[-n+2] \\
+\mathbf{ (e) } & & x[-n-2]
+\end{eqnarray*}
+\label{prob:1-4}
+\end{prob}
+
+For the given signals \(\mathbf{(a)}\) to \(\mathbf{(e)}\), the transformations
+of the variable \(n\) will change the interval in which the signals are zero.
+For the convenience of calculation, we write the origin signal as:
+\begin{equation*}
+x[m] = 0, m< -2 \quad \mathrm{and} \quad m>4
+\end{equation*}
+
+We can visualize \(x(m)\) as below (I just give an example, you can name any
+signal that satisfy \(x[m] = 0, m< -2 \ \mathrm{and} \ m>4\)):
+
+\begin{center}
+\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-4.pdf}
+\end{center}
+
+\(\mathbf{(a)}:x[n-3]\)
+
+For signal \(\mathbf{(a)}\), to get the interval where \(x[n-3] = 0\), we have:
+\begin{eqnarray*}
+  t=n-3 &<& -2 \\
+  t=n-3 &>& 4
+\end{eqnarray*}
+ Then, we have \(n < 1 \ \mathrm{and} \ n > 7\) from which we can see that
+the new signal is a right shift three relative to the origin signal, i.e. new
+signal is delayed with three.
+
+\begin{center}
+\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-4a.pdf}
+\end{center}
+
+\(\mathbf{(b)}:x[n+4]\)
+
+For signal \(\mathbf{(b)}\), we have:
+\begin{eqnarray*}
+t=n+4&<&-2 \\
+t=n+4&>&4
+\end{eqnarray*}
+Then, we have \(n<-6\ \mathrm{and}\ n>0\) from which we can see that the new
+signal is a left shift four relative to the origin singal, i.e. new
+signal is advanced with four.
+
+\begin{center}
+\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-4b.pdf}
+\end{center}
+
+\(\mathbf{(c)}: x[-n]\)
+
+For signal \(\mathbf{( c )}\), we have:
+\begin{eqnarray*}
+t=-n&<&-2 \\
+t=-n&>&4
+\end{eqnarray*}
+
+Then, we have \(n>2\ \mathrm{and} \ n<-4\) from which we can see that the new
+signal is a reversal of the origin signal.
+
+\begin{center}
+\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-4c.pdf}
+\end{center}
+
+\(\mathbf{(d)}: x[-n+2]\)
+
+for signal \(\mathbf{(d)}\), we have:
+\begin{eqnarray*}
+t=-n+2&<&-2 \\
+t=-n+2&>&4
+\end{eqnarray*}
+Then, we have \(n>4\ \mathrm{and}\ n<-2\). For \(x[-n+2]\), we can first
+flip the original signal then right shift the flipped signal by 2. Notice the
+contents in the brackets \(-(n+2)\). I would like treat it as \(-(n-2)\), by
+which I know that the minus symbol means reversal and \(-2\) means right
+shift by 2.
+
+\begin{center}
+\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-4d.pdf}
+\end{center}
+
+\(\mathbf{(e)}: x[-n-2]\)
+
+For signal \(\mathbf{(e)}\), we have:
+
+\begin{eqnarray*}
+t=-n-2&<&-2 \\
+t=-n-2&>&4
+\end{eqnarray*}
+
+Then, we have \(n>0 \ \mathrm{and}\ n<-6\). To get the new signal, we have
+to filp the original signal first then left shift the flipped signal by two.
+
+\begin{center}
+\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-4e.pdf}
+\end{center}
 \end{document}

### 2020-01-18 mstemc/mstemc.tex
finish the figures in prob1.4

--- 2020-01-08 mstemc/mstemc.tex
@@
 \usetikzlibrary{arrows,decorations.pathmorphing,,backgrounds,positioning,fit,petri,calc,intersections,through,shapes.misc,mindmap,calendar,shadows,mindmap,calendar,graphdrawing,trees}
-               \usepackage{tikz}
 \author{Eason}
 \date{\today}
-\title{Basic Problems With Answers}
+\title{Problem 1.4}
 \hypersetup{
  pdfauthor={Eason},
- pdftitle={Basic Problems With Answers},
+ pdftitle={Problem 1.4},
  pdfkeywords={},
@@
 
-\begin{prob}[]{prob:1.1}
-Express each of the following complex numbers in \emph{Cartesian} form \(x+iy\):
-\begin{equation*}
-\begin{array}{ccc}
- \frac{1}{2}e^{i\pi}  & \frac{1}{2}e^{-i\pi}  & e^{i\pi/2}  \\
- e^{-i\pi/2}         & e^{i5\pi/2}  & \sqrt{2}e^{i\pi/4}  \\
- \sqrt{2}e^{i9\pi/4} & \sqrt{2}e^{-9i\pi/4}  & \sqrt{2} e^{-i\pi/4}
-\end{array}
-\end{equation*}
-\label{prob:1.1}
+\begin{prob}[]{prob:1-4}
+ Problem 1.4 Let \(x[n]\) be a signal with \(x[n]=0\) for\(n< -2\) and \(n>4\),
+for each signal given below, determine the values of \(n\) for which it is
+guaranteed to be zero.
+\begin{eqnarray*}
+\mathbf{ (a) } & & x[n-3] \\
+\mathbf{ (b) } & & x[n+4] \\
+\mathbf{ (c) } & & x[-n]  \\
+\mathbf{ (d) } & & x[-n+2] \\
+\mathbf{ (e) } & & x[-n-2]
+\end{eqnarray*}
+\label{prob:1-4}
 \end{prob}
 
-\begin{prob}[]{prob:1.2}
-Express each of the following complex numbers in \emph{polar} form (\(re^{i\theta},
--\pi < \theta \leq -\pi\)):
+For the given signals \(\mathbf{(a)}\) to \(\mathbf{(e)}\), the transformations
+of the variable \(n\) will change the interval in which the signals are zero.
+For the convenience of calculation, we write the origin signal as:
 \begin{equation*}
-\begin{array}{c{3cm}c{3cm}c{3cm}}
-5 & -2 & -3i \\
-\frac{1}{2} - i \frac{\sqrt{3}}{2} & 1+i & (1-i)^{2} \\
-i(1-i)  & \frac{1+i}{1-i}  & \frac{\sqrt{2} + i \sqrt{2}}{1+i\sqrt{3}}
-\end{array}
+x[m] = 0, m< -2 \quad \mathrm{and} \quad m>4
 \end{equation*}
-\label{prob:1.2}
-\end{prob}
 
-Every complex number \(a+ib\) can be visualized in the complex plane
-\(\mathbb{C}\). It can be viewed as the point with the coordinate \((a,b)\) in
-the plane or as a vector starting from \(0,0\) to the point \((a,b)\).
-
-Also every complex number \(a+ib\) can be represented in the exponential form
-conveniently through the Euler's formula \(e^{i\alpha} = \cos\alpha +
-i\sin\alpha\).
+We can visualize \(x(m)\) as below (I just give an example, you can name any
+signal that satisfy \(x[m] = 0, m< -2 \ \mathrm{and} \ m>4\)):
 
 \begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/eulerEquation.pdf}
+\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-4.pdf}
+\end{center}
+
+\(\mathbf{(a)}:x[n-3]\)
+
+For signal \(\mathbf{(a)}\), to get the interval where \(x[n-3] = 0\), we have:
+\begin{eqnarray*}
+  t=n-3 &<& -2 \\
+  t=n-3 &>& 4
+\end{eqnarray*}
+ Then, we have \(n < 1 \ \mathrm{and} \ n > 7\) from which we can
+see that the new signal is a right shift with step three relative to the origin
+signal. The new signal is delayed with three.
+
+\begin{center}
+\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-4a.pdf}
+\end{center}
+
+\(\mathbf{(b)}:x[n+4]\)
+
+For signal \(\mathbf{(b)}\), we have:
+\begin{eqnarray*}
+t=n+4&<&-2 \\
+t=n+4&>&4
+\end{eqnarray*}
+Then, we have \(n<-6\ \mathrm{and}\ n>0\) from which we can see that the new
+signal is a left shift with step four relative to the origin singal. The new
+signal is advanced with four.
+
+\begin{center}
+\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-4b.pdf}
+\end{center}
+
+\(\mathbf{(c)}: x[-n]\)
+
+For signal \(\mathbf{( c )}\), we have:
+\begin{eqnarray*}
+t=-n&<&-2 \\
+t=-n&>&4
+\end{eqnarray*}
+
+Then, we have \(n>2\ \mathrm{and} \ n<-4\) from which we can see that the new
+signal is a reversal of the origin signal.
+
+\begin{center}
+\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-4c.pdf}
+\end{center}
+
+\(\mathbf{(d)}: x[-n+2]\)
+
+for signal \(\mathbf{(d)}\), we have:
+\begin{eqnarray*}
+t=-n+2&<&-2 \\
+t=-n+2&>&4
+\end{eqnarray*}
+Then, we have \(n>4\ \mathrm{and}\ n<-2\). For \(x[-n+2]\), we can first
+flip the original signal then right shift the flipped signal by 2. Notice the
+contents in the brackets \(-(n+2)\). I would like treat it as \(-(n-2)\), by
+which I know that the minus symbol means reversal and \(-2\) means right
+shift by 2.
+
+\begin{center}
+\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-4d.pdf}
+\end{center}
+
+\(\mathbf{(e)}: x[-n-2]\)
+
+For signal \(\mathbf{(e)}\), we have:
+
+\begin{eqnarray*}
+t=-n-2&<&-2 \\
+t=-n-2&>&4
+\end{eqnarray*}
+Then, we have \(n>0 \ \mathrm{and}\ n<-6\). To get the new signal, we have
+to filp the original signal first then left shift the flipped one by two.
+
+\begin{center}
+\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-4e.pdf}
 \end{center}

### 2020-02-11 mstemc/index.tex
trivial update

--- 2020-01-08 mstemc/index.tex
@@
 \usepackage{tikz}
-\usetikzlibrary{arrows,decorations.pathmorphing,,backgrounds,positioning,fit,petri,calc,intersections,through,shapes.misc,mindmap,calendar,shadows,mindmap,calendar,graphdrawing,trees}
-               \usepackage{tikz}
+\usetikzlibrary{arrows,decorations.pathmorphing,,backgrounds,positioning,fit,petri,calc,intersections,through,shapes.misc,mindmap,calendar,shadows,mindmap,calendar,graphdrawing,trees,shapes.misc,quotes,angles}
+\definecolor{mycolor}{RGB}{139,0,0}
 \author{Eason}
 \date{\today}
-\title{signals and systems chapter 1 problems}
+\title{Signals and Systems Chapter 1 Problems Part 3 (1.32-1.47)}
 \hypersetup{
  pdfauthor={Eason},
- pdftitle={signals and systems chapter 1 problems},
+ pdftitle={Signals and Systems Chapter 1 Problems Part 3 (1.32-1.47)},
  pdfkeywords={},
- pdfsubject={summary of this post},
+ pdfsubject={This post consists of solutions to problems from 1.21 to 1.31 in chapter 1 of the book Signals and Systems by Oppenheim ,Willsky and Nawab.\cite{oppenheim_signals_1997}},
  pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
@@
 
- \thispagestyle{empty}
- \begingroup
-\begin{center}
- \vspace{\baselineskip}
- \textbf{\Huge signal and system chapter 1 problems} \par
- \vspace{2\baselineskip}  \newline
- \textbf{\large Eason Zhang with www.makesteamclear.com \par}
- \vspace{\baselineskip} \newline
-  \today \par
- \vspace{\baselineskip}
-  \vfill
- \setlength{\unitlength}{3pt}
- \includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/eulerEquation.pdf}
- \vfill \vspace{\baselineskip}
- \href{WWW.MAKESTEAMCLEAR.COM}{\Large WWW.MAKESTEAMCLEAR.COM} \par\newline
-  makesteamclear is a free project, run by Eason Zhang, to make videos about STEAM in a more approachable way.
-If you find the contents in this article or the site or the youtube channel helpful, please consider \href{www.makesteamclear.com}{\ensuremath \heartsuit support me\ensuremath\heartsuit }, thanks \par
- \end{center}
- \endgroup
+\section{Problem 1.32}
+\label{sec:org919e435}
 
- \newpage \thispagestyle{empty} \textbf{copyright page} \newpage \tableofcontents \newpage
-\hspace{0pt}\\
+\begin{prob}[]{prob:1-32}
+Let \(x(t)\) be a continuous-time signal, and let
+\begin{equation*}
+y_{1}(t) = x(2t) \ \mathrm{and} \ y_{2}(t) = x(t/2)
+\end{equation*}
+The signal \(y_{1}(t)\) represents a speeded up version of \(x(t)\) in the
+sense that the duration of the signal is cut in half. Similarly,
+\(y_{2}(t)\) represents a slowed down version of \(x(t)\) in the sense that
+the duration of the signal is doubled. Consider the following statements:
 
-summary of this post
-\section{Basic Problems With Answers}
-\label{sec:org8f261cc}
+\begin{enumerate}
+\item If \(x(t)\) is periodic, then \(y_{1}(t)\) is periodic.
+\item If \(y_{1}(t)\) is periodic, then \(x(t)\) is periodic.
+\item If \(x(t)\) is periodic, then \(y_{2}(t)\) is periodic.
+\item If \(y_{2}(t)\) is periodic, then \(x(t)\) is periodic.
+\end{enumerate}
 
-\begin{prob}[]{prob:1.1}
-Express each of the following complex numbers in \emph{Cartesian} form \(x+iy\):
-\begin{equation*}
-\begin{array}
-\quad \frac{1}{2}e^{i\pi}  & \frac{1}{2}e^{-i\pi}  & e^{i\pi/2}  \\
- e^{-i\pi/2}         & e^{i5\pi/2}  & \sqrt{2}e^{i\pi/4}  \\
- \sqrt{2}e^{i9\pi/4} & \sqrt{2}e^{-9i\pi/4}  & \sqrt{2} e^{-i\pi/4}
-\end{array}
-\end{equation*}
-\label{prob:1.1}
+For each of these statements, determine whether it is true, and if so,
+determine the relationship between the fundamental periods of the two
+signals considered in the statement. If the statement is not true, produce a
+counterexample to it.
+\label{prob:1-32}
 \end{prob}
 
-\begin{prob}[]{prob:1.2}
-Express each of the following complex numbers in \emph{polar} form (\(re^{i\theta},
--\pi < \theta \leq -\pi\)): \(5\),\(-2\),\(-3i\),\(\frac{1}{2} -
-i\frac{\sqrt{3}}{2}\), \(1 + i\), \((1-i)^{2}\), \(i(1-i)\), \((1+i)/(1-i)\), \((\sqrt{2} +i\sqrt{2})/ (1 +i\sqrt{3})\)
-\label{prob:1.2}
+\textbf{Problem 1.32a} \label{Problem 1.32a}
+
+Let \(T\) be the fundamental period of \(x(t)\), then we have \(x(t+T) = x(t)\).
+So \(y_{1}(t) = x(2t) = x(2t + T) = x(2(t+ \frac{T}{2} ))=
+y_{1}(t+\frac{T}{2})\), \(y_{1}(t)\) is periodic and the fundamental period is
+\(\frac{T}{2}\) which is consistent with our commonsense that \(y_{1}(t)\) is an
+speeded up version of \(x(t)\).
+
+\textbf{Problem 1.32b}
+
+Let \(T\) be the fundamental period of \(y_{1}(t)\), then based on the analysis
+of \hyperref[Problem 1.32a]{Problem 1.32a} , we have \(x(t)\) is a slowed down version of \(y_{1}(t)\),
+hense \(x(t)\) is periodic and has fundamental period \(2T\).
+
+\textbf{Problem 1.32c} \label{Problem 1.32c}
+
+Let \(T\) be the fundamental period of \(x(t)\), then we have \(x(t+T) = x(t)\).
+So \(y_{2}(t) = x(\tfrac{t}{2}) = x(\tfrac{t}{2} + T) = x(\frac{t+ 2T}{2})=
+y_{2}(t+2T)\), \(y_{2}(t)\) is periodic and the fundamental period is
+\(2T\) which is consistent with our commonsense that \(y_{2}(t)\) is an
+slowed down version of \(x(t)\).
+
+\textbf{Problem 1.32d}
+
+Let \(T\) be the fundamental period of \(y_{2}(t)\), then based on the analysis
+of \hyperref[Problem 1.32c]{Problem 1.32c} , we have \(x(t)\) is a speeded up version of \(y_{2}(t)\),
+hense \(x(t)\) is periodic and has fundamental period \(\frac{T}{2}\).
+\section{Problem 1.33}
+\label{sec:org7dadf9d}
+
+\begin{prob}[]{prob:1-33}
+Let \(x[n]\) be a discrete-time signal, and let
+\begin{equation*}
+y_{1}[n] = x[2n] \ \mathrm{and}\ y_{2}[n] =
+\begin{cases}
+x[n/2], & n\ \mathrm{even} \\
+0, & n\ \mathrm{odd}
+\end{cases}
+\end{equation*}
+The signals \(y_{1}[n]\) and \(y_{2}[n]\) respectively represent in some
+sense the speeded  up and slowed down versions of \(x[n]\). However, it
+should be noted that the discrete-time notions of speeded up and slowed down
+have subtle differences with respect to their continuous-time counterparts.
+Consider the following statements:
+
+\begin{enumerate}
+\item If \(x[n]\) is periodic, then \(y_{1}[n]\) is periodic.
+\item If \(y_{1}[n]\) is periodic, then \(x[n]\) is periodic.
+\item If \(x[n]\) is periodic, then \(y_{2}[n]\) is periodic.
+\item If \(y_{2}[n]\) is periodic, then \(x[n]\) is periodic.
+\end{enumerate}
+\label{prob:1-33}
 \end{prob}
 
-Every complex number \(a+ib\) can be visualized in the complex plane
-\(\mathbb{C}\). It can be viewed as the point with the coordinate \((a,b)\) in
-the plane or as a vector starting from \(0,0\) to the point \((a,b)\).
+\textbf{Problem 1.33a}
 
-Also every complex number \(a+ib\) can be represented in the exponential form
-conveniently through the Euler's formula \(e^{i\alpha} = \cos\alpha +
-i\sin\alpha\).
+Let \(N\) be the fundamental period of \(x[n]\), then \(x[n+N] = x[n]\), and
+\(y_{1}[n] = x[2n] = x[2n+N] = y_{1}[n+ \frac{N}{2}]\). If \(N\) is even, then
+\(y_{1}[n]\) has fundamental period \(\frac{N}{2}\).  It is a little tricky
+that when \(N\) is odd \(\frac{N}{2}\) has no meaning. If \(N\) is odd, we have
+to express \(y_{1}[n] = x[2n] = x[2n+2N] = y_{1}[n+ N]\) hence \(y_{1}[n]\) has
+fundamental period \(N\) if \(N\) is odd.
+
+\textbf{Problem 1.33b}
+
+We can see \(y_{1}[n]\) is not only a speeded up version but also a down
+sampling version of \(x[n]\). we cannot determine whether or not \(y_{1}[n]\)
+is periodic based on that \(x[n]\) is periodic. We can only tell that the even
+indexed value of \(x[n]\) is period. we know nothing about the odd indexed value
+of \(x[n]\). An example is given below:
+
+The given \(x[n]\) is periodic at \(2n\) but is random at \(2n+1\).
+\begin{center}
+\includegraphics[width=.9\linewidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-33b.pdf}
+\end{center}
 
 \begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/eulerEquation.pdf}
+\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-33b.pdf}
 \end{center}
+
+\textbf{Problem 1.33c} \label{Problem 1.33c}
+
+\(y_{2}[n]\) can treated as interpolation of \(x[n]\) with zero. So \(y_{2}[n]\)
+is periodic with fundamental period \(2N\) where \(N\) is fundamental period of
+\(x[n]\).
+
+\textbf{Problem 1.33d}
+
+Based on analysis of \hyperref[Problem 1.33c]{Problem 1.33c} , \(y_{2}[n]\) has fundamental period \(2N\)
+where \(N\) is the fundamental period of \(x[n]\).
+
+Based on the fact that only integer is valid for the independent variable of
+discrete-time signal, \(y_{2}[n]\) contains all the value of \(x[n]\) at the
+even index whereas at the odd index \(y_{2}[n]= 0\).
+\section{Problem 1.34}
+\label{sec:org20cd069}
+
+\begin{prob}[]{prob:1-34}
+In this problem, we explore several of the properties of even and odd
+signals.
+
+\begin{enumerate}
+\item Show that if \(x[n]\) is an odd signal, then
+\begin{equation*}
+\sum_{n=-\infty}^{+\infty} x[n] =0
+\end{equation*}
+\item Show that if \(x_{1}[n]\) is an odd signal and \(x_{2}[n]\) is an even
+signal, then \(x_{1}[n]x_{2}[n]\) is an odd signal.
+\item Let \(x[n]\) be an arbitrary signal with even and odd parts denoted by
+\begin{equation*}
+x_{e}[n] = \mathrm{Even}\{ x[n] \}
+\end{equation*}
+and
+\begin{equation*}
+x_{o}[n] = \mathrm{Odd} \{ x[n] \}
+\end{equation*}
+Show that
+\begin{equation*}
+\sum_{n=-\infty}^{+\infty} x^{2}[n] = \sum_{n=-\infty}^{+\infty} x_{e}^{2}[n] +  \sum_{n=-\infty}^{+\infty} x_{o}^{2}[n]
+\end{equation*}
+\item Although parts 1-3 have been stated in terms of discrete-time
+signals, the analogous properties are also valid in continuous time. To
+demonstrate this, show that
+\begin{equation*}
+\int_{-\infty}^{+\infty}x^{2}(t)dt = \int_{-\infty}^{+\infty} x_{e}^{2}(t)dt + \int_{-\infty}^{+\infty} x_{o}^{2}(t)dt
+\end{equation*}
+where \(x_{e}(t)\) and \(x_{o}(t)\) are, respectively, the even and odd
+parts of \(x(t)\).
+\end{enumerate}
+\label{prob:1-34}
+\end{prob}
+
+\textbf{Problem 1.34a}
+
+If \(x[n]\) is an odd signal, then we have \(x[n] = -x[-n]\) and \(x[0]=0\), so
+\begin{eqnarray*}
+\sum_{n=-\infty}^{+\infty} x[n] &=& \sum_{n=0}^{+\infty} x[n] + \sum_{-\infty}^{0} x[n] \\
+&=& \sum_{n=0}^{\infty} \big( x[n] + x[-n] \big)  \\
+&=& 0
+\end{eqnarray*}
+
+\textbf{Problem 1.34b}
+
+Because \(x_{1}[n]\) is an odd signal, \(x_{1}[n] = -x_{1}[-n]\). Because
+\(x_{2}[n]\) is an even signal, \(x_{2}[n] = x_{2}[-n]\). we have
+
+\begin{equation*}
+x_{1}[n]x_{2}[n] = -x_{1}[-n]x_{2}[-n] \\
+\end{equation*}
+
+i.e. \(x_{1}[n]x_{2}[n]\) is an odd signal.
+
+\textbf{Problem 1.34c}
+
+\begin{eqnarray*}
+x_{e}[n] &=& \frac{x[n] + x[-n]}{2} \\
+x_{o}[n] &=& \frac{x[n] - x[-n]}{2}
+\end{eqnarray*}
+Then we have
+\begin{eqnarray*}
+\sum_{n=-\infty}^{+\infty} x_{e}^{2}[n]  &=& \sum_{n=-\infty}^{+\infty} \bigg(  \frac{ x[n] + x[-n] }{2} \bigg)^{4}   \\
+&=& \sum_{n=-\infty}^{+\infty} \bigg(  \frac{ x^{2}[n]  + x^{2}[-n] + 2x[n]x[-n]}{2} \bigg)
+\end{eqnarray*}
+\begin{eqnarray*}
+\sum_{n=-\infty}^{+\infty} x_{o}^{2}[n]  &=& \sum_{n=-\infty}^{+\infty} \bigg(  \frac{ x[n] - x[-n] }{2} \bigg)^{2}   \\
+&=& \sum_{n=-\infty}^{+\infty} \bigg(  \frac{ x^{2}[n]  + x^{2}[-n] - 2x[n]x[-n]}{4} \bigg)
+\end{eqnarray*}
+Then we add the above two equations and get
+\begin{eqnarray*}
+\sum_{n=-\infty}^{+\infty} x_{e}^{2}[n] +  \sum_{n=-\infty}^{+\infty} x_{o}^{2}[n]  &=& \sum_{n=-\infty}^{+\infty} \frac{x^{2}[n] + x^{2}[-n]}{2} \\
+&=& \sum_{n=-\infty}^{+\infty} x^{2}[n]
+\end{eqnarray*}
+
+This conclusion tells us that even we seperate the signal into two parts(even
+part and odd part), the sum of energy from the even part and odd part is the
+total energy of the original signal.
+
+Let
+\begin{eqnarray*}
+\int_{-\infty}^{+\infty} x^{2}(t) dt &=& \int_{-\infty}^{+\infty} ( x_{e}(t) + x_{o}(t) )^{2}dt  \\
+&=& \int_{-\infty}^{+\infty} x_{e}^{2}(t)dt + \int_{-\infty}^{+\infty} x_{o}^{2}(t) dt + \int_{-\infty}^{+\infty} x_{e}(t)x_{o}(t) dt \\
+&=& \int_{-\infty}^{+\infty} x_{e}^{2}(t)dt + \int_{-\infty}^{+\infty} x_{o}^{2}(t) dt
+\end{eqnarray*}
+
+Notice that \(x_{e}(t)x_{o}(t)\) is and odd signal, so \(\int_{-\infty}^{+\infty} x_{e}(t)x_{o}(t) dt = 0\)
+\section{Problem 1.35}
+\label{sec:orgcf4d953}
+
+\begin{prob}[]{prob:1-35}
+Consider the periodic discrete-time exponential time signal
+\begin{equation*}
+x[n] = e^{im(2\pi/N)n}
+\end{equation*}
+Show that the fundamental period of this signal is
+\begin{equation*}
+N_{0} = N / \mathrm{gcd}(m,N)
+\end{equation*}
+where \(\mathrm{gcd}(m,N)\) is the greatest common divisor of \(m\) and
+\(N\)----that is, the largest integer that divides both \(m\) and \(N\) an
+integral number of times. For example,
+\begin{equation*}
+\mathrm{gcd}(2,1) = 1, \mathrm{gcd}(2,4) = 2, \mathrm{gcd}(8,12) = 4
+\end{equation*}
+Note that \(N_{0} = N\) if \(m\) and \(N\) have no factors in common.
+\label{prob:1-35}
+\end{prob}
+
+\begin{prf}[]{}
+Let \(N_{0}\) the fundamental period of \(x[n]\), so that
+\begin{equation*}
+m(2\pi / N) N_{0} = l\times 2\pi
+\end{equation*}
+So, we have \(N_{0} = \frac{lN}{m}\) . If \(m\) and \(N\) have no factors in
+common, we have \(N_{0} = N\) when \(l = m\). If \(m\) and \(N\) have factors in
+common, the fundamental period should be
+\begin{equation*}
+N_{0} = l \frac{N/ \mathrm{gcd}(m,N) }{m/ \mathrm{gcd}(m,N)}
+\end{equation*}
+
+When \(l = m/ \mathrm{gcd}(m,N)\), we have \(N_{0} = \frac{N}{ \mathrm{gcd}(m,N) }\).
+\end{prf}
 \end{document}

### 2020-02-11 mstemc/mstemc.tex
trivial update

--- 2020-01-08 mstemc/mstemc.tex
@@
 \usepackage{tikz}
-\usetikzlibrary{arrows,decorations.pathmorphing,,backgrounds,positioning,fit,petri,calc,intersections,through,shapes.misc,mindmap,calendar,shadows,mindmap,calendar,graphdrawing,trees}
-               \usepackage{tikz}
+\usetikzlibrary{arrows,decorations.pathmorphing,,backgrounds,positioning,fit,petri,calc,intersections,through,shapes.misc,mindmap,calendar,shadows,mindmap,calendar,graphdrawing,trees,shapes.misc,quotes,angles}
+\definecolor{mycolor}{RGB}{139,0,0}
 \author{Eason}
 \date{\today}
-\title{Basic Problems With Answers}
+\title{Problem 1.21}
 \hypersetup{
  pdfauthor={Eason},
- pdftitle={Basic Problems With Answers},
+ pdftitle={Problem 1.21},
  pdfkeywords={},
@@
 
-\begin{prob}[]{prob:1.1}
-Express each of the following complex numbers in \emph{Cartesian} form \(x+iy\):
+\begin{prob}[]{prob:1-21}
+A continuout-time signal \(x(t)\) is shown below. Sketch and label carefully
+each of the following signals:
 \begin{equation*}
-\begin{array}{ccc}
- \frac{1}{2}e^{i\pi}  & \frac{1}{2}e^{-i\pi}  & e^{i\pi/2}  \\
- e^{-i\pi/2}         & e^{i5\pi/2}  & \sqrt{2}e^{i\pi/4}  \\
- \sqrt{2}e^{i9\pi/4} & \sqrt{2}e^{-9i\pi/4}  & \sqrt{2} e^{-i\pi/4}
+\begin{array}{ll}
+\mathbf{(a)}: x(t-1) & \mathbf{(b)}: x(2-t) \\
+\mathbf{(c)}: x(2t + 1) & \mathbf{(d)}: x(4-\frac{t}{2}) \\
+\mathbf{(e)}: [x(t) + x(-t)] u(t) & \mathbf{(f)}: x(t)\delta(t +\frac{3}{2}) - \delta(t-\frac{3}{2})
 \end{array}
 \end{equation*}
-\label{prob:1.1}
+\begin{center}
+\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-21-0.pdf}
+\end{center}
+\label{prob:1-21}
 \end{prob}
 
-\begin{prob}[]{prob:1.2}
-Express each of the following complex numbers in \emph{polar} form (\(re^{i\theta},
--\pi < \theta \leq -\pi\)):
-\begin{equation*}
-\begin{array}{c{3cm}c{3cm}c{3cm}}
-5 & -2 & -3i \\
-\frac{1}{2} - i \frac{\sqrt{3}}{2} & 1+i & (1-i)^{2} \\
-i(1-i)  & \frac{1+i}{1-i}  & \frac{\sqrt{2} + i \sqrt{2}}{1+i\sqrt{3}}
-\end{array}
-\end{equation*}
-\label{prob:1.2}
-\end{prob}
+Before we figure all the sub-problem out. Let's review how \(a\) and \(b\)
+affect \(x(at+b)\) . we know that:
 
-Every complex number \(a+ib\) can be visualized in the complex plane
-\(\mathbb{C}\). It can be viewed as the point with the coordinate \((a,b)\) in
-the plane or as a vector starting from \(0,0\) to the point \((a,b)\).
+\begin{enumerate}
+\item when \(|a| < 1\), \(x(t)\) will be linearly stretched;
+\item when \(|a|>1\), \(x(t)\) will be linearly compressed;
+\item when \(a < 0\), \(x(t)\) will be reversed;
+\item when \(b\neq 0\) , \(x(t)\) will be shifted in time.
+\item when \(a>0, b>0\), \(x(t)\) will be shifted left.
+\item when \(a>0,b<0\), \(x(t)\) will be shifted right.
+\item when \(a<0,b>0\), \(x(t)\) will be reversed first then shifted right.
+\item when \(a<0,b<0\), \(x(t)\) will be reversed first, then shifted left.
+\end{enumerate}
 
-Also every complex number \(a+ib\) can be represented in the exponential form
-conveniently through the Euler's formula \(e^{i\alpha} = \cos\alpha +
-i\sin\alpha\).
+\textbf{Problem 1.21a}
+
+Based on the conclusion given above, we know that \(x(t-1)\) can be obtained by right
+shifting \(x(t)\) with step \(1\). So the result can be visualized as follows.
 
 \begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/eulerEquation.pdf}
+\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-21a.pdf}
+\end{center}
+
+\textbf{Problem 1.21b}
+
+For \(x(2-t)\), we re-write it as \(x(-(t-2))\) which can be obtained by first
+reversing \(x(t)\) then right shifting it with step \(2\). The result can be
+shown as follows
+
+\begin{center}
+\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProblem1-21b.pdf}
+\end{center}
+
+\textbf{Problem 1.21c}
+
+\(x(2t + 1)\) can be re-written as \(x(2(t+\frac{1}{2}))\) which means that
+\(x(2t+1)\) can be obtained by first linearly compressing \(x(t)\) with factor 2
+then left shifting compressed signal by \(\frac{1}{2}\).
+
+\begin{center}
+\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-21c.pdf}
+\end{center}
+
+\textbf{Problem 1.21d}
+
+\(x(4-\frac{t}{2})\) can be re-written as \(x( -\frac{1}{2}( t - 8 ) )\) which
+means that \(x(4-\frac{t}{2})\)  can be obtained by first linearly stretching
+\(x(t)\) by factor \(2\) then right shifting it with step \(8\).
+
+\begin{center}
+\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-21d.pdf}
+\end{center}
+
+\textbf{Problem 1.21e}
+
+At first glance, \(\big[x(t) + x(-t)\big] u(t)\) is \(0\) if \(t<0\) .
+
+If \(t > 0\), we have to figure out \(x( -t )\). After obtaining \(x(-t)\), we
+add the right part of \(x(t)\) and left part of \(x(-t)\) then we have \([x(t) +
+x(-t)]u(t)\)
+
+\begin{center}
+\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProblem1-21e.pdf}
+\end{center}
+
+\(x(t)\delta(t +\frac{3}{2}) - \delta(t-\frac{3}{2})\) only have two points with
+non-negative values: \(t=\frac{3}{2}\) and \(t=-\frac{3}{2}\).
+
+\begin{center}
+\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-21f.pdf}
 \end{center}

### 2020-02-18 mstemc/index.tex
trivial modification

@@
 
+ \thispagestyle{empty}
+ \begingroup
+\begin{center}
+ \vspace{\baselineskip}
+ \textbf{\Huge Signals and Systems Chapter 1 Problems Part 3 (1.32-1.47)} \par
+ \vspace{2\baselineskip}  \newline
+ \textbf{\large Eason Zhang with www.makesteamclear.com \par}
+ \vspace{\baselineskip} \newline
+  \today \par
+ \vspace{\baselineskip}
+  \vfill
+ \setlength{\unitlength}{3pt}
+ \includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-21-0.pdf}
+ \vfill \vspace{\baselineskip}
+ \href{WWW.MAKESTEAMCLEAR.COM}{\Large WWW.MAKESTEAMCLEAR.COM} \par\newline
+  makesteamclear is a free project, run by Eason Zhang, to make videos about STEAM in a more approachable way.
+If you find the contents in this article or the site or the youtube channel helpful, please consider \href{www.makesteamclear.com}{\ensuremath \heartsuit support me\ensuremath\heartsuit }, thanks \par
+ \end{center}
+ \endgroup
+
+ \newpage \thispagestyle{empty} \textbf{copyright page} \newpage \tableofcontents \newpage
+\hspace{0pt}\\
+
+This post consists of solutions to problems from 1.21 to 1.31 in chapter 1 of the book Signals and Systems by Oppenheim ,Willsky and Nawab.\cite{oppenheim_signals_1997}
+
+ \thispagestyle{empty}
+ \begingroup
+\begin{center}
+ \vspace{\baselineskip}
+ \textbf{\Huge Signals and Systems Chapter 1 Problems Part 3 (1.32-1.47)} \par
+ \vspace{2\baselineskip}  \newline
+ \textbf{\large Eason Zhang with www.makesteamclear.com \par}
+ \vspace{\baselineskip} \newline
+  \today \par
+ \vspace{\baselineskip}
+  \vfill
+ \setlength{\unitlength}{3pt}
+ \includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-47d.pdf}
+ \vfill \vspace{\baselineskip}
+ \href{WWW.MAKESTEAMCLEAR.COM}{\Large WWW.MAKESTEAMCLEAR.COM} \par\newline
+  makesteamclear is a free project, run by Eason Zhang, to make videos about STEAM in a more approachable way.
+If you find the contents in this article or the site or the youtube channel helpful, please consider \href{www.makesteamclear.com}{\ensuremath \heartsuit support me\ensuremath\heartsuit }, thanks \par
+ \end{center}
+ \endgroup
+
+ \newpage \thispagestyle{empty} \textbf{copyright page} \newpage \tableofcontents \newpage
+\hspace{0pt}\\
+
+This post consists of solutions to problems from 1.21 to 1.31 in chapter 1 of the book Signals and Systems by Oppenheim ,Willsky and Nawab.\cite{oppenheim_signals_1997}
+
 \section{Problem 1.32}
-\label{sec:org919e435}
+\label{sec:orgfc1022f}
 
@@
 \section{Problem 1.33}
-\label{sec:org7dadf9d}
+\label{sec:orgc6b726e}
 
@@
 \section{Problem 1.34}
-\label{sec:org20cd069}
+\label{sec:org4fc36d2}
 
@@
 \section{Problem 1.35}
-\label{sec:orgcf4d953}
+\label{sec:orgd2ae89c}
 
@@
 \end{prf}
+\section{Problem 1.36}
+\label{sec:org4a7f30f}
+
+\begin{prob}[]{prob:1-36}
+Let \(x(t)\) be the continuous-time complex exponential signal:
+\begin{equation*}
+x(t) = e^{i\omega_{0}t}
+\end{equation*}
+with fundamental frequency \(\omega_{0}\) and fundamental period \(T_{0} =
+    2\pi /\omega_{0}\). Consider the discrete-time signal obtained by taking
+equally spaced samples of \(x(t)\) --- that is,
+\begin{equation*}
+x[n] = x(nT) = e^{i\omega_{0}nT}
+\end{equation*}
+
+\begin{enumerate}
+\item Show that \(x[n]\) is periodic if and only if \(T/T_{0}\) is a rational
+number -- that is, if and only if some multiple of the sampling interval
+exactly equals a multiple of the period of \(x(t)\).
+\item Suppose that \(x[n]\) is periodic --- that is, that
+\begin{equation}
+\label{eq:1-36-1}
+\frac{T}{T_{0}} = \frac{p}{q}
+\end{equation}
+where \(p\) and \(q\) are integers. What are the fundamental period and
+fundamental frequency of \(x[n]\)? Express the fundamental frequency as a
+fraction of \(\omega_{0}T\)
+\item Again assuming that \(T/T_{0}\) satisfies eq (\ref{eq:1-36-1}), determine
+precisely how many periods of \(x(t)\) are needed to obtain the samples
+that form a single period of \(x[n]\).
+\end{enumerate}
+\label{prob:1-36}
+\end{prob}
+
+\textbf{Problem 1.36a}
+
+\begin{prf}[]{}
+Let \(N\) the fundamental period of \(x[n]\), then we have
+\begin{equation*}
+\omega_{0} N T = 2\pi m
+\end{equation*}
+So \(N = \frac{2\pi m}{\omega_{0}T}\), We also have \(T_{0}=
+\frac{2\pi}{\omega_{0}}\), then
+\begin{equation*}
+N = m\frac{T_{0}}{T}
+\end{equation*}
+Then \(\frac{T_{0}}{T}\) must be a rational number so that \(m\frac{T_{0}}{T}\)
+is an integer and \(N\) could be an integer i.e. \(x[n]\) is periodic.
+\end{prf}
+
+\textbf{Problem 1.36b}
+
+Based on the analysis of Problem 1.36a, we have fundamental period of \(x[n]\)
+\begin{equation*}
+N = m\frac{T_{0}}{T} = m \frac{q}{p}
+\end{equation*}
+Where \(m\) is the minimum integer so that \(N\) is an integer. Based on the
+conclusion of \hyperref[sec:orgd2ae89c]{Problem 1.35} , we can re-express \(N\) as
+\begin{equation*}
+N = \frac{q}{\mathrm{gcd}(p,q)}
+\end{equation*}
+Where \(m = \frac{p}{\mathrm{gcd}(p,q)}\).
+The fundamental frequency is
+\begin{equation*}
+\frac{2\pi}{N} = \frac{2\pi \mathrm{gcd}(p,q)}{q} = \omega_{0}T_{0} \frac{\mathrm{gcd}(p,q)}{q} = \omega_{0}T\frac{\mathrm{gcd}(p,q)}{p}
+\end{equation*}
+
+\textbf{Problem 1.36c}
+
+The fundamental period of \(x(t)\) is \(T_{0} = \frac{2\pi}{\omega_{0}}\) and
+\(x[n]\) , \(N= \frac{q}{\mathrm{gcd}(p,q)}\). we have
+
+\begin{equation*}
+\frac{N}{T_{0}}= \frac{Np}{Tq} = \frac{q}{\mathrm{gcd}(p,q)T} \frac{p}{q} = \frac{p}{\mathrm{gcd}(p,q)T}
+\end{equation*}
+So, the discrete-time version of signal \(x(t)\) need at least
+\(\frac{p}{\mathrm{gcd}(p,q)T}\) periods of \(x(t)\) to obtain one period of \(x[n]\).
+
+Let's talk more about this problem. This problem preliminary discloses the concept
+of sampling which is a main method of obtaining discrete-time signal from
+continuous-time signal. Now let's put Nyquist's sampling theory aside and focus
+on the sampling itself.
+
+Suppose we have a continuous-time signal
+\begin{equation*}
+x(t) = \cos(4\pi t)
+\end{equation*}
+whose fundamental period is \(T_{0} = \frac{2\pi }{4\pi} = \frac{1}{2}\). Then
+the sampling interval \(T\) must satisfies that \(T/T_{0}\) is a rational
+number so that \(x[n]= x(nT)= \cos(4\pi nT )\) is a periodic signal.
+
+Let \(T\), say, be \(\frac{1}{5}\), then
+\begin{equation*}
+\frac{T}{T_{0}} = \frac{2}{5}
+\end{equation*}
+The fundamental period of \(x[n]\) is \(N = \frac{q}{\mathrm{gcd}(p,q)} =
+\frac{5}{\mathrm{gcd}(2,5)} = 5\).
+
+We can visualize \(x(t)\) and \(x[n]\) as below.
+
+\begin{center}
+\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-36-1.pdf}
+\end{center}
+
+From the above figure, we can see that the discrete-time signal \(x[n]\) has
+fundamental period of \(5\) and its counterparts has fundamental period
+\(\frac{1}{2}\). We need at least \(10\) period of \(x(t)\) to get one period of
+\(x[n]\).
+
+Now, if we take the Nyquist's sampling into consideration, we must sampling a
+baseband signal with at least two times higher frequency of the signal to
+recover the baseband signal without alias. i.e. we must sample \(x(t) =
+\cos(4\pi t)\) with a signal of fundamental frequency \(8\pi\) to get signal
+\(x[n] = \cos(8\pi n)\).
+\section{Problem 1.37}
+\label{sec:org5b0c999}
+
+\begin{prob}[]{prob:1-37}
+An important concept in many communications applications in the correlation
+between two signals. In the problems at the end of Chapter 2, we will have
+more to say about this topic and will provide some indication of how it is
+used in practice. For now, we content ourselves with a brief introduction to
+correlation functions and some of their properties.
+
+Let \(x(t)\) and \(y(t)\) be two signals; then the correlation function is
+defined as
+\begin{equation*}
+\phi_{xy}(t) = \int_{-\infty}^{+\infty} x(t+ \tau) y(\tau)d\tau
+\end{equation*}
+
+The function \(\phi_{xx}(t)\) is usually referred to as the autocorrelation
+function of the signal \(x(t)\) , while \(\phi_{xy}(t)\) is often called a
+cross-correlation function.
+
+\begin{enumerate}
+\item What is the relationship between \(\phi_{xy}(t)\) and \(\phi_{yx}(t)\) ?
+\item Compute the odd part of \(\phi_{xx}(t)\).
+\item Suppose that \(y(t)= x(t+ T)\). Express \(\phi_{xy}(t)\) and
+\(\phi_{yy}(t)\) in terms of \(\phi_{xx}(t)\).
+\end{enumerate}
+\label{prob:1-37}
+\end{prob}
+
+\textbf{Problem 1.37a} \label{Problem 1.37a}
+
+by the definition of correlation, we have
+\begin{equation*}
+\phi_{yx} = \int_{-\infty}^{+\infty} y(t + \tau)x(\tau) d \tau
+\end{equation*}
+
+we set \(t+ \tau = s\), then
+\begin{eqnarray*}
+\phi_{yx}(t) &=& \int_{-\infty}^{+\infty} y(t + \tau)x(\tau) d \tau \\
+&=& \int_{-\infty}^{+\infty} x(s-t) y(s) ds \\
+&=& \phi_{xy}(-t)
+\end{eqnarray*}
+
+Using the same procedure, we can also have \(\phi_{xy}(t) = \phi_{yx}(-t)\).
+
+\textbf{Problem 1.37b}
+
+we have
+\begin{equation*}
+\phi_{xx}(t) = \int_{-\infty}^{+\infty} x(t+\tau)x(\tau) d\tau
+\end{equation*}
+the odd part of \(\phi_{xx}(t)\) can be expressed as
+\begin{equation*}
+\phi_{oxx}(t) = \frac{\phi_{xx}(t) - \phi_{xx}(-t)}{2}
+\end{equation*}
+
+Based on \hyperref[Problem 1.37a]{Problem 1.37a}, we have \(\phi_{xx}(t) = \phi_{xx}(-t)\) , so
+\(\phi_{oxx}(t) = 0\). which means that \(\phi_{oxx}(t)\) is an even signal.
+
+\textbf{Problem 1.37c}
+
+\begin{eqnarray*}
+\phi_{xy}(t) &=& \int_{-\infty}^{+\infty} x(t+ \tau) y(\tau)d\tau \\
+&=& \int_{-\infty}^{+\infty} x(t+ \tau) x(\tau + T)d\tau \\
+&=& \int_{-\infty}^{+\infty} x(t + s -T) x(s) ds
+\end{eqnarray*}
+So we have \(\phi_{xy}(t) = \phi_{xx}(t-T)\).
+
+\begin{eqnarray*}
+\phi_{yy}(t) &=& \int_{-\infty}^{+\infty} y(t+ \tau) y(\tau)d\tau \\
+&=& \int_{-\infty}^{+\infty} x(t+ \tau + T) x(\tau + T)d\tau \\
+&=& \int_{-\infty}^{+\infty} x(t + s) x(s) ds
+\end{eqnarray*}
+So we have \(\phi_{yy}(t) = \phi_{xx}(t)\).
+\section{Problem 1.38}
+\label{sec:orgef628d7}
+
+\begin{prob}[]{prob:1-38}
+In this problem, we examine a few of the properties of the unit impulse
+function.
+\begin{enumerate}
+\item show that
+\begin{equation*}
+\delta(2t) = \frac{1}{2} \delta(t)
+\end{equation*}
+Hint: Examine \(\delta_{\Delta}(t)\). (See Figure 1.34 in the textbook).
+\item In Section 1.4, we defined the continuous-time unit impulse as the limit
+of the signal \(\delta_{\Delta}(t)\). More precisely, we defined several
+of the properties of \(\delta(t)\) by examining the corresponding
+properties of \(\delta_{\Delta}(t)\). For example, since the signal
+\begin{equation*}
+u_{\Delta}(t) = \int_{-\infty}^{t}\delta_{\Delta}(\tau)d\tau
+\end{equation*}
+converges to the unit step:
+\begin{equation*}
+u(t) = \lim_{\Delta\to 0} u_{\Delta}(t),
+\end{equation*}
+we could interpret \(\delta(t)\) through the equation
+\begin{equation}
+\label{eq:problem1-38-1}
+u(t) = \int_{-\infty}^{t} \delta(\tau)d\tau
+\end{equation}
+or by viewing \(\delta(t)\) as the formal derivative of \(u(t)\).
+
+This type of discussion is important, as we are in effect trying to
+define \(\delta(t)\) through its properties rather than by specifying its
+value for each \(t\), which is not possible. In Chapter 2, we provide a
+very simple characterization of the behavior of the unit impulse that is
+extremely useful in the study of linear time-invariant systems. For the
+present, however, we concentrate on demonstrating that the important
+concept in using the unit impulse is to understand how it behave. To do
+this, consider the six signals depicted in Figure shown below. Show that
+each "behaves like an impulse" as \(\Delta\to 0\) in that, if we let
+\begin{equation*}
+u_{\Delta}^{i}(t) = \int_{-\infty}^{t} r_{\Delta}^{i}(\tau)d\tau,
+\end{equation*}
+then
+\begin{equation*}
+\lim_{\Delta\to 0} u_{\Delta}^{i}(t) = u(t)
+\end{equation*}
+In each case, sketch and label carefully the signal
+\(u_{\Delta}^{i}(t)\). Note that
+\begin{equation*}
+r_{\Delta}^{2}(0) = r_{\Delta}^{4}(0) = 0 \ \forall \Delta
+\end{equation*}
+Therefore, it is not enough to define or to think of \(\delta(t)\) as
+being zero for \(t\neq 0\) and infinite for \(t=0\). Rather, it is
+properties such as equation (\ref{eq:problem1-38-1}) that define the
+impulse. In Section 2.5 we will define a whole class of signals known as
+singularity function, which are related to the unit impulse and which are
+also defined in terms of their properties rather than their values.
+
+\begin{center}
+\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-38-2.pdf}
+\end{center}
+\end{enumerate}
+\label{prob:1-38}
+\end{prob}
+
+\begin{center}
+\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-38-0.pdf}
+\label{figProb1-38-0}
+\end{center}
+
+\textbf{Problem 1.38a}
+
+Base on fig \ref{figProb1-38-0} , \(\delta(2t)\) can be visualized as follows
+
+\begin{center}
+\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-38-1.pdf}
+\end{center}
+
+Based on the fact \(\delta(t)\) has unit area, so \(\delta(2t)\) will have
+\(\frac{1}{2}\) . So \(\delta(2t) = \frac{1}{2}\delta(t)\).
+
+\textbf{Problem 1.38b}
+
+Because
+\begin{equation*}
+u_{\Delta}(t) = \int_{-\infty}^{t}\delta_{\Delta}(\tau)d\tau
+\end{equation*}
+We can get \(u_{\Delta}^{1}(t)\) easily.
+
+\(r_{\Delta}^{1}(t)\) can be represented as
+\begin{equation*}
+r_{\Delta}^{1}(t) =
+\begin{cases}
+\frac{1}{\Delta}, & -\frac{\Delta}{2} \leq t \leq \frac{\Delta}{2} \\
+               0, & \mathrm{Otherwise}
+\end{cases}
+\end{equation*}
+
+Then during the integration, \(u_{\Delta}^{1}(t)\) can be represented as
+\begin{equation*}
+u_{\Delta}^{1}(t) =
+\begin{cases}
+0, &  t < -\frac{\Delta}{2} \\
+\frac{t}{\Delta}, & -\frac{\Delta}{2} \leq t \leq \frac{\Delta}{2} \\
+1, & t > \frac{\Delta}{2}
+\end{cases}
+
+\end{equation*}
+
+\begin{center}
+\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-38b.pdf}
+\end{center}
+
+we can express the \(r_{\Delta}^{2}(t)\) as :
+\begin{equation*}
+r_{\Delta}^{2}(t) =
+\begin{cases}
+\frac{1}{\Delta} , & \Delta \leq t \leq 2\Delta \\
+0, & \mathrm{Otherwise}
+\end{cases}
+\end{equation*}
+
+So the \(u_{\Delta}^{2}(t)\) can be expressed as:
+\begin{equation*}
+u_{\Delta}^{2}(t) =
+\begin{cases}
+0, & t < \Delta \\
+\frac{t-\Delta}{\Delta} & \Delta \leq t \leq 2\Delta \\
+1, & t> 2\Delta
+\end{cases}
+\end{equation*}
+\begin{center}
+\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-38c.pdf}
+\end{center}
+
+We express \(r_{\Delta}^{3}(t)\) as:
+\begin{equation*}
+r_{\Delta}^{3}(t) =
+\begin{cases}
+\frac{1}{\Delta^{2}} ( t +  \Delta) , & - \Delta < t \leq 0 \\
+\frac{1}{\Delta^{2}} ( -t + \Delta) , & 0 < t \leq \Delta \\
+0, & \mathrm{otherwise}
+\end{cases}
+\end{equation*}
+and \(u_{\Delta}^{3}(t)\):
+
+\begin{equation*}
+u_{\Delta}^{3}(t) =
+\begin{cases}
+\frac{1}{\Delta^{2}}( \frac{t^{2}}{2} + \Delta t + \frac{\Delta^{2}}{2}) ,& -\Delta < t \leq  0 \\
+\frac{1}{2} + \frac{1}{\Delta^{2}} ( - \frac{t^{2}}{2} + \Delta t ) , & 0 < t < \Delta \\
+1, & t > \Delta
+\end{cases}
+\end{equation*}
+
+So we can visualize them as follows:
+
+\begin{center}
+\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-38d.pdf}
+\end{center}
+
+We can represent \(r_{\Delta}^{4}(t)\) as :
+\begin{equation*}
+r_{\Delta}^{4}(t) =
+\begin{cases}
+- \frac{1}{\Delta^{2}} t , &  -\Delta < t \leq 0 \\
+\frac{1}{\Delta^{2}} t , &   0 < t \leq \Delta  \\
+0, & \mathrm{Otherwise}
+\end{cases}
+\end{equation*}
+
+and \(u_{\Delta}^{4}(t)\)
+
+\begin{equation*}
+u_{\Delta}^{4}(t) =
+\begin{cases}
+0, &  t < -\Delta \\
+- \frac{t^{2}}{2\Delta^{2}} + \frac{1}{2}, & - \Delta < t \leq 0\\
+ \frac{t^{2}}{2\Delta^{2}} + \frac{1}{2}, & - \Delta < t \leq 0\\
+1, & t > \Delta
+\end{cases}
+\end{equation*}
+and we visualize them as:
+
+\begin{center}
+\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-38e.pdf}
+\end{center}
+
+We can express \(r_{\Delta}^{5}(t)\) as :
+\begin{equation*}
+r_{\Delta}^{5}(t) =
+\begin{cases}
+- \frac{1}{\Delta} , & -\Delta < t \leq 0 \\
+\frac{2}{\Delta} , & 0 < t \leq \Delta \\
+0, & \mathrm{Otherwise}
+\end{cases}
+\end{equation*}
+
+and \(u_{\Delta}^{5}(t)\) as:
+
+\begin{equation*}
+u_{\Delta}^{5}(t) =
+\begin{cases}
+- \frac{t}{\Delta} -1, & -\Delta < t < 0 \\
+-1 + \frac{2t}{\Delta} , & 0 < t \leq \Delta \\
+1,& t > \Delta
+\end{cases}
+\end{equation*}
+So we can visualize them as below:
+
+\begin{center}
+\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-38f.pdf}
+\end{center}
+
+We can express \(r_{\Delta}^{6}(t)\) as :
+\begin{equation*}
+r_{\Delta}^{6}(t) = \frac{1}{2\Delta} e^{-|t|/\Delta}
+\end{equation*}
+
+and \(u_{\Delta}^{6}(t)\) as :
+\begin{equation*}
+u_{\Delta}^{6}(t) =
+\begin{cases}
+\frac{1}{2} e^{\frac{t}{\Delta}} , & t< 0 \\
+1 - \frac{1}{2}e^{ \frac{-t}{\Delta}} , & t> 0 \\
+\end{cases}
+\end{equation*}
+So we can visualize them as below:
+\begin{center}
+\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-38g.pdf}
+\end{center}
+\section{Problem 1.39}
+\label{sec:org95fdb02}
+
+\begin{prob}[]{prob:1-39}
+The role played by \(u(t)\) and \(\sigma(t)\) and other singularity
+functions in the study of linear time-invariant systems is that of an
+idealization of a physical phenomenon, and, as we will see, the use of these
+idealizations allow us to obtain an exceedingly important and very simple
+representation of such systems. In using singularity functions, we need,
+however, to be careful. In particular, we must remember that they are
+idealizations, and thus, whenever we perform a calculation using them, we
+are implicitly assuming that this calculation represents an accurate
+description of the behavior of the signals that they are intended to
+idealize. To illustrate, consider the equation
+\begin{equation}
+\label{eq:prob1-39-0}
+x(t)\sigma(t) = x(0)\sigma(t)
+\end{equation}
+This equation is based on the observation that
+\begin{equation}
+\label{eq:prob1-39-1}
+x(t)\sigma_{\Delta}(t) \approx x(0)\sigma_{\Delta}(t)
+\end{equation}
+Taking the limit of this relationship then yields the idealized one given by
+equation (\ref{eq:prob1-39-0}). However, a more careful examination of our
+derivation of equation (\ref{eq:prob1-39-1}) shows that that equation really
+makes senses only if \(x(t)\) is continuous at \(t=0\). If it is not, then
+we will not have \(x(t)\approx x(0)\)  for \(t\) small.
+
+To make this point clearer, consider the unit step signal \(u(t)\). Recall
+from the following equation:
+\begin{equation*}
+u(t) =
+\begin{cases}
+  0, & t< 0\\
+  1, & t> 0
+\end{cases}
+\end{equation*}
+that
+
+\begin{enumerate}
+\item \(u(t)= 0\) for \(t<0\)
+\item \(u(t) = 1\) for \(t> 0\),
+\end{enumerate}
+
+but that its value at \(t=0\) is not defined. The fact that \(u(0)\) is not
+defined is not particularly bothersome, as long as the calculations we
+perform using \(u(t)\) do not rely on a specific choice for \(u(0)\). For
+example, if \(f(t)\) is a signal that is continuous at \(t=0\), then the
+value of
+\begin{equation*}
+\int_{-\infty}^{+\infty} f(\sigma) u(\sigma) d \sigma
+\end{equation*}
+does not depend upon a choice for \(u(0)\). On the other hand, the fact that
+\(u(0)\) is undefined is significant in that it means that certain
+calculations involving singularity functions are undefined. Consider trying
+to define a value for the product \(u(t)\delta(t)\).
+
+To see that this cannot be defined, show that
+\begin{equation*}
+\lim_{\Delta\to 0} [u_{\Delta}(t)\delta(t)] = 0,
+\end{equation*}
+but
+\begin{equation*}
+\lim_{\Delta\to 0} [u_{\Delta}(t)\delta_{\Delta}(t)] = \frac{1}{2} \delta(t)
+\end{equation*}
+
+In general, we can define the product of two signals without any difficulty,
+as long as the signals do not contain  singularities  ( discontinuities,
+impulse, or the other singularities introduced in Section 2.5) whose
+locations coincide. When the locations do coincide, the product is
+undefined. As an example, show that the signal
+\begin{equation*}
+g(t) = \int_{-\infty}^{+\infty} u( \tau )\delta(t-\tau)d\tau
+\end{equation*}
+is identical to \(u(t)\); that is, it is \(0\) for \(t < 0\), it equals
+\(1\) for \(t> 0\), and it is undefined for \(t=0\)
+\label{prob:1-39}
+\end{prob}
+
+\begin{equation*}
+\lim_{\Delta\to 0} [u_{\Delta}(t)\delta(t)] = \lim_{\Delta\to 0} [u_{\Delta}(t)\delta(0)] = 0
+\end{equation*}
+
+And
+\begin{eqnarray*}
+\lim_{\Delta\to 0} [u_{\Delta}(t)\delta_{\Delta}(t)] &=& \lim_{\Delta\to 0 } \frac{1}{2} \frac{d u_{\Delta}^{2}(t)}{dt} \\
+&=& \frac{1}{2} \delta(t)
+\end{eqnarray*}
+Notice that when \(\Delta\to 0\) the item  \(\frac{u_{\Delta}^{2}(t)}{dt}\)
+also approach to \(\delta(t)\).
+
+for equation:
+\begin{equation*}
+g(t) = \int_{-\infty}^{+\infty} u( \tau )\delta(t-\tau)d\tau
+\end{equation*}
+we have
+\begin{equation*}
+g(t) =
+\begin{cases}
+0, & t< 0 \\
+1, & t> 0 \\
+\mathrm{undefined}, & t = 0
+\end{cases}
+
+\end{equation*}
+So \(g(t)\) has the same property as \(u(t)\)
+\section{Problem 1.40}
+\label{sec:org71282a6}
+
+\begin{prob}[]{prob:1-40}
+\begin{enumerate}
+\item Show that if a system is either additive or homogeneous, it has the
+property that if the input is identically zero, then the output is also
+identically zero.
+\item Determine a system (either in continuous or discrete time) that is
+neither additive nor homogeneous but which has a zero output if the input
+is identically zero.
+\item From part (a) can you include that if the input to a linear system is
+zero  between times \(t_{1}\) and \(t_{2}\) in continuous time or between
+times \(n_{1}\) and \(n_{2}\) in descrete time, then its output must also
+be zero between these same times? Explain your answer.
+\end{enumerate}
+\label{prob:1-40}
+\end{prob}
+
+\textbf{Problem 1.40a}
+
+\begin{prf}[]{}
+Let \(x_{1}(t)\) and \(x_{2}(t)\) be two input signals of system
+\(\mathcal{S}\), and \(y_{1}(t)\) and \(y_{2}(t)\) two output respectively. The
+system is represented as \(y(t) = f(x(t))\). Then
+\begin{eqnarray*}
+y_{1}(t)&=& f(x_{1}(t)) \\
+y_{2}(t)&=& f(x_{2}(t))
+\end{eqnarray*}
+Let \(x_{3}(t)= x_{1}(t) + x_{2}(t)\), then by the definition of additive
+property
+\begin{equation*}
+y_{3}(t) = f(x_{3}(t)) = f(x_{1}(t) + x_{2}(t)) = y_{1}(t) + y_{2}(t)
+\end{equation*}
+If \(x_{1}(t)= x_{2}(t) = 0\) , then \(x_{3}(t) = 0\) and we have
+\begin{equation*}
+f(0) = 2f(0)
+\end{equation*}
+So, \(f(0) = 0\). i.e. If a system is additive and the input is identically
+zero, then the output is also identically zero.
+
+Next we show that if a system is homogeneous, the property also holds.
+
+Let \(x_{1}(t)\) be input signals of system \(\mathcal{S}\), and \(x_{2}(t)= \alpha
+x_{1}(t)\) another input. we have
+\(y_{1}(t) = f(x_{1}(t))\) and \(y_{2}(t) = f(x_{2}(t)) = \alpha f(x_{1}(t))\).
+If \(x_{1}(t)  = 0\), then \(x_{2}(t) = 0\) so \(y_{2}(t) = f(0) = \alpha
+f(0)\). Then we have \(f(0) = 0 = y_{2}(t)\). i.e. if a system is homogeneous
+and the input is identically zero, then the output is also identically zero.
+\end{prf}
+
+\textbf{Problem 1.40b}
+
+It is easy to construct such a system, for a continuous-time version, we have
+\(y(t) = x^{2}(t)\) and it discrete-time counterparts \(y[n] = x^{2}[n]\)
+
+We cannot reach that conclusion. Because for a system has memory, a certain
+zero period \(t_{1}\) to \(t_{2}\) does not result the same zero period in the
+output. Let's take \(y[n] = x[n-n_{0}]\) where \(n_{0}\neq 0\), the output will
+have a delay ( \(n_{0}\) is positive) and an advance ( \(n_{0}\) is negative).
+\section{Problem 1.41}
+\label{sec:orgb5785da}
+
+\begin{prob}[]{prob:1-41}
+Consider a system \(\mathcal{S}\) with input \(x[n]\) and output \(y[n]\)
+related by
+\begin{equation*}
+y[n] = x[n]\{ g[n] + g[n-1] \}
+\end{equation*}
+
+\begin{enumerate}
+\item If \(g[n] = 1\) for all \(n\), show that \(S\) is time invariant.
+\item If \(g[n] = n\) , show that \(\mathcal{S}\) is not time invariant.
+\item If \(g[n] = 1 + (-1)^{n}\), show that \(\mathcal{S}\) is time invariant.
+\end{enumerate}
+\label{prob:1-41}
+\end{prob}
+
+\textbf{Problem 1.41a}
+
+If \(g[n] = 1 \forall \ n\) , then we have
+\begin{equation*}
+y[n] = 2x[n]
+\end{equation*}
+
+Next, we proof that this system is time invariant. Let \(x_{1}[n]\) and
+\(y_{1}[n]\) are the input and output respectively i.e.
+\begin{equation*}
+y_{1}[n] = 2x_{1}[n]
+\end{equation*}
+Let \(x_{2}[n] = x_{1}[n-n_{0}]\) then we have
+\begin{equation*}
+y_{2}[n] = 2x_{2}[n] = 2x_{1}[n-n_{0}] = 2y_{1}[n-n_{0}]
+\end{equation*}
+So we have that one time shift in the input signal will result in an identical
+time shift in the output. The system is time invariant.
+
+if \(g[n] = n\), we have
+\begin{equation*}
+y[n] = (2n-1) x[n]
+\end{equation*}
+
+Let \(x_{1}[n]\) and \(y_{1}[n]\) the input and output respectively, i.e.
+\begin{equation*}
+y_{1}[n] = (2n-1)x_{1}[n]
+\end{equation*}
+
+Let \(x_{2}[n] = x_{1}[n-n_{0}]\), then we have
+\begin{equation*}
+y_{2}[n] = (2n-1)x_{2}[n] = (2n-1)x_{1}[n-n_{0}]
+\end{equation*}
+
+We also have:
+\begin{equation*}
+y_{1}[n-n_{0}] = ( 2(n-n_{0}) ) x_{1}[n-n_{0}]
+\end{equation*}
+Obviously, \(y_{2}[n]\neq y_{1}[n-n_{0}]\). The system is time invariant.
+
+If \(g[n] = 1 + (-1)^{n}\), then
+\begin{equation*}
+g[n] + g[n-1] = 1 + (-1)^{n} + 1 + (-1)^{n-1} = 2
+\end{equation*}
+
+Which means that the system is identical as the system in part (a) and hence the
+system is time invariant.
+\section{Problem 1.42}
+\label{sec:org8f471d7}
+
+\begin{prob}[]{prob:1-42}
+\begin{enumerate}
+\item Is the following statement true or false?
+
+The series interconnection of two linear time-invariant system is itself
+a linear, time-invariant system.
+
+Justify your answer.
+
+\item Is the following statement true or false?
+
+The series interconnection of two nonlinear systems is itself nonlinear.
+
+Justify your answer.
+
+\item Consider three systems with the following input-output relationships:
+
+System 1:
+
+\begin{equation*}
+ y[n] =
+ \begin{cases}
+ x[n/2], & n\ \mathrm{even} \\
+ 0, & n\ \mathrm{odd}
+ \end{cases}
+\end{equation*}
+
+System 2:
+
+\begin{equation*}
+y[n]  = x[n] + \frac{1}{2}x[n-1] + \frac{1}{4}x[n-2]
+\end{equation*}
+
+System 3:
+\begin{equation*}
+y[n] = x[2n]
+\end{equation*}
+
+Suppose that these systems are connected in series as depicted in Figure
+below. Find the input-output relationship for the overall interconnected
+system. Is this system linear? Is it time invariant?
+\end{enumerate}
+
+\begin{center}
+\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-42.pdf}
+\end{center}
+\label{prob:1-42}
+\end{prob}
+
+Let \(\mathcal{S}_{1}\) and \(\mathcal{S}_{2}\) two connected LTI system. Let
+\(x_{11}(t)\) and \(x_{12}(t)\) arbitrary signals, \(a_{1}\) and \(b_{1}\)
+arbitrary consstants.
+
+Then:
+\begin{eqnarray*}
+x_{11}(t)&\xrightarrow{\mathcal{S}_{1}} & y_{11}(t)  \\
+x_{12}(t)&\xrightarrow{\mathcal{S}_{1}} & y_{12}(t)  \\
+\end{eqnarray*}
+Let \(x_{13}(t) = a_{1} x_{11}(t) + b_{1}x_{12}(t)\), then
+\begin{equation*}
+x_{13}(t)  = a_{1} x_{11}(t) + b_{1}x_{12}(t) \xrightarrow{\mathcal{S}_{1}}  y_{13}(t) = a_{1}y_{11}(t) + b_{1} y_{12}(t)
+\end{equation*}
+
+For System \(\mathcal{S}_{2}\), we have the similar results:
+\begin{eqnarray*}
+x_{21}(t)&\xrightarrow{\mathcal{S}_{2}} & y_{21}(t)  \\
+x_{22}(t)&\xrightarrow{\mathcal{S}_{2}} & y_{22}(t)  \\
+\end{eqnarray*}
+Let \(x_{23}(t) = a_{2} x_{21}(t) + b_{2}x_{22}(t)\), then
+\begin{equation*}
+x_{23}(t)  = a_{2} x_{21}(t) + b_{2}x_{22}(t) \xrightarrow{\mathcal{S}_{2}}  y_{23}(t) = a_{2}y_{21}(t) + b_{2} y_{22}(t)
+\end{equation*}
+Because \(S_{1}\) and \(S_{2}\) are interconnected in series. So let \(x_{21}(t) = y_{11}(t)\) and \(x_{22}(t) = y_{12}(t)\) we can see the overall
+system is linear.
+
+Next we check the time invariant property of the overall system. Since
+\(\mathcal{S}_{1}\) and \(S_{2}\) are time invariant. we have
+\begin{eqnarray*}
+x_{1}(t-t_{1})&\xrightarrow{\mathcal{S}_{1}}& y_{1}(t-t_{1}) \\
+x_{2}(t-t_{2})&\xrightarrow{\mathcal{S}_{2}}& y_{2}(t-t_{2})
+\end{eqnarray*}
+Since the two systems are in series, the overall system is time invariant.
+
+False, we just take one counterexample. Consider the following two nonlinear systems.
+\begin{eqnarray*}
+y_{1}[n] &=& x_{1}[n] + 1 \\
+y_{2}[n] &=& x_{2}[n] - 1
+\end{eqnarray*}
+Since the two systems are in series. Let \(y_{1}[n] = x_{2}[n]\), then we have
+the overall system \(y_{2}[n] = x_{1}[n]\) which is linear.
+
+First we can express the interconnection of system 1 and system 2 as:
+\begin{equation*}
+y[n] =
+\begin{cases}
+x[ \frac{n}{2} ] + \frac{1}{4} x[ \frac{n-2}{2} ] , & n \ \mathrm{even} \\
+\frac{1}{2} x[ \frac{n-1}{2} ] , & n \ \mathrm{odd}
+\end{cases}
+\end{equation*}
+Then we express the interconnection of all the three systems.
+\begin{equation*}
+y[n] = x[ \tfrac{2n}{2} ] + \tfrac{1}{4} x[ \tfrac{2n-2}{2} ] = x[n] + \tfrac{1}{4} x[n-1]
+\end{equation*}
+So the system is an LTI system.
+\section{Problem 1.43}
+\label{sec:org772be8f}
+
+\begin{prob}[]{prob:1-43}
+\begin{enumerate}
+\item Consider a time-invariant system with input \(x(t)\) and output \(y(t)\).
+Show that if \(x(t)\) is periodic with period \(T\), then so is \(y(t)\).
+Show that the analogous result also holds in descrete time.
+\item Give an example of a time-invariant system and a nonperiodic input signal
+\(x(t)\) such that the corresponding output \(y(t)\) is periodic.
+\end{enumerate}
+\label{prob:1-43}
+\end{prob}
+
+\textbf{Problem 1.43a}
+
+For a time-invariant system, an arbitrary time shifting \(t_{0}\) in the input
+will result in an identical time shifting in the output. So let the \(t_{0}\) be
+the period \(T\), the the output should also be a time shifting \(T\). Because
+the system is period \(x(t) = x(t+T)\), then the output \(y(t) = y(t+T)\).
+
+For the descrete time, the conclusion also holds.
+
+Suppose that we have a system:
+\begin{equation*}
+y[n] = 1
+\end{equation*}
+Then this system is time-invariant, any input will not change the property of
+its output.
+\section{Problem 1.44}
+\label{sec:orgefef85f}
+
+\begin{prob}[]{prob:1-44}
+\begin{enumerate}
+\item Show that causality for a continuous-time linear system is equivalent to
+the following statement:
+
+For any time \(t_{0}\) and any input \(x(t)\) such that \(x(t) = 0\) for
+\(t<t_{0}\), the corresponding output \(y(t)\) must also be zero for \(t<
+       t_{0}\).
+
+The analogous statement can be made for a discrete-time linear system.
+
+\item Find a nonlinear system that satisfies the foregoing condition but is not
+causal.
+
+\item Find a nonlinear system that is causal but does not satisfy the
+condition.
+
+\item Show that invertibility for a discrete-time linear system is equivalent
+to be the following statement:
+
+The only input that produces \(y[n] = 0\) for all \(n\) is \(x[n]= 0\)
+for all \(n\).
+
+The analogous statement is also true for a continuous-time linear system.
+
+\item Find a nonlinear system that satisfies the condition of part (d) but is
+not invertible.
+\end{enumerate}
+\label{prob:1-44}
+\end{prob}
+
+\textbf{Problem 1.44a}
+
+A system is causal if the output at any time depends on values of the input at
+only the present and past times.
+
+Let's suppose that \(y(t) \neq 0, t< t_{0}\), which mean for some \(x(t) \neq
+0, t< t_{0}\). However this is not true. So for \(x(t) = 0, t< t_{0}\), it must
+be that \(y(t)= 0 , t< t_{0}\)
+
+\(y(t) = x^{2}(t)x^{2}(t+1)\) where \(x(t) = 0, t< t_{0}\).
+
+\(y(t) = x(t) + 1\)
+
+First let's proof that suppose  \(y[n] = 0, \forall n\) if \(x[n]=0 ,\forall n\)
+, then the system is invertible.
+
+let \(x_{1}[n]\) and \(x_{2}[n]\) be two arbitrary inputs and these two inputs
+lead to the same output \(y_{1}[n]\) .
+
+\begin{eqnarray*}
+x_{1}[n] &\xrightarrow{\mathcal{S}}& y_{1}[n] \\
+x_{2}[n] &\xrightarrow{\mathcal{S}}& y_{1}[n]
+\end{eqnarray*}
+Because the system is linear.
+\begin{equation*}
+x_{1}[n] - x_{2}[n] \xrightarrow{\mathcal{S}} y_{1}[n]-y_{1}[n] = 0
+\end{equation*}
+So we must have \(x_{1}[n] = x_{2}[n]\) which is not consist with the
+assumption and means that any output \(y_{1}[n]\) must have single one input.
+i.e. the system is invertible.
+
+Next we proof that for a invertible linear system, \(y[n] = 0, \forall n\) if
+and only if \(x[n] = 0, \forall n\)
+
+If \(x[n] = 0\), then we have
+\begin{eqnarray*}
+x[n] = 0 &\xrightarrow{\mathcal{S}} &y[n] \\
+\alpha x[n] = 0 &\xrightarrow{\mathcal{S}}&  \alpha y[n]
+\end{eqnarray*}
+
+where \(\alpha\) is arbitrary constants. Because the system is invertible, so
+the same input \(0\) must lead to the same output, so \(y[n]=\alpha y[n]\).
+then \(y[n] = 0\).
+
+\(y[n] = x^{m}[n] , m\neq 1 \ \mathrm{and}\ m\neq 0\)
+
+\(m=1\) \(y[n] = x[n]\) is a linear system.
+\(m=0\), \(y[n] = 1\) does satisfies that \(y[n]= 0, \forall n\)
+\section{Problem 1.45}
+\label{sec:orgb8bc776}
+
+\begin{prob}[]{prob:1-45}
+In Problem 1.37, we introduced the concept of correlation functions. It is
+often important in practice to compute the correlation function
+\(\phi_{hx}(t)\) where \(h(t)\) is a fixed given signal, but where \(x(t)\)
+may be any of a wide variety of signals. In this case, what is done is to
+design a system \(\mathcal{S}\) with input \(x(t)\) and output
+\(\phi_{hx}(t)\).
+
+\begin{enumerate}
+\item Is \(\mathcal{S}\) linear ? Is \(\mathcal{S}\) time invariant? Is
+\(\mathcal{S}\) causal? Explain your answers.
+\item Do any of your answers to part (a) change if we take as the output
+\(\phi_{xh}(t)\) rather than \(\phi_{hx}(t)\)?
+\end{enumerate}
+\label{prob:1-45}
+\end{prob}
+
+First, let's recall the definition of \(\phi_{hx}(t)\):
+\begin{equation*}
+\phi_{hx}(t) = \int_{-\infty}^{+\infty} h(t + \tau)x(\tau)d\tau
+\end{equation*}
+
+\textbf{Problem 1.37a}
+
+Let \(x_{1}(t)\) and \(x_{2}(t)\) two arbitrary input signals, and \(\alpha\)
+and \(\beta\) two arbitrary constants. Let \(x_{3}(t) = \alpha x_{1}(t) + \beta
+x_{2}(t)\), then we have
+\begin{eqnarray*}
+\phi_{hx_{1}}(t) &=& \int_{-\infty}^{+\infty} h(t+\tau)x_{1}(\tau)d\tau \\
+\phi_{hx_{2}}(t) &=& \int_{-\infty}^{+\infty} h(t+\tau)x_{2}(\tau)d\tau \\
+\phi_{hx_{3}}(t) &=& \int_{-\infty}^{+\infty} h(t+\tau)x_{3}(\tau)d\tau \\
+&=& \int_{-\infty}^{+\infty} h(t+\tau)( \alpha x_{1}(t) + \beta x_{2}(t) )d\tau \\
+&=& \alpha \int_{-\infty}^{+\infty} h(t+\tau)x_{1}(\tau)d\tau  + \beta \int_{-\infty}^{+\infty} h(t+\tau)x_{2}(\tau)d\tau \\
+&=& \alpha \phi_{hx_{1}}(t) + \beta \phi_{hx_{2}}(t)
+\end{eqnarray*}
+Then we have that the system is linear.
+
+Next we check the property of time invariance.
+
+Let \(x_{4}(t) = x_{1}(t+T_{0})\) So
+\begin{eqnarray*}
+\phi_{hx_{4}}(t) &=& \int_{-\infty}^{+\infty} h(t+\tau)x_{4}(\tau)d\tau \\
+&=& \int_{-\infty}^{+\infty} h(t+\tau)x_{1}(\tau + T_{0})d\tau \\
+&=& \int_{-\infty}^{+\infty} h(t+s-T_{0})x_{1}(s)ds \\
+&=& \phi_{hx_{1}}(t-T_{0})
+\end{eqnarray*}
+We have \(\phi_{hx_{4}}(t)\neq \phi_{hx_{1}}(t+T_{0})\). So the system is not
+time invariant.
+
+The system is not causal, because the output depends on all time of the input.
+
+\(\phi_{xh}(t)\) can be expressed as
+\begin{equation*}
+\phi_{xh}(t) = \int_{-\infty}^{+\infty} x(t+ \tau) h(\tau)d\tau
+\end{equation*}
+
+Based on similar analysis as in part (a), we can conclude that the system is
+linear.
+
+Next, we check the property of time invariance.
+Let \(x_{1}(t)\) be arbitrary input signal and \(x_{4}(t) = x_{1}(t+T_{0})\)
+then we have
+\begin{eqnarray*}
+\phi_{x_{4}h}(t) &=& \int_{-\infty}^{+\infty} x_{4}(t+\tau) h(\tau) d\tau \\
+&=& \int_{-\infty}^{+\infty} x_{1}(t+T_{0}+\tau) h(\tau) d\tau \\
+&=& \phi_{x_{1}h}(t+T_{0}) = \phi_{x_{1}h}(t+T_{0})
+\end{eqnarray*}
+Which means that the system is time invariant.
+
+The system is not causal because the output depends on all the value of \(x(t)\).
+\section{Problem 1.46}
+\label{sec:orgd263cd1}
+
+\begin{prob}[]{prob:1-46}
+Consider the feedback system of Figure shown as below. Assume that \(y[n] =
+    0, n<0\)
+
+\begin{enumerate}
+\item Sketch the output when \(x[n] = \delta[n]\)
+\item Sketch the output when \(x[n] = u[n]\)
+\end{enumerate}
+
+\begin{center}
+\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-46.pdf}
+\end{center}
+\label{prob:1-46}
+\end{prob}
+
+From the figure given, we have:
+\begin{eqnarray*}
+e[n]&=& x[n] - y[n] \\
+y[n] &=& e[n-1]
+\end{eqnarray*}
+So we have \(y[n] = x[n-1] - y[n-1]\)
+
+\textbf{Problem 1.46a}
+
+\(x[n] = \sigma[n]\) So  we have \(x[0] = 1\) and \(x[n] = 0, n\neq 0\)
+\begin{eqnarray*}
+y[0]&=& x[-1] - y[-1] = 0 \\
+y[1]&=& x[0] - y[0] = 1 \\
+y[2]&=& x[1] - y[1] = -1 \\
+y[3]&=& x[2] - y[2] = 1 \\
+\end{eqnarray*}
+So the output can be sketched as:
+
+\begin{center}
+\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-46a.pdf}
+\end{center}
+
+\textbf{Problem 1.46b}
+
+\(x[n] = u[n]\) So  we have \(x[n] = 1, n\geq 0\)
+\begin{eqnarray*}
+y[0]&=& x[-1] - y[-1] = 0 \\
+y[1]&=& x[0] - y[0] = 1 \\
+y[2]&=& x[1] - y[1] = 0 \\
+y[3]&=& x[2] - y[2] = 1 \\
+\end{eqnarray*}
+So the output can be sketched as:
+
+\begin{center}
+\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-46b.pdf}
+\end{center}
+\section{Problem 1.47}
+\label{sec:org09ffb49}
+
+\begin{prob}[]{prob:1-47}
+\begin{enumerate}
+\item Let \(\mathcal{S}\) denote an incrementally linear system, and let
+\(x_{1}[n]\) be an arbitrary input signal to \(\mathcal{S}\) with
+corresponding output \(y_{1}[n]\).  Consider the system illustrated in
+Figure \hyperref[figProb1-47a]{1-47(a)}.  Show that this system is linear and that, in fact, the overall
+input-output relationship between \(x[n]\) and \(y[n]\) does not depend
+on the particular choice of \(x_{1}[n]\).
+\item Use the result of part (a) to show that \(\mathcal{S}\) can be
+represented in the form shown in Figure  \hyperref[figProb1-47d]{1-48} .
+\item Which of the following systems are incrementally linear? Justify your
+answers, and if a system is incrementally linear, identify the linear
+system \(L\) and the zero-input response \(y_{0}[n]\) or \(y_{0}(t)\) for
+the representation of the system as shown in Figure 1.48
+\begin{enumerate}
+\item \(y[n] = n + x[n] + 2x[n+4]\)
+\item The system is shown as below
+\begin{equation*}
+y[n] =
+\begin{cases}
+n/2, & n\ \mathrm{even}\\
+(n-1)/2 + \sum_{k=-\infty}^{(n-1)/2} x[k],& n\ \mathrm{odd}
+\end{cases}
+\end{equation*}
+
+\item The system is shown as below
+\begin{equation*}
+y[n] =
+\begin{cases}
+x[n] - x[n-1]  + 3, & \mathrm{if}\ x[0] \geq 0 \\
+x[n] - x[n-1]  - 3, & \mathrm{if}\ x[0] < 0
+\end{cases}
+\end{equation*}
+\item The system depicted in Figure \hyperref[figProb1-47b]{1-47(b)}
+\item The system depicted in Figure  \hyperref[figProb1-47c]{1-47(c)}
+\end{enumerate}
+\item Suppose that a particular incrementaly linear system has a representation
+as in figure  \hyperref[figProb1-47d]{1-48}, with \(\mathcal{L}\) denoting the linear system and
+\(y_{0}[n]\) the zero input reponse, Show that \(S\) is time invariant if
+and only if \(\mathcal{L}\) is a time-invariant system and \(y_{0}[n]\) is constant.
+\end{enumerate}
+
+\begin{center}
+\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-47a.pdf}
+\label{figProb1-47a}
+\end{center}
+
+\begin{center}
+\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-47b.pdf}
+\label{figProb1-47b}
+\end{center}
+
+\begin{center}
+\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1.47c.pdf}
+\label{figProb1-47c}
+\end{center}
+
+\begin{center}
+\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-47d.pdf}
+\label{figProb1-47d}
+\end{center}
+\label{prob:1-47}
+\end{prob}
+
+\textbf{Problem 1.47a}
+
+An incrementally linear system can be expressed as Figure \hyperref[figProb1-47d]{1-47d} : a linear
+system followed by another signal equal to the zero-input response of the
+system. Because \(\mathcal{S}\) is an incrementally linear system, the output
+\(y[n] = y^{'}[n] - y_{1}[n]\) where \(y^{'}[n]\) is the output of
+\(\mathcal{S}\). The \(y^{'}[n]\) contains the response of \(x[n]\) and
+\(x_{1}[n]\) i.e. \(y^{'}[n]\) at lease contains \(y_{1}[n]\). So \(y[n] =
+y^{'}[n] - y_{1}[n]\) will not containt the zero-input response of system
+\(\mathcal{S}\). and the overall system from \(x[n]\) to \(y[n]\) only have the
+result of the linear part of system \(\mathcal{S}\) hence the system is linear.
+
+Furthermore, no matter what \(x_{1}[n]\) we choose, its effect will be cancelled
+by substracting \(y_{1}[n]\). hence, the overall input-output relationship
+between \(x[n]\) and \(y[n]\) does not depend on the particular choice of \(x_{1}[n]\).
+
+\textbf{Problem 1.47b}
+
+\(\mathcal{S}\) is an incrementally linear system. By substracting its
+zero-input response \(y_{0}[n]\) we have a linear system.
+
+\begin{center}
+\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-47b1.pdf}
+\end{center}
+
+The system from \(x[n]\) to \(y^{'}[n]\) is the linear part, and the overall
+input-output is the system \(\mathcal{S}\) represented as incrementally linear system.
+
+\textbf{Problem 1.47c-1}
+
+The system is incrementally linear with the linear part:
+\begin{equation*}
+x[n] \xrightarrow{\mathcal{L}} x[n] + 2x[n+4]
+\end{equation*}
+and the zero-input response
+\begin{equation*}
+y_{0}[n] = n
+\end{equation*}
+
+\textbf{Problem 1.47c-2}
+
+The system is incrementally linear with the linear part:
+\begin{equation*}
+x[n] \xrightarrow{\mathcal{L}}
+\begin{cases}
+0, & n\ \mathrm{even} \\
+\sum_{k=-\infty}^{(n-1)/2}x[k], & n\ \mathrm{odd}
+\end{cases}
+\end{equation*}
+and the zero-input response
+\begin{equation*}
+y_{0}[n] =
+\begin{cases}
+n/2 , & n\ \mathrm{even} \\
+(n-1)/2, & n\ \mathrm{odd}
+\end{cases}
+\end{equation*}
+
+\textbf{Problem 1.47c-3}
+
+Not incrementally linear system. because for \(x[0] \geq 0\) there is one
+zero-input response \(+3\), for \(x[0] < 0\), there is one zero-input response
+\(-3\). So the overall system cannot choose one zero-input response.
+
+\textbf{Problem 1.47c-4}
+
+The overall system can be expressed as
+
+\begin{equation*}
+y(t) = x(t) + t\frac{dx(t)}{t}
+\end{equation*}
+
+The system is linear itself and of course is incrementally linear with zero-input
+reponse zero.
+
+\textbf{Problem 1.47c-5}
+
+The overall system can be expressed as:
+\begin{eqnarray*}
+y[n]&=& (x[n] + \cos(\pi n))^{2} - (x^{2}[n]) \\
+&=& 2x[n]\cos(\pi n) + \cos^{2}(\pi n)
+\end{eqnarray*}
+
+Therefore, the system is incrementally linear with the linear part:
+\begin{equation*}
+x[n] \xrightarrow{\mathcal{L}} 2x[n]\cos(\pi n)
+\end{equation*}
+
+and the zero-input response
+\begin{equation*}
+y_{0}[n] = \cos^{2}(\pi n)
+\end{equation*}
+
+\textbf{Problem 1.47d}
+
+First, let's proof that if \(\mathcal{S}\) is time invariant we can conclude
+that \(\mathcal{L}\) is a time-invariant system and \(y_{0}[n]\) is constant
+
+For the linear part we have:
+\begin{equation*}
+x[n] \xrightarrow{\mathcal{L}} L[n]
+\end{equation*}
+And the zero-input part.
+\begin{equation*}
+y[n] = L[n] + y_{0}[n]
+\end{equation*}
+
+Suppose \(\mathcal{S}\) is time invariant, let \(x_{1}[n]\) and arbitrary input signal.
+
+\begin{equation*}
+y_{1}[n] = x_{1}[n] + y_{0}[n]
+\end{equation*}
+
+and let \(x_{2}[n]\) be \(x_{1}[n-n_{0}]\), where \(n_{0}\) is an arbitrary integer So
+\begin{equation*}
+y_{2}[n] = x_{2}[n] + y_{0}[n] = x_{1}[n-n_{0}] + y_{0}[n]
+\end{equation*}
+
+we also have \(y_{1}[n-n_{0}] = x_{1}[n-n_{0}] + y_{0}[n-n_{0}]\) and \(y_{2}[n]
+= y_{1}[n-n_{0}]\), so we have \(y_{0}[n] = y_{0}[n-n_{0}]\). Since \(n_{0}\) is
+an arbitrary integer, so \(y_{0}[n]\) must be an constant.
+
+Also \(y_{2}[n] = y_{1}[n-n_{0}]\) also implies that \(L_{1}(n-n_{0}) =
+L_{2}[n]\) which means that the linear part is time invariant.
+
+Next, let's proof that if \(\mathcal{L}\) is a time-invariant system and
+\(y_{0}[n]\) is constant then \(\mathcal{S}\) is time invariant. This is easy to
+reach when we write \(\mathcal{S}\) as linear part plus and the zero-input
+consponse:
+
+For the linear part we have:
+\begin{equation*}
+x[n] \xrightarrow{\mathcal{L}} L[n]
+\end{equation*}
+And the zero-input part.
+\begin{equation*}
+y[n] = L[n] + y_{0}[n]
+\end{equation*}
+
+\(\mathcal{L}\) is time-invariant means that \(L[n]\) will experience the same
+time shifting as \(x[n]\) will be. \(y_{0}[n]\) is constant means that
+\(y_{0}[n]\) will not change as time shifts. So \(\mathcal{S}\) is time-invariant.
 \end{document}

### 2020-02-18 mstemc/mstemc.tex
trivial modification

@@
 \definecolor{mycolor}{RGB}{139,0,0}
+\usetheme{CambridgeUS}
 \author{Eason}
 \date{\today}
-\title{Problem 1.21}
+\title{A title}
+\definecolor{links}{HTML}{8c1515}
+\hypersetup{colorlinks=,linkcolor=,urlcolor=links}
+\setbeamertemplate{itemize items}[default]
+\setbeamertemplate{enumerate items}[default]
+\setbeamertemplate{items}[default]
+\setbeamercolor*{local structure}{fg=darkred}
+\setbeamercolor{section in toc}{fg=darkred}
+\setlength{\parskip}{\smallskipamount}
+\institute[INST]{Institute\\\url{http://www.institute.edu}}
+\titlegraphic{\includegraphics[height=1.5cm]{~/Dropbox/mstemc_hugo/static/img/icon-32.png}}
 \hypersetup{
  pdfauthor={Eason},
- pdftitle={Problem 1.21},
+ pdftitle={A title},
  pdfkeywords={},
@@
 
-\begin{prob}[]{prob:1-21}
-A continuout-time signal \(x(t)\) is shown below. Sketch and label carefully
-each of the following signals:
-\begin{equation*}
-\begin{array}{ll}
-\mathbf{(a)}: x(t-1) & \mathbf{(b)}: x(2-t) \\
-\mathbf{(c)}: x(2t + 1) & \mathbf{(d)}: x(4-\frac{t}{2}) \\
-\mathbf{(e)}: [x(t) + x(-t)] u(t) & \mathbf{(f)}: x(t)\delta(t +\frac{3}{2}) - \delta(t-\frac{3}{2})
-\end{array}
-\end{equation*}
-\begin{center}
-\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-21-0.pdf}
-\end{center}
-\label{prob:1-21}
-\end{prob}
+\framesubtitle{A subtitle}
 
-Before we figure all the sub-problem out. Let's review how \(a\) and \(b\)
-affect \(x(at+b)\) . we know that:
-
-\begin{enumerate}
-\item when \(|a| < 1\), \(x(t)\) will be linearly stretched;
-\item when \(|a|>1\), \(x(t)\) will be linearly compressed;
-\item when \(a < 0\), \(x(t)\) will be reversed;
-\item when \(b\neq 0\) , \(x(t)\) will be shifted in time.
-\item when \(a>0, b>0\), \(x(t)\) will be shifted left.
-\item when \(a>0,b<0\), \(x(t)\) will be shifted right.
-\item when \(a<0,b>0\), \(x(t)\) will be reversed first then shifted right.
-\item when \(a<0,b<0\), \(x(t)\) will be reversed first, then shifted left.
-\end{enumerate}
-
-\textbf{Problem 1.21a}
-
-Based on the conclusion given above, we know that \(x(t-1)\) can be obtained by right
-shifting \(x(t)\) with step \(1\). So the result can be visualized as follows.
-
-\begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-21a.pdf}
-\end{center}
-
-\textbf{Problem 1.21b}
-
-For \(x(2-t)\), we re-write it as \(x(-(t-2))\) which can be obtained by first
-reversing \(x(t)\) then right shifting it with step \(2\). The result can be
-shown as follows
-
-\begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProblem1-21b.pdf}
-\end{center}
-
-\textbf{Problem 1.21c}
-
-\(x(2t + 1)\) can be re-written as \(x(2(t+\frac{1}{2}))\) which means that
-\(x(2t+1)\) can be obtained by first linearly compressing \(x(t)\) with factor 2
-then left shifting compressed signal by \(\frac{1}{2}\).
-
-\begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-21c.pdf}
-\end{center}
-
-\textbf{Problem 1.21d}
-
-\(x(4-\frac{t}{2})\) can be re-written as \(x( -\frac{1}{2}( t - 8 ) )\) which
-means that \(x(4-\frac{t}{2})\)  can be obtained by first linearly stretching
-\(x(t)\) by factor \(2\) then right shifting it with step \(8\).
-
-\begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-21d.pdf}
-\end{center}
-
-\textbf{Problem 1.21e}
-
-At first glance, \(\big[x(t) + x(-t)\big] u(t)\) is \(0\) if \(t<0\) .
-
-If \(t > 0\), we have to figure out \(x( -t )\). After obtaining \(x(-t)\), we
-add the right part of \(x(t)\) and left part of \(x(-t)\) then we have \([x(t) +
-x(-t)]u(t)\)
-
-\begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProblem1-21e.pdf}
-\end{center}
-
-\(x(t)\delta(t +\frac{3}{2}) - \delta(t-\frac{3}{2})\) only have two points with
-non-negative values: \(t=\frac{3}{2}\) and \(t=-\frac{3}{2}\).
-
-\begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-21f.pdf}
-\end{center}
+\begin{itemize}
+\item Bullet 1
+\item Bullet 2
+\item Bullet 3
+\end{itemize}
 \end{document}

### 2020-09-05 mstemc/post/technology/SignalsAndSystems/Chapter1BasicProblems3.tex
trivial commit

--- 2020-02-18 mstemc/index.tex
@@
 \date{\today}
-\title{Signals and Systems Chapter 1 Problems Part 3 (1.32-1.47)}
+\title{}
 \hypersetup{
  pdfauthor={Eason},
- pdftitle={Signals and Systems Chapter 1 Problems Part 3 (1.32-1.47)},
+ pdftitle={},
  pdfkeywords={},
- pdfsubject={This post consists of solutions to problems from 1.21 to 1.31 in chapter 1 of the book Signals and Systems by Oppenheim ,Willsky and Nawab.\cite{oppenheim_signals_1997}},
+ pdfsubject={},
  pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
@@
 
- \thispagestyle{empty}
- \begingroup
-\begin{center}
- \vspace{\baselineskip}
- \textbf{\Huge Signals and Systems Chapter 1 Problems Part 3 (1.32-1.47)} \par
- \vspace{2\baselineskip}  \newline
- \textbf{\large Eason Zhang with www.makesteamclear.com \par}
- \vspace{\baselineskip} \newline
-  \today \par
- \vspace{\baselineskip}
-  \vfill
- \setlength{\unitlength}{3pt}
- \includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-21-0.pdf}
- \vfill \vspace{\baselineskip}
- \href{WWW.MAKESTEAMCLEAR.COM}{\Large WWW.MAKESTEAMCLEAR.COM} \par\newline
-  makesteamclear is a free project, run by Eason Zhang, to make videos about STEAM in a more approachable way.
-If you find the contents in this article or the site or the youtube channel helpful, please consider \href{www.makesteamclear.com}{\ensuremath \heartsuit support me\ensuremath\heartsuit }, thanks \par
- \end{center}
- \endgroup
-
- \newpage \thispagestyle{empty} \textbf{copyright page} \newpage \tableofcontents \newpage
-\hspace{0pt}\\
-
-This post consists of solutions to problems from 1.21 to 1.31 in chapter 1 of the book Signals and Systems by Oppenheim ,Willsky and Nawab.\cite{oppenheim_signals_1997}
-
- \thispagestyle{empty}
- \begingroup
-\begin{center}
- \vspace{\baselineskip}
- \textbf{\Huge Signals and Systems Chapter 1 Problems Part 3 (1.32-1.47)} \par
- \vspace{2\baselineskip}  \newline
- \textbf{\large Eason Zhang with www.makesteamclear.com \par}
- \vspace{\baselineskip} \newline
-  \today \par
- \vspace{\baselineskip}
-  \vfill
- \setlength{\unitlength}{3pt}
- \includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-47d.pdf}
- \vfill \vspace{\baselineskip}
- \href{WWW.MAKESTEAMCLEAR.COM}{\Large WWW.MAKESTEAMCLEAR.COM} \par\newline
-  makesteamclear is a free project, run by Eason Zhang, to make videos about STEAM in a more approachable way.
-If you find the contents in this article or the site or the youtube channel helpful, please consider \href{www.makesteamclear.com}{\ensuremath \heartsuit support me\ensuremath\heartsuit }, thanks \par
- \end{center}
- \endgroup
-
- \newpage \thispagestyle{empty} \textbf{copyright page} \newpage \tableofcontents \newpage
-\hspace{0pt}\\
-
-This post consists of solutions to problems from 1.21 to 1.31 in chapter 1 of the book Signals and Systems by Oppenheim ,Willsky and Nawab.\cite{oppenheim_signals_1997}
-
 \section{Problem 1.32}
-\label{sec:orgfc1022f}
+\label{sec:orgf15481f}
 
@@
 \section{Problem 1.33}
-\label{sec:orgc6b726e}
+\label{sec:orgf7b6502}
 
@@
 \section{Problem 1.34}
-\label{sec:org4fc36d2}
+\label{sec:orgb3a8c01}
 
@@
 \section{Problem 1.35}
-\label{sec:orgd2ae89c}
+\label{sec:org1baca05}
 
@@
 \section{Problem 1.36}
-\label{sec:org4a7f30f}
+\label{sec:org2d12240}
 
@@
 Where \(m\) is the minimum integer so that \(N\) is an integer. Based on the
-conclusion of \hyperref[sec:orgd2ae89c]{Problem 1.35} , we can re-express \(N\) as
+conclusion of \hyperref[sec:org1baca05]{Problem 1.35} , we can re-express \(N\) as
 \begin{equation*}
@@
 \section{Problem 1.37}
-\label{sec:org5b0c999}
+\label{sec:org62dbfe6}
 
@@
 \section{Problem 1.38}
-\label{sec:orgef628d7}
+\label{sec:org977ea11}
 
@@
 \section{Problem 1.39}
-\label{sec:org95fdb02}
+\label{sec:orgfa85644}
 
@@
 \section{Problem 1.40}
-\label{sec:org71282a6}
+\label{sec:orge406af3}
 
@@
 \section{Problem 1.41}
-\label{sec:orgb5785da}
+\label{sec:org13d0b92}
 
@@
 \section{Problem 1.42}
-\label{sec:org8f471d7}
+\label{sec:orgb6902d3}
 
@@
 \section{Problem 1.43}
-\label{sec:org772be8f}
+\label{sec:org51636a9}
 
@@
 \section{Problem 1.44}
-\label{sec:orgefef85f}
+\label{sec:org159eee9}
 
@@
 \section{Problem 1.45}
-\label{sec:orgb8bc776}
+\label{sec:org4477d7c}
 
@@
 \section{Problem 1.46}
-\label{sec:orgd263cd1}
+\label{sec:org34ba874}
 
@@
 \section{Problem 1.47}
-\label{sec:org09ffb49}
+\label{sec:orgc922959}
 

### 2020-11-10 msteamc/index.tex
change mstemc to msteamc

% Intended LaTeX compiler: lualatex
\documentclass[koma,a4paper,utopia,12pt,listings-color,microtype,paralist,colorlinks,urlcolor=red]{org-article}
\usepackage{tikz}
\usetikzlibrary{arrows,decorations.pathmorphing,,backgrounds,positioning,fit,petri,calc,intersections,through,shapes.misc,mindmap,calendar,shadows,mindmap,calendar,graphdrawing,trees,shapes.misc,quotes,angles}
\definecolor{mycolor}{RGB}{139,0,0}
\author{Eason}
\date{\today}
\title{Signals and Systems Chapter 1 Problems Part 1 (1.1-1.20)}
\hypersetup{
 pdfauthor={Eason},
 pdftitle={Signals and Systems Chapter 1 Problems Part 1 (1.1-1.20)},
 pdfkeywords={},
 pdfsubject={This post consists of solutions to problems from 1.1 to 1.21 in chapter 1 of the book Signals and Systems by Oppenheim ,Willsky and Nawab.},
 pdfcreator={Emacs 26.3 (Org mode 9.3.7)},
 pdflang={English}}
\begin{document}

 \thispagestyle{empty}
 \begingroup
\begin{center}
 \vspace{\baselineskip}
 \textbf{\Huge Signal and System Chapter 1 Problems} \par
 \vspace{2\baselineskip}  \newline
 \textbf{\large Eason Zhang with www.makesteamclear.com \par}
 \vspace{\baselineskip} \newline
  \today \par
 \vspace{\baselineskip}
  \vfill
 \setlength{\unitlength}{3pt}
 \includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/eulerEquation.pdf}
 \vfill \vspace{\baselineskip}
 \href{WWW.MAKESTEAMCLEAR.COM}{\Large WWW.MAKESTEAMCLEAR.COM} \par\newline
  makesteamclear is a free project, run by Eason Zhang, to make videos about STEAM in a more approachable way. If you find the contents in this article or the site or the youtube channel helpful, please consider \href{www.makesteamclear.com}{\ensuremath \heartsuit support me\ensuremath\heartsuit }, thanks \par
 \end{center}
 \endgroup

 \newpage \thispagestyle{empty} \textbf{copyright page} \newpage \tableofcontents \newpage
\hspace{0pt}\\

This post consists of solutions to problems from 1.1 to 1.21 in chapter 1 of the book Signals and Systems by Oppenheim ,Willsky and Nawab.

\section{Problem 1.1}
\label{sec:org3c85e3e}

\begin{prob}[]{prob:1.3}
Problem 1.1: Express each of the following complex numbers in \emph{Cartesian} form \(x+iy\):
\begin{equation*}
\begin{array}{ccc}
 \frac{1}{2}e^{i\pi}  & \frac{1}{2}e^{-i\pi}  & e^{i\pi/2}  \\
 e^{-i\pi/2}         & e^{i5\pi/2}  & \sqrt{2}e^{i\pi/4}  \\
 \sqrt{2}e^{i9\pi/4} & \sqrt{2}e^{-i9\pi/4}  & \sqrt{2} e^{-i\pi/4}
\end{array}
\end{equation*}
\label{prob11}
\end{prob}

First, let's figure them out using the Euler's formula. For the nine complex
numbers in  \hyperref[prob11]{Problem 1.1}, we have:

\begin{eqnarray*}
\tfrac{1}{2} e^{i\pi } &=&  \tfrac{1}{2} (\cos(\pi) + i\sin(\pi) ) = \tfrac{1}{2} \cos(\pi) = -\tfrac{1}{2} \\
\tfrac{1}{2} e^{-i\pi} &=& \tfrac{1}{2}  (\cos(-\pi) + i\sin(-\pi) ) = \tfrac{1}{2} \cos(-\pi) = -\tfrac{1}{2} \\
e^{i\pi/2} &=& \cos(\pi/2) + i \sin(\pi/2) = i \\
e^{-i\pi/2} &=& \cos(-\pi/2) + i \sin(-\pi/2) = -i \\
e^{i5\pi/2} &=& \cos(5\pi/2) + i \sin(5\pi/2) = \cos(2\pi + \pi/2) + i \sin(2\pi + \pi/2) = i \sin(\pi/2) = i \\
\sqrt{2}e^{i\pi/4} &=& \sqrt{2} ( \cos(\pi/4) + i \sin(\pi/4) ) = \sqrt{2} ( \tfrac{\sqrt{2}}{2} + i\tfrac{\sqrt{2}}{2}  ) = 1 + i \\
 \sqrt{2} e^{i9 \pi/4} &=& \sqrt{2} ( \cos(9\pi/4) + i \sin(9\pi/4) ) = 1 + i \\
 \sqrt{2} e^{-i9 \pi/4} &=& \sqrt{2} ( \cos(-9\pi/4) + i \sin(-9\pi/4) ) = 1 - i \\
 \sqrt{2} e^{-i \pi/4} &=& \sqrt{2} ( \cos(-\pi/4) + i \sin(-\pi/4) ) = 1 - i
\end{eqnarray*}

\section{Problem 1.2}
\label{sec:orgbdb3cb8}

\begin{prob}[]{prob:1.3}
Problem 1.2: Express each of the following complex numbers in \emph{polar} form (\(re^{i\theta},
 -\pi < \theta \leq \pi\)):
\begin{equation*}
\begin{array}{c{3cm}c{3cm}c{3cm}}
5 & -2 & -3i \\
\frac{1}{2} - i \frac{\sqrt{3}}{2} & 1+i & (1-i)^{2} \\
i(1-i)  & \frac{1+i}{1-i}  & \frac{\sqrt{2} + i \sqrt{2}}{1+i\sqrt{3}}
\end{array}
\end{equation*}
\label{prob12}
\end{prob}

For the nine complex numbers in  \hyperref[prob12]{Problem 1.2} , we have:

\begin{eqnarray*}
 5 &=& 5 e^{i0} = 5 e^{i(2\pi n)}, n\in \{\ldots, -2,-1,0,1,2,\ldots \} \\
 -2 &=& 2 e^{i\pi} = -2 e^{i0} \\
 -3i &=& 3 e^{-i\pi} \\
 \tfrac{1}{2} - i \tfrac{\sqrt{3}}{2}  &=& e^{-i\pi/3} \\
 1+i &=& \sqrt{2} e^{i\pi/4} \\
 (1-i)^{2} &=& ( \sqrt{2} e^{-i\pi/4} )^{2} = 2 e^{-i\pi/2} \\
 i(1-i) &=& 1 - i = \sqrt{2} e^{-i\pi/4} \\
 \tfrac{1+i}{1-i} &=& \tfrac{ \sqrt{2}e^{i\pi/4} } { \sqrt{2}e^{-i\pi/4} } = e^{i\pi/2} \\
 \tfrac{\sqrt{2} + i \sqrt{2}}{1+i\sqrt{3}} &=& \tfrac{ 2e^{i\pi/4} }{ 2 e^{i\pi/3} } = e^{-i\pi/12}
\end{eqnarray*}

Every complex number \(a+ib\) can be visualized in the complex plane
\(\mathbb{C}\). It can be viewed either as the point with the coordinate
\((a,b)\) or as a vector starting from \(( 0,0 )\) to the point \((a,b)\).

Also every complex number \(a+ib\) can be represented in the exponential form
conveniently by using the Euler's formula \(e^{i\alpha} = \cos\alpha +
 i\sin\alpha\). One complex number have unique Cartesian form but many
expoential forms. Taking \(1+i\) for example, its expoential form can be
\(\sqrt{2}e^{i(\pi/4 + 2n\pi)}, n\in \{ \ldots, -2,-1,0,1,2,\ldots \}\). When
we express a complex number in expoential form, it helps to keep a concept of
rotation in mind. In the complex plane \(\mathbb{C}\), a complex number will
return to itself if it rotates a multiple of \(2\pi\) around the origin point
with radius equal to its modulus. please keep the concept of roatation in mind
and it will become increasingly important during our later study.

In the development of complex analysis, \(a+ib\) has another form \(r\angle
 \theta\), where \(r\) is the modulus and \(\theta\) the argument (or the
angle). Obviously, this notation is not as good as the expoential form,
espacialy when we want to do complex analysis such as differentiation and
integration. We just mention it here for the sake of completion. The expoential
form will be deployed from now on.

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/eulerEquation.pdf}
\end{center}

Now, let's go back to \hyperref[prob11]{Problem 1.1} and Problem \hyperref[prob12]{Problem
1.2}. It's easy to figure the answers out using the Euler's formula. Let's do
more to show them on the complex plane keeping the concept of rotation in mind.

\begin{figure}[htbp]
\centering
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/problem1_1.pdf}
\caption{\label{problem1-1}visualized the complex numbers from Problem \hyperref[prob11]{Problem 1.1} in the complex plan}
\end{figure}

From Figure \ref{problem1-1} , taking \(\color{green}{\tfrac{1}{2}e^{i\pi}}\) and
\(\color{red}{\tfrac{1}{2}e^{-i\pi}}\) for example, in the complex plane, they
are the same point \(-\tfrac{1}{2}\) which means \(-\tfrac{1}{2}\) can be
reached by rotating \(\tfrac{1}{2}\) with angle \(\pi\) anti-clockwise or with angle
\(-\pi\) clockwise. Essentially, this is because that \(e^{i\theta} =
 e^{i(\theta + 2n\pi)}, n\in \{\ldots,-2,-1,0,1,2,\ldots\}\). It's
straightforward that \(e^{i\pi} = e^{i(\pi + 2(-1)\pi)} = e^{-i\pi}\).

In the end of \hyperref[prob11]{Problem 1.1} and \hyperref[prob12]{Problem 1.2}, I want to say
more about expressing \(\tfrac{1+i}{1-i}\) in its polar form. There are two
methods to get the polar form:
\begin{enumerate}
\item multiply the fraction's numerator and denominator by \(( 1 + i )\)

So we have:
\begin{eqnarray*}
\frac{1+i}{1-i}& = & \frac{(1+i)(1+i)}{(1-i)(1+i)} \\
&=& \frac{2i}{2} = i
\end{eqnarray*}

\item express the numerator and denominator in expoential form first, then do the
following calculation.

\begin{eqnarray*}
\frac{1+i}{1-i} &=& \frac{\sqrt{2}e^{i\pi/4}}{\sqrt{2}e^{-i\pi/4}}  \\
&=& e^{i2\pi/4} = e^{i\pi/2} = i
\end{eqnarray*}
\end{enumerate}
\section{Problem 1.3}
\label{sec:org975ac37}

\begin{prob}[]{prob:1.3}
Problem 1.3: Determine the values of \(P_{\infty}\) and \(E_{\infty}\) for each
of the following signals:
\begin{equation*}
\begin{array}{ll}
\mathrm{(a)} \quad x_{1}(t) = e^{-2t}u(t) & \mathrm{(b)} \quad x_{2}(t) = e^{i(2t + \pi/4)} \\
 \mathrm{(c)} \quad x_{3}(t) = \cos(t) & \mathrm{(d)} \quad x_{1}[n] = (\tfrac{1}{2})^{n} u[n] \\
 \mathrm{( e )} \quad x_{2}[n] = e^{i(\pi/2n + \pi/8)} & \mathrm{(f)} \quad x_{3}[n] = \cos(\tfrac{\pi}{4}n)
\end{array}
\end{equation*}
\label{prob13}
\end{prob}

Before solving this problem, let's review the definition of \(P_{\infty}\) and
\(E_{\infty}\). For a continuous time signal \(x(t)\), we have
\begin{eqnarray}
\label{eq:2}
E_{\infty}&=& \lim_{T\to \infty} \int_{-T}^{T} |x(t)|^{2}\mathrm{d}t \\
P_{\infty}&=& \lim_{T\to \infty} \frac{1}{2T}\int_{-T}^{T} |x(t)|^{2}\mathrm{d}t = \lim_{T\to\infty} \frac{E_{\infty}}{2T}
\end{eqnarray}
For a discrete time signal \(x[n]\), we have:
\begin{eqnarray}
\label{eq:3}
E_{\infty}&=& \lim_{N\to \infty} \sum_{n=-N}^{+N} |x[n]|^{2} \\
P_{\infty}&=& \lim_{N\to \infty} \frac{1}{2N+1} \sum_{n=-N}^{+N} |x[n]|^{2} = \lim_{N\to\infty} \frac{E_{\infty}}{2N+1}
\end{eqnarray}

Equation (\ref{eq:2})(\ref{eq:3}) are not only mathmatical definitions but also
related to physical quantities such as power and energy in a physical system.
For an electric circuit, taking the voltage \(v(t)\) and current \(i(t)\) across
a resistor for example, the power at time \(t\) can be calculated by:
\begin{equation}
\label{eq:4}
p(t) = v(t)i(t) = \frac{v^{2}(t)}{R}
\end{equation}
Let's go back to equation (\ref{eq:2}) and equation(\ref{eq:3}), if
\(E_{\infty}< \infty\) we say that the signal has finite energy otherwise
infinite energy. If \(P_{\infty} <\infty\) we say that the signal has finite
power otherwise infinite power.

Next let's determine the values of \(P_{\infty}\) and \(E_{\infty}\) for the
given signals.
\subsection{Problem1.3a \(\mathbf{(a)}: x_{1}(t)= e^{-2t}u(t)\)}
\label{sec:orge15cb02}

\begin{eqnarray*}
E_{\infty}  & =  & \int_{\infty}^{\infty} |e^{-2t}u(t)|^{2} \mathrm{d}t \\
&=& \int_{0}^{\infty} e^{-4t} \mathrm{d}t \\
&=& \frac{1}{4}
\end{eqnarray*}
So, it's straightforward that:
\begin{equation}
\label{eq:5}
P_{\infty} = \lim_{T\to \infty} \frac{E_{\infty}}{2T}  = 0
\end{equation}

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figprob1-3.pdf}
\end{center}

\subsection{Problem1.3b \(\mathbf{(b)}: x_{2}(t)= e^{i(2t+\pi/4)}\)}
\label{sec:orgf93273c}

We have \(|e^{i(2t+\pi/4)}| = 1\) , therefore
\begin{eqnarray*}
E_{\infty}&=& \int_{\infty}^{\infty} |x_{2}(t)= e^{i(2t+\pi/4)}|^{2} \mathrm{d}t \\
&=& \infty
\end{eqnarray*}

For power \(P_{\infty}\), we have:
\begin{eqnarray*}
P_{\infty}&= &\lim_{T\to\infty} \frac{1}{2T}\int_{-T}^{T} |x_{2}(t)|^{2} \mathrm{d}t  \\
&=& 1
\end{eqnarray*}

This signal has constant power. If you keep the concept of rotation mentioned in
Problem \ref{prob11}, you will notice immediately that all the points generated by
\(x_{2}(t)\) lies on the unit circle.

\subsection{Problem 1.3c \(\mathbf{(c)}:x_{3}(t)=\cos(t)\)}
\label{sec:org2d00fa8}

\begin{eqnarray*}
E_{\infty}&=& \lim_{T\to\infty} \int_{-\infty}^{\infty} |x_{3}(t)|^{2} \mathrm{d}t \\
&=& \int_{\infty}^{\infty} \cos(t)^{2} \mathrm{d}t = \infty
\end{eqnarray*}

\begin{eqnarray*}
P_{\infty}&=& \lim_{T\to\infty} \frac{1}{2T}\int_{-T}^{T} |x_{3}(t)|^{2} \mathrm{d}t  \\
&=& \lim_{T\to\infty}\frac{1}{2T} \int_{-T}^{T} \cos(t)^{2} \mathrm{d}t \\
&=& \lim_{T\to\infty} \frac{1}{2T} \int_{-T}^{T} \frac{1+\cos(2t)}{2} \mathrm{d}t = \frac{1}{2}
\end{eqnarray*}

\(x_{3}(t)\)  can be visualized as follows:

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figprob1-3c.pdf}
\end{center}

\subsection{Problem 1.3d \(\mathbf{(d):} \quad x_{1}[n] = (\tfrac{1}{2})^{n} u[n]\)}
\label{sec:org9332415}

By definition, we have:
\begin{eqnarray*}
E_{\infty}&=&\lim_{N\to\infty}\sum_{n=-N}^{N} \big((\tfrac{1}{2})^{n}u[n]\big)^{2} \\
&=&\lim_{N\to\infty}\sum_{n=0}^{N} (\tfrac{1}{4})^{n} \\
&=& \tfrac{4}{3}
\end{eqnarray*}

Then,
\begin{eqnarray*}
P_{\infty}&=& \lim_{N\to\infty} \frac{1}{2N+1} \sum_{n=-N}^{N} \big((\tfrac{1}{2})^{n}u[n]\big)^{2}   \\
&=& 0
\end{eqnarray*}

\(x_{1}[n]\) can visualized as:
\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figprob1-3d.pdf}
\end{center}

\section{Problem 1.4}
\label{sec:orgcfde750}

\begin{prob}[]{prob:1-4}
 Problem 1.4: Let \(x[n]\) be a signal with \(x[n]=0\) for\(n< -2\) and \(n>4\),
for each signal given below, determine the values of \(n\) for which it is
guaranteed to be zero.
\begin{eqnarray*}
\mathbf{ (a) } & & x[n-3] \\
\mathbf{ (b) } & & x[n+4] \\
\mathbf{ (c) } & & x[-n]  \\
\mathbf{ (d) } & & x[-n+2] \\
\mathbf{ (e) } & & x[-n-2]
\end{eqnarray*}
\label{prob:1-4}
\end{prob}

For the given signals \(\mathbf{(a)}\) to \(\mathbf{(e)}\), the transformations
of the variable \(n\) will change the interval in which the signals are zero.
For the convenience of calculation, we write the origin signal as:
\begin{equation*}
x[m] = 0, m< -2 \quad \mathrm{and} \quad m>4
\end{equation*}

We can visualize \(x(m)\) as below (I just give an example, you can name any
signal that satisfy \(x[m] = 0, m< -2 \ \mathrm{and} \ m>4\)):

\begin{center}
\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-4.pdf}
\end{center}

\subsection{Problem 1.4a \(\mathbf{(a)}:x[n-3]\)}
\label{sec:org897c6ea}

For signal \(\mathbf{(a)}\), to get the interval where \(x[n-3] = 0\), we have:
\begin{eqnarray*}
  m=n-3 &<& -2 \\
  m=n-3 &>& 4
\end{eqnarray*}
 Then, we have \(n < 1 \ \mathrm{and} \ n > 7\) from which we can see that
the new signal is a right shift three relative to the origin signal, i.e. new
signal is delayed with three.

\begin{center}
\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-4a.pdf}
\end{center}

\subsection{Problem 1.4b \(\mathbf{(b)}:x[n+4]\)}
\label{sec:org9176217}

For signal \(\mathbf{(b)}\), we have:
\begin{eqnarray*}
m=n+4&<&-2 \\
m=n+4&>&4
\end{eqnarray*}
Then, we have \(n<-6\ \mathrm{and}\ n>0\) from which we can see that the new
signal is a left shift four relative to the origin signal, i.e. new
signal is advanced with four.

\begin{center}
\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-4b.pdf}
\end{center}

\subsection{Problem 1.4c \(\mathbf{(c)}: x[-n]\)}
\label{sec:org71c1184}

For signal \(\mathbf{( c )}\), we have:
\begin{eqnarray*}
m=-n&<&-2 \\
m=-n&>&4
\end{eqnarray*}

Then, we have \(n>2\ \mathrm{and} \ n<-4\) from which we can see that the new
signal is a reversal of the origin signal.

\begin{center}
\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-4c.pdf}
\end{center}

\subsection{Problem 1.4d \(\mathbf{(d)}: x[-n+2]\)}
\label{sec:org0b89113}

for signal \(\mathbf{(d)}\), we have:
\begin{eqnarray*}
m=-n+2&<&-2 \\
m=-n+2&>&4
\end{eqnarray*}
Then, we have \(n>4\ \mathrm{and}\ n<-2\). For \(x[-n+2]\), we can first
flip the original signal then right shift the flipped signal by 2. Notice the
contents in the brackets \(-(n+2)\). I would like treat it as \(-(n-2)\), by
which I know that the minus symbol means reversal and \(-2\) means right
shift by 2.

\begin{center}
\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-4d.pdf}
\end{center}

\subsection{Problem 1.4e \(\mathbf{(e)}: x[-n-2]\)}
\label{sec:org04ff18a}

For signal \(\mathbf{(e)}\), we have:

\begin{eqnarray*}
m=-n-2&<&-2 \\
m=-n-2&>&4
\end{eqnarray*}

Then, we have \(n>0 \ \mathrm{and}\ n<-6\). To get the new signal, we have
to filp the original signal first then left shift the flipped signal by two.

\begin{center}
\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-4e.pdf}
\end{center}

\section{Problem 1.5}
\label{sec:org8c8f6ba}

\begin{prob}[]{prob:1-5}
Let \(x(t)\) be a signal with \(x(t)=0, \ x<3\). For each signal
given below, determine the values of \(t\) for which it is guaranteed to be
zero.

\begin{equation*}
\begin{array}{ll}
\mathbf{(a)}: x(1-t) \qquad  &   \mathbf{(b)}: x(1-t) + x(2-t)\qquad   \\
\mathbf{(c)}: x(1-t)x(2-t)\qquad &  \mathbf{(d)}: x(3t) \qquad  \\
  \mathbf{(e)}: x(t/3)\qquad & \\
\end{array}
\end{equation*}
\label{prob:1-5}
\end{prob}

For signal \(\mathbf{(a)}: x(1-t)\),  we have:
\begin{equation*}
1-t < 3
\end{equation*}

So, \(t>-2\). Signal \(\mathbf{(a)}: x(1-t)\) can be achieved by flipping the
origin signal first then right shifting one.

For signal \(\mathbf{(b)}: x(1-t) + x(2-t)\) , we have:
\begin{eqnarray*}
1-t&< &3 \\
2-t&<& 3
\end{eqnarray*}
Because it a "\(+\)" between \(x(1-t)\) and \(x(2-t)\) so only when both of the
two signals are zero, the result will be zero. For the first part we have the
value zero when \(t>-2\) the second \(t>-1\), so the result will be the
intersect of these two intervals, i.e. \(t>-1\) . we achieve signal
\(\mathbf{(b)}: x(1-t) + x(2-t)\) by adding signal \(\mathbf{(a)}: x(1-t)\)
with a second signal \(x(2-t)\) which can be achieved by flipping it first then
right shifting two.

For signal \(\mathbf{(c)}: x(1-t)x(2-t)\), \(x(1-t)\) is multiplied by
\(x(2-t)\), so if any one of these two signals is zero, the result is zero.
Based on the result of signal \(\mathbf{( b )}\), we have \(t>-2\).

For signal \(\mathbf{( d )}: x(3t)\), we have:
\begin{equation*}
3t < 3
\end{equation*}
Then, \(t<1\). The signal is compressed by \(3\).

For signal \(\mathbf{( e )}: x(t/3)\), we have:
\begin{equation*}
t/3 < 3
\end{equation*}
Then, \(t<9\). The signal is streched by \(3\).

\section{Problem 1.6}
\label{sec:orgb735a47}

\begin{prob}[]{prob:1-6}
Determine whether or not each of the following signals is periodic:

\begin{eqnarray*}
&&  \mathbf{(a)}: x_{1}(t) = 2e^{i(t+\pi/4)}u(t) \\
&&  \mathbf{( b )}: x_{2}[n] = u[n] + u[-n]  \\
&&  \mathbf{(c)}: x_{3}[n] = \sum_{k=-\infty}^{\infty} \{ \delta[n-4k] - \delta[n-1-4k] \}
\end{eqnarray*}
\label{prob:1-6}
\end{prob}

\begin{itemize}
\item \(x_{1}(t)\) is not periodic because \(u(t) = 0, t<0\)
\item \(x_{2}[n]\) is not periodic because
\begin{equation*}
x_{2}[n] =
\begin{cases}
2 & n=0 \\
1 & n\neq 0
\end{cases}
\end{equation*}
\item For signal \(x_{3}[n]\) we know that with a \(n\), \(\delta[n-4k]\) and
\(\delta[n-1-4k]\) can not be zero at the same time. Because \(k\) and
\(n-4k\) must be integers, \(\delta[n-4k]\) and \(\delta[n-1-4k]\) will repeat
themself every four steps. Furthermore, for every \(n\), the \(k\) runs from
\(-\infty\) to \(\infty\), and only one \(k\) will match the \(n\) to set
\(\delta[n-4k]\) or \(\delta[n-1-4k]\) as zero. We can test it by setting
\(n = 0,1,2,\ldots\)
\begin{eqnarray*}
&& x[0] = 1,\quad x[1] = -1, \quad x[2] = 0, \quad x[3] = 0 \\
&& x[4] = 1,\quad x[5] = -1, \quad x[6] = 0, \quad x[7] = 0 \\
&& x[8] = 1,\quad x[9] = -1, \quad x[10] = 0, \quad x[11] = 0
\end{eqnarray*}

\begin{center}
\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figprob1-6.pdf}
\end{center}
\end{itemize}

\section{Problem 1.7}
\label{sec:org292be4b}

\begin{prob}[]{prob:1-7}
For each signal given below, determine all the values of the independent
variable at which the even part of the signal is guaranteed to be zero.

\begin{equation*}
\small
\begin{array}{ll}
 \mathbf{(a)}: x_{1}[n] = u[n] - u[n-4] \qquad  &   \mathbf{(b)}: x_{2}(t) = \sin(\tfrac{1}{2} t) \qquad   \\
  \mathbf{(c)}: x_{3}[n] = (\frac{1}{2})^{n} u[n-3] \qquad &  \mathbf{(d)}: x_{4}(t) = e^{-5t}u(t+2) \\
\end{array}
\end{equation*}
\label{prob:1-7}
\end{prob}

\subsection{Problem 1.7a \(\mathbf{(a)}: x_{1}[n] = u[n] - u[n-4]\)}
\label{sec:orgcc2fcf2}

Any signal \(x_{1}(t)\) consists of two parts, even part \(\mathrm{Ev}
\{x_{1}(t)\}\) and odd part \(\mathrm{Od} \{ x_{1}(t)\}\). For signal \(\mathbf{(a)}\), when the signal is zero, we have the domain of the independent
value \(n< 0\) and \(n \geq 4\) , so the even part of the signal will be
zero when \(n\leq 4\) and \(n\geq 4\). \(x_{t}(t)\) and its even part and odd
part can be illustrated as:

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figprob1-7.pdf}
\end{center}

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figprob1-7ab.pdf}
\end{center}

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figprob1-7ac.pdf}
\end{center}

\subsection{Problem 1.7b \(\mathbf{(b)}: x_{2}(t) = \sin(\tfrac{1}{2} t)\)}
\label{sec:orge473634}
For signal \(x_{2}(t) = \sin (\frac{1}{2} t)\), because it is an odd signal, so
for all \(t\), the even part of \(x_{2}(t)\) is zero.

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/fig1-7b.pdf}
\end{center}

Notice that for \(\sin(\frac{1}{2}t)\), the signal can be obtained by streching
\(\sin(t)\) with a factor \(2\). In particular, the fundamental period is \(4\pi\).

\subsection{Problem 1.7c \(\mathbf{(c)}: x_{3}[n] = ( \frac{1}{2} )^{n} u[n-3]\)}
\label{sec:orgbe754f7}

For signal \(x_{3}[n] = ( \frac{1}{2} )^{n} u[n-3]\), which will be zeros for
\(n<3\). By definition, the even part of \(x_{3}[n]\) will be zeros for \(|n| <
3\). Actually, we do not visualize the signal to draw such a conclusion. For the
sake of visualization, I illustrate the signal as below:

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-7ca.pdf}
\end{center}

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-7cb.pdf}
\end{center}

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-7cc.pdf}
\end{center}

\subsection{Problem 1.7d \(\mathbf{(d)}: x_{4}(t) = e^{-5t}u(t+2)\)}
\label{sec:orgca169be}

For signal \(\mathbf{(d)}: x_{4}(t) = e^{-5t}u(t+2)\), we have \(x_{4}(t) = 0,\
t<-2\). Because the even and odd part is symmetrical with y-axis, there is no
\(t\) at which the even and odd part of will be zero.

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-7da.pdf}
\end{center}

\section{Problem 1.8}
\label{sec:org9d56250}

\begin{prob}[]{prob:1-8}
Express the real part of each of the following signals in the form
\(Ae^{-at}\cos(\omega t + \phi)\), where \(A,a,\omega, \phi\) are real numbers
with \(A>0\) and \(-\pi < \phi \leq \pi\):
\begin{equation*}
\small
\begin{array}{ll}
  \mathbf{( a )}: x_{1}(t) = -2 &  \mathbf{( b )}: x_{2}(t) = \sqrt{2}e^{i\pi/4}\cos(3t + 2\pi) \\
  \mathbf{( c )}: x_{3}(t) = e^{-t}\sin(3t + \pi) & \mathbf{( d )}: x_{4}(t) = i e^{(-2+i100)t}
\end{array}
\end{equation*}
\label{prob:1-8}
\end{prob}

\begin{enumerate}
\item \(\mathrm{Re}\{x_{1}(t)\} = -2 = 2e^{-0t}\cos(0t + \pi)\) with \(A = 2,
   a=0, \omega = 0, \phi = \pi\)
\item \(\mathrm{Re} \{x_{2}(t)\} = \mathrm{Re} \{ \sqrt{2} ( \cos( \pi/4 ) + i
   \sin (\pi/4) ) \cos(3t) \} = \cos(3t) = e^{-0t}\cos( 3t + 0 )\) with \(A =
   1\), \(a = 0\), \(\omega = 3\),\(\phi = 0\)
\item \(\mathrm{Re} \{ x_{3}(t) \} = \mathrm{Re} \{ e^{-t} \sin ( 3t + \pi )  \}
   = e^{-t}\cos(3t + \pi/2)\) with \(A=1\), \(a=1\), \(\omega=3\), \(\phi=\pi/2\)
\item \(\mathrm{Re} \{x_{4}(t)\}   = \mathrm{Re} \{
   e^{i\pi/2} e^{(-2+i100)t} \} = \mathrm{Re}\{ e^{(-2 + i100)t + i\pi/2} \} =
   e^{-2t}\cos(100t + \pi/2)\) with\(A = 1\), \(a=2\), \(\omega=100\), \(\phi=\pi/2\)
\end{enumerate}

\section{Problem 1.9}
\label{sec:orgea8c035}

\begin{prob}[]{prob:1-9}
Determine whether or not each of the following signals is periodic. If a signal
is periodic, specify its fundamental period.

\begin{equation*}
\begin{array}{ll}
\mathbf{( a )}: x_{1}(t) = ie^{i10t} &  \mathbf{( b )}: x_{2}(t) = e^{(-1 + i)t} \\
\mathbf{( c )}: x_{3}[n] = e^{i7\pi n} & \mathbf{( d )}: x_{4}[n] = 3e^{i( 3\pi ( n + 0.5 ) ) / 5} \\
\mathbf{( e )}: x_{5}[n] = 3e^{ i3/5(n+ 0.5 )} & \
\end{array}
\end{equation*}
\label{prob:1-9}
\end{prob}

During figuring all the problems, we have to keep in mind that for a complex
number after rotating \(2\pi\) around the origin the number returns to itself.

\begin{enumerate}
\item For \(x_{1}(t)\), only when phase \(10t\) increases multiples of \(2\pi\),
does the signal return to itself. So the fundamental period is \(\frac{2\pi}{10} = \frac{\pi}{5}\).
\item For \(x_{2}(t)\), which can be expressed as \(e^{-t}e^{it}\), because the
factor \(e^{-t}\) , the signal is not periodic.
\item For \(x_{3}[ n ]\), we have \(e^{i7\pi n} = e^{i\pi n}\), then the
fundamental period is \(\frac{2\pi}{\pi} = 2\)
\item For \(x_{4}[n]\), we have:
\begin{equation*}
\frac{3\pi N}{5} = 2\pi m
\end{equation*}
Then \(N = \frac{10m}{3}\), So fundamental period \(N=10\) when \(m=3\).
\item For \(x_{5}[n]\), because \(m\frac{2\pi \times 5}{ 3 }\) is an irrational number, so
the signal is not periodic.
\end{enumerate}
\section{Problem 1.10}
\label{sec:org6ae4e57}

\begin{prob}[]{prob:1-10}
Determine the fundamental period of the signal \(x(t) = 2\cos(10t + 1) -
     \sin(4t -1)\)
\label{prob:1-10}
\end{prob}

\(x(t)\) consists of two parts, \(2\cos(10t + 1)\) and \(-\sin(4t -1)\).
First, We figure out the fundamental period for these two signals
respectively. For \(cos(10t + 1)\), \(10T_{1} = 2\pi \to T_{1} =
     \frac{\pi}{5}\);  For \(-\sin(4t -1)\) , we have \(4T_{2} = 2\pi \to T_{2}
     = \frac{\pi}{2}\)  . Then, the fundamental period \(T = mT_{1} = nT_{2}\)
,So when \(m=5\) and  \(n=2\) , we have \(T=\pi\) , \(T\)  is the least
common multiples of \(T_{1}\) and \(T_{2}\)

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figprob1-10.pdf}
\end{center}
\section{Problem 1.11}
\label{sec:org7a4aebe}

\begin{prob}[]{prob:1-10}
Determine the fundamental period of the signal \(x[n] = 1 + e^{i4\pi n/7} -
e^{i2\pi n/5}\)
\label{prob:1-10}
\end{prob}

\(x[n]\) consists of two main parts, \(e^{i4\pi n/7}\) and \(e^{i2\pi n/5}\).
We have to figure out the two fundamental periods respectively then calculate
the least common multiple of the two fundamental periods.

For the first part we have:
\begin{equation*}
N_{1} = m \frac{2\pi}{ 4\pi /7 } = m\frac{7}{2}
\end{equation*}

So when \(m=2\), we have \(N_{1} = 7\).

For the second part we have:
\begin{equation*}
N_{2} = m \frac{2\pi}{ 2\pi /5 }
\end{equation*}

So when \(m=1\), we have \(N_{2} = 5\). The lease common multiple of \(N_{1}\)
and \(N_{2}\) is 35, i.e. the fundamental period of \(x[n]\)

It is easy to validate it. We have \(x[0] = 1 = x[35]\)
\section{Problem 1.12}
\label{sec:orgbd55a30}

\begin{prob}[]{prob:1-12}
Consider the discrete-time signal
\begin{equation*}
x[n] = 1- \sum_{k=3}^{\infty}\delta[n-1-k]
\end{equation*}
Determine the values of the integers \(M\) and \(n_{0}\) so that \(x[n]\)
may be expressed as
\begin{equation*}
x[n] = u[Mn - n_{0}]
\end{equation*}
\label{prob:1-12}
\end{prob}

By definition of \(\delta[n]\) , we know that when \(n=1+k\), \(\delta[n-1-k] =
1\). For \(x[n]\), because \(k\geq 3\), so for every \(n\geq 4\), there will
always be one \(k\) such that \(x[n] = 0\). However, for every \(n\leq 3\),
such that \(\sum_{k=3}^{\infty} \delta[n-1-k] = 1\), i.e. \(\sum_{k=3}^{\infty}
\delta[n-1-k] = 0\) for all \(n\leq 3\) , So \(x[n] = 1\) for all \(n\leq 3\).

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-12.pdf}
\end{center}

Then, by the definition of unit step function, we have \(M=-1\) and \(n_{0}=
-3\) . We can see that \(x[n]\) can be obtained by flipping the unit step signal
then right shifting it with \(3\).
\section{Problem 1.13}
\label{sec:org6ebc91b}

\begin{prob}[]{prob:1-13}
Consider the continuous-time signal
\begin{equation*}
x(t) = \delta(t+2) - \delta(t-2)
\end{equation*}
Calculate the value of \(E_{\infty}\) for the signal
\begin{equation*}
y(t) = \int_{-\infty}^{t} x(\tau) \mathrm{d} \tau
\end{equation*}
\label{prob:1-13}
\end{prob}

First let's visualize \(x(t)\) which can be shown as below

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-13a.pdf}
\end{center}

Notice the "\(1\)" along with the end of the impulses at \((-2,0)\) and \((2,0)\)  only
represent that the area of the impulse is \(1\).

For \(y(t)\), we have:
\begin{eqnarray*}
y(t)&=& \int_{-\infty}^{t} x(\tau) \mathrm{d} \tau\\
&=&
\begin{cases}
0 & t < -2 \\
1 & -2 \leq t < 2 \\
0 & 2 \leq t
\end{cases}
\end{eqnarray*}

Then,
\begin{equation*}
E_{\infty} = \lim_{T\to\infty} \int_{-T}^{T} |y(t)|^{2} \mathrm{d}t = 4
\end{equation*}

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-13b.pdf}
\end{center}
\section{Problem 1.14}
\label{sec:orgaa2c3bc}
\begin{itemize}
\item CLOSING NOTE \textit{[2020-01-27 Mon 11:00]}
\end{itemize}

\begin{prob}[]{prob:1-14}
Consider a periodic signal
\begin{equation*}
x(t) =
\begin{cases}
1, & 0\leq t\leq 1 \\
-2, & 1 < t <2
\end{cases}
\end{equation*}
with period \(T=2\), The derivative of this signal is related to the
"impulse train"
\begin{equation*}
g(t) = \sum_{k=-\infty}^{\infty} \delta(t-2k)
\end{equation*}
with period \(T=2\). It can be shown that
\begin{equation*}
\frac{\mathrm{d}x(t)}{\mathrm{d}t} = A_{1}g(t-t_{1}) + A_{2} g(t-t_{2})
\end{equation*}
Determine the values of \(A_{1},t_{1},A_{2}\) and \(t_{2}\)
\label{prob:1-14}
\end{prob}

First let's visualize \(x(t)\) and \(g(t)\) :

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-14a.pdf}
\end{center}

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-14b.pdf}
\end{center}

Then we try to figure out \(\frac{\mathrm{d}x(t)}{\mathrm{d}t}\) . By definition
of \(\delta (t)\) in section of the textbook, we know that,
\begin{equation*}
\frac{\mathrm{d}x(t)}{\mathrm{d}t} = 3\sum_{k=-\infty}^{\infty} \sigma(t-2k )  -3 \sum_{k=-\infty}^{\infty} \sigma(t-2k -1)
\end{equation*}

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-14c.pdf}
\end{center}

Compared the result with \(g(t)\), then we have \(A_{1} = 3\), \(A_{2} = -3\),
\(t_{1} = 0\) ,\(t_{2} = 1\)

\section{Problem 1.15}
\label{sec:org9bba923}

\begin{prob}[]{prob:1-15}
Consider a system \(S\) with input \(x[n]\) and output \(y[n]\). This
system is obtained through a series interconnection of a system \(S_{1}\)
followed by a system \(S_{2}\). The input-output relationships for
\(S_{1}\) and \(S_{2}\) are:
\begin{eqnarray*}
S_{1}:\quad  y_{1}[n]&=& 2x_{1}[n] + 4x_{1}[n-1] \\
S_{2}:\quad  y_{2}[n]&=& x_{2}[n-2] + \frac{1}{2}x_{2}[n-3]
\end{eqnarray*}
where \(x_{1}[n]\) and \(x_{2}[n]\) denote input signals.
\begin{enumerate}
\item Determine the input-output relationship for system \(S\)
\item Does the input-output relationship of system \(S\) change if the order
in which \(S_{1}\) and \(S_{2}\) are connected in series is reversed
(i.e., if \(S_{2}\) follows \(S_{1}\))?
\end{enumerate}
\label{prob:1-15}
\end{prob}

\subsection{\(S_{1}\) is followed by \(S_{2}\)}
\label{sec:orgf5adda9}
Because \(S_{1}\) is followed by \(S_{2}\), then the output of \(S_{1}\) is the
input of \(S_{2}\) i.e., \(y_{1}[n]\) can be treated as \(x_{2}[n]\) , So,
\begin{eqnarray*}
y_{2}[n]&=& x_{2}[n-2] + \frac{1}{2}x_{2}[n-3] \\
&=& \underbrace{2x_{1}[n-2] + 4x_{1}[n-2-1]}_{y_{1}[n-2]}  + \underbrace{\tfrac{1}{2} \Big( 2x_{1}[n-3] + 4x_{1}[n-3-1] \Big)}_{\frac{1}{2}y_{1}[n-3]} \\
&=& 2x_{1}[n-2] + 5x_{1}[n-3] + 2x_{1}[n-4]
\end{eqnarray*}

\(y_{2}\) is the final output of system \(S\), and \(x_{1}[n]\) the input.

\subsection{\(S_{2}\) is followed by \(S_{1}\)}
\label{sec:org515eee7}

If \(S_{2}\) is followed by \(S_{1}\), then \(y_{2}[n]\) can be treated by
\(x_{1}[n]\), \(y_{1}[n]\) is the final output of system \(S\) and \(x_{2}[n]\)
the input.

\begin{eqnarray*}
y_{1}[n]&=& 2x_{1}[n] + 4x_{1}[n-1] \\
&=& \underbrace{2 \Big( x_{2}[n-2]  + \tfrac{1}{2} x_{2}[n-3] \Big)}_{2{y_{2}[n]}} + \underbrace{4 \Big( x_{2}[n-1-2] + \tfrac{1}{2}x_{2}[n-3-1] \Big)}_{4y_{2}[n]}   \\
&=& 2x_{2}[n-2] + 5x_{2}[n-3] + 2x_{2}[n-4]
\end{eqnarray*}

After comparing the result from (1) we can see that the two systems are
identical, no matter who ( either \(S_{1}\) or \(S_{2}\)) comes first.

Later we will learn that for any number of linear systems, the input-output
relationship does not change no matter what order by which they are
concatenated.
\section{Problem 1.16}
\label{sec:org3634202}

\begin{prob}[]{prob:1-16}
Consider a discrete-time system with input \(x[n]\) and output \(y[n]\).
The input-output relationship for this system is
\begin{equation*}
y[n] = x[n]x[n-2]
\end{equation*}

\begin{enumerate}
\item Is the system memoryless?
\item Determine the output of the system when the input is \(A\delta[n]\),
where \(A\) is any real or complex number.
\item Is the system invertible?
\end{enumerate}
\label{prob:1-16}
\end{prob}

\begin{enumerate}
\item Is the system memoryless?

By definition, a system is memoryless if its output for each value of
the independent variable at a given time is dependent on the input at
only the same time. Obviously, the output \(y[n]\) is dependent on not
only the current time \(x[n]\) but also \(x[n-2]\). So the system is not
memoryless.

\item The output of the system \(y[n] = x[n]x[n-2] = A \delta[n] A \delta[n-2]
        = A^{2} \delta[n]\delta[n-2]\). By the definition of \(\delta[n]\), we
have \(y[n] = 0\)

\item Is the system invertible?

A system is said to be invertible if distinct inputs lead to distinct
outputs. We can take it as the input and output has one-to-one map. For
the given system, if we get one positive value, we cannot determine
where the sign come from. i.e. it can be have a positive \(x[n]\) and a
positive \(x[n-2]\) or a negative \(x[n]\) and a negative \(x[n-2]\). So
the system is not invertible.
\end{enumerate}
\section{Problem 1.17}
\label{sec:orgff04483}

\begin{prob}[]{prob:1-17}
Consider a continuout-time system with input \(x(t)\) and output \(y(t)\)
related by \(y(t) = x( \sin(t) )\).

\begin{enumerate}
\item Is this system causal?
\item Is this system linear?
\end{enumerate}
\label{prob:1-17}
\end{prob}

A system is causal if the output at any time depends on values of the input at
only the present and past times. We can anticipate the output of one causal
system based on the history of the input. When it comes to \(y(t) = x(\sin(t))\)
, we can have \(y(-\pi) = x(0), t=-\pi\). i.e. \(y(-\pi)\) is determined by
an input from the future. So the system is not causual.

If a system is linear, we have:
\begin{enumerate}
\item The response to \(x_{1}(t) + x_{2}(t)\) is \(y_{1}(t) + y_{2}(t)\).
\item The response to \(ax_{1}(t)\) is \(ay_{1}(t)\), where \(a\) is any complex
constant.
\end{enumerate}

When the input is \(a_{1}x_{1}(\sin(t)) + a_{2}x_{2}(\sin(t))\), the output
will be \(a_{1}y_{1}(t) + a_{2}y_{2}(t)\) . The system is linear.
\section{Problem 1.18}
\label{sec:org2f0d4a2}

\begin{prob}[]{prob:1-18}
Consider a discrete-time system with input \(x[n]\) and output \(y[n]\)
related by
\begin{equation*}
y[n] = \sum_{k=n-n_{0}}^{n+n_{0}} x[k]
\end{equation*}
where \(n_{0}\) is a finite positive integer.
\begin{enumerate}
\item Is this system linear?
\item Is this system time-invariant?
\item If \(x[n]\) is known to be bounded by a finite integer \(B\) , (i.e.
\(|x[n]| < B\) for all \(n\)), it can be shown that \(y[n]\) is bounded
by a finite number \(C\). We conclude that the given system is stable.
Express \(C\) in terms of \(B\) and \(n_{0}\).
\end{enumerate}
\label{prob:1-18}
\end{prob}
\subsection{linearity}
\label{sec:orgb420d77}
According to definition of linearity, suppose we have two inputs \(x_{1}[n]\)
and \(x_{2}[n]\), the reponse is \(y_{1}[n]\) and \(y_{2}[n]\). i.e.
\begin{eqnarray*}
y_{1}[n]&=& \sum_{k=n-n_{0}}^{n+n_{0}} x_{1}[k] \\
y_{2}[n]&=& \sum_{k=n-n_{0}}^{n+n_{0}} x_{2}[k] \\
\end{eqnarray*}
Then for \(x_{3}[n] = x_{1}[n] + x_{2}[n]\), we have
\begin{eqnarray*}
y_{3}[n]&=& \sum_{k=n-n_{0}}^{n+n_{0}} x_{3}[k]   \\
&=& \sum_{k=n-n_{0}}^{n+n_{0}} (x_{1}[k] + x_{2}[k]) \\
&=&\sum_{k=n-n_{0}}^{n+n_{0}} x_{1}[k]   + \sum_{k=n-n_{0}}^{n+n_{0}} x_{2}[k]   \\
&=& y_{1}[n] + y_{2}[n]
\end{eqnarray*}

When \(x_{3}[n] = ax_{1}[n]\),
\begin{eqnarray*}
y_{3}[n] &=& \sum_{k=n-n_{0}}^{n+n_{0}} x_{3}[k]   \\
&=& \sum_{k=n-n_{0}}^{n+n_{0}} ax_{1}[k] \\
&=& a y_{1}[n]
\end{eqnarray*}

So that the system is linear.
\subsection{time invariant}
\label{sec:orgee6e1e5}

If a system is time invariant, the output does not change if you input the
same signal at any time. No matter when you repeat the same experiment, you will
get the same output.

For an input \(x_{1}[n]\), we have
\begin{equation*}
y_{1}[n] = \sum_{k=n-n_{0}}^{n+n_{0}} x_{1}[k]
\end{equation*}
Suppose we have another input \(x_{2}[n] = x_{1}[n-n_{1}]\), so

\begin{eqnarray*}
y_{2}[n]&=& \sum_{k=n-n_{0}}^{n+n_{0}} x_{2}[k]  \\
&=& \sum_{k=n-n_{0}}^{n+n_{0}} x_{1}[k-n_{1}] \\
&=& \sum_{k=n-n_{1}-n_{0}}^{n-n_{1}+n_{0}} x_{1}[k] \\
&=& y_{1}[n-n_{1}]
\end{eqnarray*}

So when we have \(x_{2}[n] = x_{1}[n- n_{1}]\), then we have \(y_{2}[n] =
y_{1}[n- n_{1}]\). So, the system is time invariant.

\subsection{find \(C\)}
\label{sec:org7bac5ad}

we know that \(x[n] \leq B\), then
\begin{eqnarray*}
y[n] &=& \sum_{k=n-n_{0}}^{n+n_{0}} x[k] \\
&\leq &  \sum_{k=n-n_{0}}^{n+n_{0}} B \\
&=& ( 2n_{0} + 1 ) B
\end{eqnarray*}
So we have \(C \leq ( 2n_{0} +1 )B\).
\section{Problem 1.19}
\label{sec:orgd18fdbd}

\begin{prob}[]{prob:1-19}
For each of the following input-output relationships, determine whether
the corresponding system is linear, time invariant or both
\begin{eqnarray*}
\mathbf{(a)}\quad y(t)&=& t^{2} x(t-1) \\
\mathbf{(b)}\quad y[n]&=& x^{2}[n-2] \\
\mathbf{(c)}\quad y[n]&=& x[n+1] - x[n-1] \\
\mathbf{(d)}\quad y( t )&=& \mathrm{Odd}\{ x(t) \}
\end{eqnarray*}
\label{prob:1-19}
\end{prob}

\subsection{Problem 1.19a  \(\mathbf{(a)}: y(t)= t^{2} x(t-1)\)}
\label{sec:org87ea096}

Suppose that \(y_{1}(t)\) and \(y_{2}(t)\) are the responses for input
\(x_{1}(t)\) and \(x_{2}(t)\), respectively. Given \(x_{3}(t) = ax_{1}(t) +
bx_{2}(t)\), then we have:
\begin{equation*}
  y_{3}(t) = t^{2}x_{3}(t-1) = t^{2} \Big( ax_{1}(t-1) + bx_{2}(t-1) \Big) = ay_{1}(t) + by_{2}(t)
\end{equation*}

\textbf{So the system is linear.}

 To check whether this system is time invariant, we must
determine whether the time-invariant property holds for any input and any time
shift \(t_{0}\). Suppose when \(x_{1}(t)\) is applied we have output \(y_{1}(t)
= t^{2}x_{1}(t-1)\). We shfit \(x_{1}(t)\) with \(t_{0}\) to get
\(x_{2}(t-t_{0})\) and apply it to the system. Then we have \(y_{2}(t) =
t^{2}x_{2}(t-t_{0}-1)\) which is not the shifted version of \(y_{1}(t)\) which
is \(y_{1}(t-t_{0}) = (t-t_{0})^{2} x_{2}(t-t_{0}-1)\).  \textbf{So the system is not time invariant.}

\subsection{Problem 1.19b  \(\mathbf{(b)}: y[n]= x^{2}[n-2]\)}
\label{sec:org54f2d2d}

To check whether the system is linear or not, suppose \(x_{3}[n] = ax_{1}[n] +
bx_{2}[n]\)  then
\begin{eqnarray*}
y_{3}[n] &=& x_{3}^{2}[n-2] \\
&=& ( ax_{1}[n-2] + bx_{2}[n-2] )^{2} \\
&=& a^{2} x_{1}^{2}[n-2] + b^{2}x_{2}^{2}[n-2] + 2abx_{1}[n-2]x_{2}[n-2] \\
&\neq& ay_{1}[n] + by_{2}[n]
\end{eqnarray*}

\textbf{So the system is not linear}

\(x_{1}[n]\) will generate output \(y_{1}[n] = x_{1}^{2}[n-2]\). Suppose
\(x_{2}[n] = x_{1}[n-n_{0}]\), then we have \(y_{2}[n] = x_{2}^{2}[n-2] =
 x_{1}^{2}[n-n_{0}-2] = y_{1}[n-n_{0}]\) , i.e. when the input shift with
\(n_{0}\) the output will all shift with \(n_{0}\). \textbf{So this system is time invariant}
\subsection{Problem 1.19c \(\mathbf{(c)}: y[n]= x[n+1] - x[n-1]\)}
\label{sec:org2f58a2e}

First, we check whether or not the system is linear. consider
\begin{eqnarray*}
x_{1}[n]&\to& y_{1}[n] \\
x_{2}[n]&\to& y_{2}[n]
\end{eqnarray*}
Let \(x_{3}[n] = ax_{1}[n] + bx_{2}[n]\), then
\begin{eqnarray*}
y_{3}[n]&=& x_{3}[n+1] - x_{3}[n-1] \\
&=& ax_{1}[n+1] + bx_{2}[n+1] - ( ax_{1}[n-1] + bx_{2}[n-1] ) \\
&=& a(x_{1}[n+1] - ax_{1}[n-1]) + b(x_{2}[n+1] - x_{2}[n-2]) \\
&=& a y_{1}[n] + by_{2}[n]
\end{eqnarray*}

So
\begin{equation*}
ax_{1}[n] + bx_{2}[n] \to ay_{1}[n] + by_{2}[n]
\end{equation*}
\textbf{The system is linear.}

Second, we check whether or not the system is time invariant. let \(x_{2}[n] =
x_{1}[n-n_{0}]\) then
we have
\begin{equation*}
y_{2}[n] = x_{2}[n+1] - x_{2}[n-1] = x_{1}[n-n_{0} + 1] - x_{1}[n-n_{0} -1] = y_{1}[n-n_{0}]
\end{equation*}

So the system's output and input see the same time shift. \textbf{The system is time
invariant}

\subsection{Problem 1.19d \(\mathbf{(d)}: y(t)= \mathrm{Odd}\{ x(t) \}\)}
\label{sec:org4f05b22}

First, we check whether or not the system is linear. Considering two inputs
\(x_{1}(t)\) and \(x_{2}(t)\), we have:
\begin{eqnarray*}
y_{1}(t)&=& \mathrm{Odd}\{ x_{1}(t) \}  \\
y_{2}(t) &=& \mathrm{Odd} \{ x_{2}(t) \}
\end{eqnarray*}
Let \(x_{3}(t) = ax_{1}(t) + bx_{2}(t)\), then
\begin{eqnarray*}
y_{3}(t)&=& \mathrm{Odd} \{ x_{3}(t) \} \\
&=& \mathrm{Odd} \{ ax_{1}(t) + bx_{2}(t) \} \\
&=& \mathrm{Odd} \{ax_{1}(t) \} + \mathrm{Odd} \{ bx_{2}(t) \} \\
&=& ay_{1}(t) + by_{2}(t)
\end{eqnarray*}

\textbf{The system is linear}.

Second we check whether or not the system is time-invariant. A system is time
invariant if a time shift in the input signal results in an identical shift in
the output signal.

If we shift the input \(x(t)\) and get \(x(t-t_{0})\) then the result \(y(t)\)
we become as \(y(t-t_{0})\). Before we check the property of time-invarant,
let's first check one example. Suppose
\begin{equation*}
x_{1}(t) =
\begin{cases}
t, & 0\leq t \leq 4 \\
0, & \mathrm{otherwise}
\end{cases}
\end{equation*}

Then
\begin{equation*}
y_{1}(t) = \mathrm{Odd}\{x_{1}(t)\} = \frac{x_{1}(t)-x_{1}(-t)}{2} =
\begin{cases}
\frac{1}{2}t & -4 \leq t \leq 4 \\
0  & \mathrm{otherwise}
\end{cases}
\end{equation*}

We can visualize \(x_{1}(t)\) and \(y_{1}(t)\) as follows:

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/fig1-19d.pdf}
\end{center}

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/fig1-19db.pdf}
\end{center}

If we shift \(x_{1}(t)\) by \(2\) to obtain \(x_{2}(t) = x_{1}(t-2)\), then we have

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-19dc.pdf}
\end{center}

Then we have \(y_{2}(t)\),
\begin{equation*}
y_{2}(t) =
\begin{cases}
0, & t < -6 \\
\tfrac{1}{2}( t+2 ), & -6 \leq t \leq -2 \\
0, & -2 < t \leq 2 \\
\frac{1}{2} (t-2), & 2 < t \leq 6 \\
0, & 6 < t
\end{cases}
\end{equation*}

Then, we visualize \(y_{2}(t)\),

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-19dd.pdf}
\end{center}

Notice, by shifting \(y_{1}(t)\) by \(2\) , we have \(y_{1}(t-2)\)
\begin{equation*}
y_{1}(t-2) =
\begin{cases}
\frac{1}{2} (t-2) &  -2 \leq t \leq 6 \\
0 & \mathrm{otherwise}
\end{cases}
\end{equation*}

Now, we can derive that  \(y_{1}(t-2) \neq y_{2}(t)\) . Hence, \textbf{The system is
not time invariant} .

Also we can visualize \(y_{1}(t-2)\) to see how different
\(y_{1}(t-2)\) and \(y_{2}(t)\) are.

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-19de.pdf}
\end{center}

Now, we deduce that the system is time-invariant. For \(x_{1}(t)\), we have,
\begin{equation*}
y_{1}(t) = \mathrm{Odd}\{ x_{1}(t) \} = \frac{ x_{1}(t) - x_{1}(-t) }{2}
\end{equation*}

Now, let \(x_{2}(t) = x_{1}(t-t_{0})\) , then
\begin{equation*}
y_{2}(t) = \mathrm{Odd}\{ x_{2}(t) \} = \frac{ x_{2}(t) - x_{2}(-t) }{2} = \frac{ x_{1}(t-t_{0})  - x_{1}(-t - t_{0}) }{2}
\end{equation*}

Also, we have
\begin{equation*}
y_{1}(t-t_{0}) = \frac{ x_{1}(t-t_{0}) - x_{1}(-t + t_{0}) }{2}
\end{equation*}

Because \(y_{2}(t) \neq y_{1}(t- t_{0})\), therefore the system is not time invariant.
\section{Problem 1.20}
\label{sec:org498dd64}

\begin{prob}[]{prob:1-2020}
A continuous-time linear system \(S\) with input \(x(t)\) and output
\(y(t)\) yields the following input-output pairs:

\begin{eqnarray*}
x(t)&=& e^{i2t} \xrightarrow{S} y(t) = e^{i3t} \\
x(t)&=& e^{-i2t} \xrightarrow{S} y(t) = e^{-i3t}
\end{eqnarray*}

\begin{enumerate}
\item If \(x_{1}(t) = \cos(2t)\), determine the corresponding output
\(y_{1}(t)\) for system \(S\).
\item If \(x_{2}(t) = \cos(2(t-\frac{1}{2}))\), determine the corresponding
output \(y_{2}(t)\) for system \(S\).
\end{enumerate}
\label{prob:1-2020}
\end{prob}

\subsection{\(x_{1}(t) = \cos(2t)\)}
\label{sec:org01dbb75}

Because
\begin{equation*}
x_{1}(t) = \cos(2t) = \frac{ e^{i2t} + e^{-i2t} }{2}
\end{equation*}

The system \(S\) is linear system, so the output should be
\begin{equation*}
y_{1}(t) = \frac{ e^{i3t} + e^{-i3t} }{2} = \cos(3t)
\end{equation*}

\subsection{\(x_{2}(t) = \cos(2(t-\frac{1}{2}))\)}
\label{sec:orgf4d37cf}

Using Euler's formula, we represent \(x_{2}(t)\) using the exponential form.

\begin{eqnarray*}
 x_{2}(t) &=& \frac{ e^{i(2(t-\frac{1}{2}))}  + e^{-i(2(t-\frac{1}{2}))} }{2} \\
&=& \frac{1}{2} e^{-i}e^{i2t} + \frac{1}{2}e^{i}e^{-i2t}
\end{eqnarray*}

Because \(\frac{1}{2}e^{i}\) and \(\frac{1}{2}e^{-i}\) are complex constants and
the system is linear, so we have the output
\begin{equation*}
y_{2}(t) = \frac{1}{2}e^{-i}e^{i3t} + \frac{1}{2}e^{i}e^{-i3t} = \frac{ e^{i3(t-\tfrac{1}{3})}  + e^{-i3(t-\tfrac{1}{3})}}{2} = \cos(3(t- \tfrac{1}{3}))
\end{equation*}

Therefore we have \(y_{2}(t) = \cos(3(t-\tfrac{1}{3}))\).
\end{document}

### 2021-02-17 msteamc/index.tex
trivial update

@@
 \date{\today}
-\title{Signals and Systems Chapter 1 Problems Part 1 (1.1-1.20)}
+\title{Export Markdown and latex using Emacs Org}
 \hypersetup{
  pdfauthor={Eason},
- pdftitle={Signals and Systems Chapter 1 Problems Part 1 (1.1-1.20)},
+ pdftitle={Export Markdown and latex using Emacs Org},
  pdfkeywords={},
- pdfsubject={This post consists of solutions to problems from 1.1 to 1.21 in chapter 1 of the book Signals and Systems by Oppenheim ,Willsky and Nawab.},
+ pdfsubject={set up the Emacs org and ox-hugo to export the org files in markdown and latex format.},
  pdfcreator={Emacs 26.3 (Org mode 9.3.7)},
@@
 
- \thispagestyle{empty}
- \begingroup
-\begin{center}
- \vspace{\baselineskip}
- \textbf{\Huge Signal and System Chapter 1 Problems} \par
- \vspace{2\baselineskip}  \newline
- \textbf{\large Eason Zhang with www.makesteamclear.com \par}
- \vspace{\baselineskip} \newline
-  \today \par
- \vspace{\baselineskip}
-  \vfill
- \setlength{\unitlength}{3pt}
- \includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/eulerEquation.pdf}
- \vfill \vspace{\baselineskip}
- \href{WWW.MAKESTEAMCLEAR.COM}{\Large WWW.MAKESTEAMCLEAR.COM} \par\newline
-  makesteamclear is a free project, run by Eason Zhang, to make videos about STEAM in a more approachable way.
-If you find the contents in this article or the site or the youtube channel helpful, please consider \href{www.makesteamclear.com}{\ensuremath \heartsuit support me\ensuremath\heartsuit }, thanks \par
- \end{center}
- \endgroup
-
- \newpage \thispagestyle{empty} \textbf{copyright page} \newpage \tableofcontents \newpage
 \hspace{0pt}\\
 
-This post consists of solutions to problems from 1.1 to 1.21 in chapter 1 of the book Signals and Systems by Oppenheim ,Willsky and Nawab.
+set up the Emacs org and ox-hugo to export the org files in markdown and latex format.
 
-\section{Problem 1.1}
-\label{sec:org3c85e3e}
+\section{Introduction}
+\label{sec:orgc771d89}
 
-\begin{prob}[]{prob:1.3}
-Problem 1.1: Express each of the following complex numbers in \emph{Cartesian} form \(x+iy\):
-\begin{equation*}
-\begin{array}{ccc}
- \frac{1}{2}e^{i\pi}  & \frac{1}{2}e^{-i\pi}  & e^{i\pi/2}  \\
- e^{-i\pi/2}         & e^{i5\pi/2}  & \sqrt{2}e^{i\pi/4}  \\
- \sqrt{2}e^{i9\pi/4} & \sqrt{2}e^{-i9\pi/4}  & \sqrt{2} e^{-i\pi/4}
-\end{array}
-\end{equation*}
-\label{prob11}
-\end{prob}
+I use hugo before it support Emacs org file. Then I use an Emacs extension
+called \href{https://github.com/kaushalmodi/ox-hugo}{ox-hugo} which is a carefully crafted Org exporter back-end for Hugo.
+Ox-hugo meets all my requirement and definitely worth a try when you are an
+advanced user of Emacs Org. By the way, if you are quite familiar with Emacs
+Org, there is no need to take time to learn markdown. Emacs Org, I think, is
+more elegant than markdown.
 
-First, let's figure them out using the Euler's formula. For the nine complex
-numbers in  \hyperref[prob11]{Problem 1.1}, we have:
+\section{set up ox-hugo}
+\label{sec:orgd4e98d9}
 
-\begin{eqnarray*}
-\tfrac{1}{2} e^{i\pi } &=&  \tfrac{1}{2} (\cos(\pi) + i\sin(\pi) ) = \tfrac{1}{2} \cos(\pi) = -\tfrac{1}{2} \\
-\tfrac{1}{2} e^{-i\pi} &=& \tfrac{1}{2}  (\cos(-\pi) + i\sin(-\pi) ) = \tfrac{1}{2} \cos(-\pi) = -\tfrac{1}{2} \\
-e^{i\pi/2} &=& \cos(\pi/2) + i \sin(\pi/2) = i \\
-e^{-i\pi/2} &=& \cos(-\pi/2) + i \sin(-\pi/2) = -i \\
-e^{i5\pi/2} &=& \cos(5\pi/2) + i \sin(5\pi/2) = \cos(2\pi + \pi/2) + i \sin(2\pi + \pi/2) = i \sin(\pi/2) = i \\
-\sqrt{2}e^{i\pi/4} &=& \sqrt{2} ( \cos(\pi/4) + i \sin(\pi/4) ) = \sqrt{2} ( \tfrac{\sqrt{2}}{2} + i\tfrac{\sqrt{2}}{2}  ) = 1 + i \\
- \sqrt{2} e^{i9 \pi/4} &=& \sqrt{2} ( \cos(9\pi/4) + i \sin(9\pi/4) ) = 1 + i \\
- \sqrt{2} e^{-i9 \pi/4} &=& \sqrt{2} ( \cos(-9\pi/4) + i \sin(-9\pi/4) ) = 1 - i \\
- \sqrt{2} e^{-i \pi/4} &=& \sqrt{2} ( \cos(-\pi/4) + i \sin(-\pi/4) ) = 1 - i
-\end{eqnarray*}
+I use Spacemacs and integrate ox-hugo into my config is easy. You can add it
+into your private layer or just add it in your \texttt{user-config} . Please refer to
+\href{https://github.com/kaushalmodi/ox-hugo}{the repo.} and read the document for more information.
 
-\section{Problem 1.2}
-\label{sec:orgbdb3cb8}
+The first time you want to export an Org file or a subtree of an Org file, use
+\texttt{M-x org-hugo-export-to-md} . There will be a hugo-related section in the
+\texttt{org-dispatcher} whenever you use \texttt{C-c C-e} .
+\section{use Org Macro replacement}
+\label{sec:org3a92f3b}
 
-\begin{prob}[]{prob:1.3}
-Problem 1.2: Express each of the following complex numbers in \emph{polar} form (\(re^{i\theta},
- -\pi < \theta \leq \pi\)):
-\begin{equation*}
-\begin{array}{c{3cm}c{3cm}c{3cm}}
-5 & -2 & -3i \\
-\frac{1}{2} - i \frac{\sqrt{3}}{2} & 1+i & (1-i)^{2} \\
-i(1-i)  & \frac{1+i}{1-i}  & \frac{\sqrt{2} + i \sqrt{2}}{1+i\sqrt{3}}
-\end{array}
-\end{equation*}
-\label{prob12}
-\end{prob}
+Often, you want different actions when you export the Org file to
+hugo-compatible markdown and latex file. For example, hugo or hugo theme supports
+summary and shortcodes such as \texttt{alert note} and \texttt{alert warning} (see  \href{https://sourcethemes.com/academic/docs/writing-markdown-latex/}{Writing
+content with Markdown, \LaTeX{}, and Shortcodes | Academic} )
 
-For the nine complex numbers in  \hyperref[prob12]{Problem 1.2} , we have:
+When you export the snippet to markdown then hugo will display the content
+according to the css. However, latex does not recognize the shortcodes. So latex
+will display \texttt{\{ \{\% alert note \%\} \}} literally which is clutter. The Org Macro may
+help. For more information please refer to \href{https://orgmode.org/manual/Macro-replacement.html}{The Org Manual: Macro replacement} and
+\href{https://github.com/fniessen/org-macros}{fniessen/org-macros: Shared macros for Org mode} . I also define my own Org Macro
+in \href{https://github.com/msteamc/.spacemacs.d/blob/master/org-templates/enpost.org}{my setup file for every .org file}. With Org Macro, I control some contents
+and options exist only for certain backend.
 
-\begin{eqnarray*}
- 5 &=& 5 e^{i0} = 5 e^{i(2\pi n)}, n\in \{\ldots, -2,-1,0,1,2,\ldots \} \\
- -2 &=& 2 e^{i\pi} = -2 e^{i0} \\
- -3i &=& 3 e^{-i\pi} \\
- \tfrac{1}{2} - i \tfrac{\sqrt{3}}{2}  &=& e^{-i\pi/3} \\
- 1+i &=& \sqrt{2} e^{i\pi/4} \\
- (1-i)^{2} &=& ( \sqrt{2} e^{-i\pi/4} )^{2} = 2 e^{-i\pi/2} \\
- i(1-i) &=& 1 - i = \sqrt{2} e^{-i\pi/4} \\
- \tfrac{1+i}{1-i} &=& \tfrac{ \sqrt{2}e^{i\pi/4} } { \sqrt{2}e^{-i\pi/4} } = e^{i\pi/2} \\
- \tfrac{\sqrt{2} + i \sqrt{2}}{1+i\sqrt{3}} &=& \tfrac{ 2e^{i\pi/4} }{ 2 e^{i\pi/3} } = e^{-i\pi/12}
-\end{eqnarray*}
+Once you are familiar with Org Macro, It behaves beyond your imagination.
+\section{use the setupfile for each Org file}
+\label{sec:org956dd85}
 
-Every complex number \(a+ib\) can be visualized in the complex plane
-\(\mathbb{C}\). It can be viewed either as the point with the coordinate
-\((a,b)\) or as a vector starting from \(( 0,0 )\) to the point \((a,b)\).
+Often, you options for a org file grows more and more. If you think it kind of
+clutter at the top of your Org files, you can group them in a setupfile then
+include it at the top of your Org file.
 
-Also every complex number \(a+ib\) can be represented in the exponential form
-conveniently by using the Euler's formula \(e^{i\alpha} = \cos\alpha +
- i\sin\alpha\). One complex number have unique Cartesian form but many
-expoential forms. Taking \(1+i\) for example, its expoential form can be
-\(\sqrt{2}e^{i(\pi/4 + 2n\pi)}, n\in \{ \ldots, -2,-1,0,1,2,\ldots \}\). When
-we express a complex number in expoential form, it helps to keep a concept of
-rotation in mind. In the complex plane \(\mathbb{C}\), a complex number will
-return to itself if it rotates a multiple of \(2\pi\) around the origin point
-with radius equal to its modulus. please keep the concept of roatation in mind
-and it will become increasingly important during our later study.
+For my setupfiles, please refer to \href{https://github.com/msteamc/.spacemacs.d/tree/master/org-templates}{my org-templates}. As you can see, I have
+several setupfiles for different aims. To include one of them in my Org file, I
+use:
 
-In the development of complex analysis, \(a+ib\) has another form \(r\angle
- \theta\), where \(r\) is the modulus and \(\theta\) the argument (or the
-angle). Obviously, this notation is not as good as the expoential form,
-espacialy when we want to do complex analysis such as differentiation and
-integration. We just mention it here for the sake of completion. The expoential
-form will be deployed from now on.
+\texttt{\#+SETUPFILE: <path+name of the setup files>}
+
+By using \texttt{\#+SETUPFILE} ,I only have to option lines at the top of my org file.
+So it looks clean.
+
+Also, you can notice that in \href{https://github.com/msteamc/.spacemacs.d/blob/master/org-templates/enpost.org}{my setupfile named enpost.org} exists options for
+different export targets.
 
 \begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/eulerEquation.pdf}
+\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProbzzzzzzzz.pdf}
 \end{center}
-
-Now, let's go back to \hyperref[prob11]{Problem 1.1} and Problem \hyperref[prob12]{Problem
-1.2}. It's easy to figure the answers out using the Euler's formula. Let's do
-more to show them on the complex plane keeping the concept of rotation in mind.
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/problem1_1.pdf}
-\caption{\label{problem1-1}visualized the complex numbers from Problem \hyperref[prob11]{Problem 1.1} in the complex plan}
-\end{figure}
-
-From Figure \ref{problem1-1} , taking \(\color{green}{\tfrac{1}{2}e^{i\pi}}\) and
-\(\color{red}{\tfrac{1}{2}e^{-i\pi}}\) for example, in the complex plane, they
-are the same point \(-\tfrac{1}{2}\) which means \(-\tfrac{1}{2}\) can be
-reached by rotating \(\tfrac{1}{2}\) with angle \(\pi\) anti-clockwise or with angle
-\(-\pi\) clockwise. Essentially, this is because that \(e^{i\theta} =
- e^{i(\theta + 2n\pi)}, n\in \{\ldots,-2,-1,0,1,2,\ldots\}\). It's
-straightforward that \(e^{i\pi} = e^{i(\pi + 2(-1)\pi)} = e^{-i\pi}\).
-
-In the end of \hyperref[prob11]{Problem 1.1} and \hyperref[prob12]{Problem 1.2}, I want to say
-more about expressing \(\tfrac{1+i}{1-i}\) in its polar form. There are two
-methods to get the polar form:
-\begin{enumerate}
-\item multiply the fraction's numerator and denominator by \(( 1 + i )\)
-
-So we have:
-\begin{eqnarray*}
-\frac{1+i}{1-i}& = & \frac{(1+i)(1+i)}{(1-i)(1+i)} \\
-&=& \frac{2i}{2} = i
-\end{eqnarray*}
-
-\item express the numerator and denominator in expoential form first, then do the
-following calculation.
-
-\begin{eqnarray*}
-\frac{1+i}{1-i} &=& \frac{\sqrt{2}e^{i\pi/4}}{\sqrt{2}e^{-i\pi/4}}  \\
-&=& e^{i2\pi/4} = e^{i\pi/2} = i
-\end{eqnarray*}
-\end{enumerate}
-\section{Problem 1.3}
-\label{sec:org975ac37}
-
-\begin{prob}[]{prob:1.3}
-Problem 1.3: Determine the values of \(P_{\infty}\) and \(E_{\infty}\) for each
-of the following signals:
-\begin{equation*}
-\begin{array}{ll}
-\mathrm{(a)} \quad x_{1}(t) = e^{-2t}u(t) & \mathrm{(b)} \quad x_{2}(t) = e^{i(2t + \pi/4)} \\
- \mathrm{(c)} \quad x_{3}(t) = \cos(t) & \mathrm{(d)} \quad x_{1}[n] = (\tfrac{1}{2})^{n} u[n] \\
- \mathrm{( e )} \quad x_{2}[n] = e^{i(\pi/2n + \pi/8)} & \mathrm{(f)} \quad x_{3}[n] = \cos(\tfrac{\pi}{4}n)
-\end{array}
-\end{equation*}
-\label{prob13}
-\end{prob}
-
-Before solving this problem, let's review the definition of \(P_{\infty}\) and
-\(E_{\infty}\). For a continuous time signal \(x(t)\), we have
-\begin{eqnarray}
-\label{eq:2}
-E_{\infty}&=& \lim_{T\to \infty} \int_{-T}^{T} |x(t)|^{2}\mathrm{d}t \\
-P_{\infty}&=& \lim_{T\to \infty} \frac{1}{2T}\int_{-T}^{T} |x(t)|^{2}\mathrm{d}t = \lim_{T\to\infty} \frac{E_{\infty}}{2T}
-\end{eqnarray}
-For a discrete time signal \(x[n]\), we have:
-\begin{eqnarray}
-\label{eq:3}
-E_{\infty}&=& \lim_{N\to \infty} \sum_{n=-N}^{+N} |x[n]|^{2} \\
-P_{\infty}&=& \lim_{N\to \infty} \frac{1}{2N+1} \sum_{n=-N}^{+N} |x[n]|^{2} = \lim_{N\to\infty} \frac{E_{\infty}}{2N+1}
-\end{eqnarray}
-
-Equation (\ref{eq:2})(\ref{eq:3}) are not only mathmatical definitions but also
-related to physical quantities such as power and energy in a physical system.
-For an electric circuit, taking the voltage \(v(t)\) and current \(i(t)\) across
-a resistor for example, the power at time \(t\) can be calculated by:
-\begin{equation}
-\label{eq:4}
-p(t) = v(t)i(t) = \frac{v^{2}(t)}{R}
-\end{equation}
-Let's go back to equation (\ref{eq:2}) and equation(\ref{eq:3}), if
-\(E_{\infty}< \infty\) we say that the signal has finite energy otherwise
-infinite energy. If \(P_{\infty} <\infty\) we say that the signal has finite
-power otherwise infinite power.
-
-Next let's determine the values of \(P_{\infty}\) and \(E_{\infty}\) for the
-given signals.
-\subsection{Problem1.3a \(\mathbf{(a)}: x_{1}(t)= e^{-2t}u(t)\)}
-\label{sec:orge15cb02}
-
-\begin{eqnarray*}
-E_{\infty}  & =  & \int_{\infty}^{\infty} |e^{-2t}u(t)|^{2} \mathrm{d}t \\
-&=& \int_{0}^{\infty} e^{-4t} \mathrm{d}t \\
-&=& \frac{1}{4}
-\end{eqnarray*}
-So, it's straightforward that:
-\begin{equation}
-\label{eq:5}
-P_{\infty} = \lim_{T\to \infty} \frac{E_{\infty}}{2T}  = 0
-\end{equation}
-
-\begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figprob1-3.pdf}
-\end{center}
-
-\subsection{Problem1.3b \(\mathbf{(b)}: x_{2}(t)= e^{i(2t+\pi/4)}\)}
-\label{sec:orgf93273c}
-
-We have \(|e^{i(2t+\pi/4)}| = 1\) , therefore
-\begin{eqnarray*}
-E_{\infty}&=& \int_{\infty}^{\infty} |x_{2}(t)= e^{i(2t+\pi/4)}|^{2} \mathrm{d}t \\
-&=& \infty
-\end{eqnarray*}
-
-For power \(P_{\infty}\), we have:
-\begin{eqnarray*}
-P_{\infty}&= &\lim_{T\to\infty} \frac{1}{2T}\int_{-T}^{T} |x_{2}(t)|^{2} \mathrm{d}t  \\
-&=& 1
-\end{eqnarray*}
-
-This signal has constant power. If you keep the concept of rotation mentioned in
-Problem \ref{prob11}, you will notice immediately that all the points generated by
-\(x_{2}(t)\) lies on the unit circle.
-
-\subsection{Problem 1.3c \(\mathbf{(c)}:x_{3}(t)=\cos(t)\)}
-\label{sec:org2d00fa8}
-
-\begin{eqnarray*}
-E_{\infty}&=& \lim_{T\to\infty} \int_{-\infty}^{\infty} |x_{3}(t)|^{2} \mathrm{d}t \\
-&=& \int_{\infty}^{\infty} \cos(t)^{2} \mathrm{d}t = \infty
-\end{eqnarray*}
-
-\begin{eqnarray*}
-P_{\infty}&=& \lim_{T\to\infty} \frac{1}{2T}\int_{-T}^{T} |x_{3}(t)|^{2} \mathrm{d}t  \\
-&=& \lim_{T\to\infty}\frac{1}{2T} \int_{-T}^{T} \cos(t)^{2} \mathrm{d}t \\
-&=& \lim_{T\to\infty} \frac{1}{2T} \int_{-T}^{T} \frac{1+\cos(2t)}{2} \mathrm{d}t = \frac{1}{2}
-\end{eqnarray*}
-
-\(x_{3}(t)\)  can be visualized as follows:
-
-\begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figprob1-3c.pdf}
-\end{center}
-
-\subsection{Problem 1.3d \(\mathbf{(d):} \quad x_{1}[n] = (\tfrac{1}{2})^{n} u[n]\)}
-\label{sec:org9332415}
-
-By definition, we have:
-\begin{eqnarray*}
-E_{\infty}&=&\lim_{N\to\infty}\sum_{n=-N}^{N} \big((\tfrac{1}{2})^{n}u[n]\big)^{2} \\
-&=&\lim_{N\to\infty}\sum_{n=0}^{N} (\tfrac{1}{4})^{n} \\
-&=& \tfrac{4}{3}
-\end{eqnarray*}
-
-Then,
-\begin{eqnarray*}
-P_{\infty}&=& \lim_{N\to\infty} \frac{1}{2N+1} \sum_{n=-N}^{N} \big((\tfrac{1}{2})^{n}u[n]\big)^{2}   \\
-&=& 0
-\end{eqnarray*}
-
-\(x_{1}[n]\) can visualized as:
-\begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figprob1-3d.pdf}
-\end{center}
-
-\section{Problem 1.4}
-\label{sec:orgcfde750}
-
-\begin{prob}[]{prob:1-4}
- Problem 1.4: Let \(x[n]\) be a signal with \(x[n]=0\) for\(n< -2\) and \(n>4\),
-for each signal given below, determine the values of \(n\) for which it is
-guaranteed to be zero.
-\begin{eqnarray*}
-\mathbf{ (a) } & & x[n-3] \\
-\mathbf{ (b) } & & x[n+4] \\
-\mathbf{ (c) } & & x[-n]  \\
-\mathbf{ (d) } & & x[-n+2] \\
-\mathbf{ (e) } & & x[-n-2]
-\end{eqnarray*}
-\label{prob:1-4}
-\end{prob}
-
-For the given signals \(\mathbf{(a)}\) to \(\mathbf{(e)}\), the transformations
-of the variable \(n\) will change the interval in which the signals are zero.
-For the convenience of calculation, we write the origin signal as:
-\begin{equation*}
-x[m] = 0, m< -2 \quad \mathrm{and} \quad m>4
-\end{equation*}
-
-We can visualize \(x(m)\) as below (I just give an example, you can name any
-signal that satisfy \(x[m] = 0, m< -2 \ \mathrm{and} \ m>4\)):
-
-\begin{center}
-\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-4.pdf}
-\end{center}
-
-\subsection{Problem 1.4a \(\mathbf{(a)}:x[n-3]\)}
-\label{sec:org897c6ea}
-
-For signal \(\mathbf{(a)}\), to get the interval where \(x[n-3] = 0\), we have:
-\begin{eqnarray*}
-  m=n-3 &<& -2 \\
-  m=n-3 &>& 4
-\end{eqnarray*}
- Then, we have \(n < 1 \ \mathrm{and} \ n > 7\) from which we can see that
-the new signal is a right shift three relative to the origin signal, i.e. new
-signal is delayed with three.
-
-\begin{center}
-\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-4a.pdf}
-\end{center}
-
-\subsection{Problem 1.4b \(\mathbf{(b)}:x[n+4]\)}
-\label{sec:org9176217}
-
-For signal \(\mathbf{(b)}\), we have:
-\begin{eqnarray*}
-m=n+4&<&-2 \\
-m=n+4&>&4
-\end{eqnarray*}
-Then, we have \(n<-6\ \mathrm{and}\ n>0\) from which we can see that the new
-signal is a left shift four relative to the origin signal, i.e. new
-signal is advanced with four.
-
-\begin{center}
-\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-4b.pdf}
-\end{center}
-
-\subsection{Problem 1.4c \(\mathbf{(c)}: x[-n]\)}
-\label{sec:org71c1184}
-
-For signal \(\mathbf{( c )}\), we have:
-\begin{eqnarray*}
-m=-n&<&-2 \\
-m=-n&>&4
-\end{eqnarray*}
-
-Then, we have \(n>2\ \mathrm{and} \ n<-4\) from which we can see that the new
-signal is a reversal of the origin signal.
-
-\begin{center}
-\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-4c.pdf}
-\end{center}
-
-\subsection{Problem 1.4d \(\mathbf{(d)}: x[-n+2]\)}
-\label{sec:org0b89113}
-
-for signal \(\mathbf{(d)}\), we have:
-\begin{eqnarray*}
-m=-n+2&<&-2 \\
-m=-n+2&>&4
-\end{eqnarray*}
-Then, we have \(n>4\ \mathrm{and}\ n<-2\). For \(x[-n+2]\), we can first
-flip the original signal then right shift the flipped signal by 2. Notice the
-contents in the brackets \(-(n+2)\). I would like treat it as \(-(n-2)\), by
-which I know that the minus symbol means reversal and \(-2\) means right
-shift by 2.
-
-\begin{center}
-\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-4d.pdf}
-\end{center}
-
-\subsection{Problem 1.4e \(\mathbf{(e)}: x[-n-2]\)}
-\label{sec:org04ff18a}
-
-For signal \(\mathbf{(e)}\), we have:
-
-\begin{eqnarray*}
-m=-n-2&<&-2 \\
-m=-n-2&>&4
-\end{eqnarray*}
-
-Then, we have \(n>0 \ \mathrm{and}\ n<-6\). To get the new signal, we have
-to filp the original signal first then left shift the flipped signal by two.
-
-\begin{center}
-\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-4e.pdf}
-\end{center}
-
-\section{Problem 1.5}
-\label{sec:org8c8f6ba}
-
-\begin{prob}[]{prob:1-5}
-Let \(x(t)\) be a signal with \(x(t)=0, \ x<3\). For each signal
-given below, determine the values of \(t\) for which it is guaranteed to be
-zero.
-
-\begin{equation*}
-\begin{array}{ll}
-\mathbf{(a)}: x(1-t) \qquad  &   \mathbf{(b)}: x(1-t) + x(2-t)\qquad   \\
-\mathbf{(c)}: x(1-t)x(2-t)\qquad &  \mathbf{(d)}: x(3t) \qquad  \\
-  \mathbf{(e)}: x(t/3)\qquad & \\
-\end{array}
-\end{equation*}
-\label{prob:1-5}
-\end{prob}
-
-For signal \(\mathbf{(a)}: x(1-t)\),  we have:
-\begin{equation*}
-1-t < 3
-\end{equation*}
-
-So, \(t>-2\). Signal \(\mathbf{(a)}: x(1-t)\) can be achieved by flipping the
-origin signal first then right shifting one.
-
-For signal \(\mathbf{(b)}: x(1-t) + x(2-t)\) , we have:
-\begin{eqnarray*}
-1-t&< &3 \\
-2-t&<& 3
-\end{eqnarray*}
-Because it a "\(+\)" between \(x(1-t)\) and \(x(2-t)\) so only when both of the
-two signals are zero, the result will be zero. For the first part we have the
-value zero when \(t>-2\) the second \(t>-1\), so the result will be the
-intersect of these two intervals, i.e. \(t>-1\) . we achieve signal
-\(\mathbf{(b)}: x(1-t) + x(2-t)\) by adding signal \(\mathbf{(a)}: x(1-t)\)
-with a second signal \(x(2-t)\) which can be achieved by flipping it first then
-right shifting two.
-
-For signal \(\mathbf{(c)}: x(1-t)x(2-t)\), \(x(1-t)\) is multiplied by
-\(x(2-t)\), so if any one of these two signals is zero, the result is zero.
-Based on the result of signal \(\mathbf{( b )}\), we have \(t>-2\).
-
-For signal \(\mathbf{( d )}: x(3t)\), we have:
-\begin{equation*}
-3t < 3
-\end{equation*}
-Then, \(t<1\). The signal is compressed by \(3\).
-
-For signal \(\mathbf{( e )}: x(t/3)\), we have:
-\begin{equation*}
-t/3 < 3
-\end{equation*}
-Then, \(t<9\). The signal is streched by \(3\).
-
-\section{Problem 1.6}
-\label{sec:orgb735a47}
-
-\begin{prob}[]{prob:1-6}
-Determine whether or not each of the following signals is periodic:
-
-\begin{eqnarray*}
-&&  \mathbf{(a)}: x_{1}(t) = 2e^{i(t+\pi/4)}u(t) \\
-&&  \mathbf{( b )}: x_{2}[n] = u[n] + u[-n]  \\
-&&  \mathbf{(c)}: x_{3}[n] = \sum_{k=-\infty}^{\infty} \{ \delta[n-4k] - \delta[n-1-4k] \}
-\end{eqnarray*}
-\label{prob:1-6}
-\end{prob}
-
-\begin{itemize}
-\item \(x_{1}(t)\) is not periodic because \(u(t) = 0, t<0\)
-\item \(x_{2}[n]\) is not periodic because
-\begin{equation*}
-x_{2}[n] =
-\begin{cases}
-2 & n=0 \\
-1 & n\neq 0
-\end{cases}
-\end{equation*}
-\item For signal \(x_{3}[n]\) we know that with a \(n\), \(\delta[n-4k]\) and
-\(\delta[n-1-4k]\) can not be zero at the same time. Because \(k\) and
-\(n-4k\) must be integers, \(\delta[n-4k]\) and \(\delta[n-1-4k]\) will repeat
-themself every four steps. Furthermore, for every \(n\), the \(k\) runs from
-\(-\infty\) to \(\infty\), and only one \(k\) will match the \(n\) to set
-\(\delta[n-4k]\) or \(\delta[n-1-4k]\) as zero. We can test it by setting
-\(n = 0,1,2,\ldots\)
-\begin{eqnarray*}
-&& x[0] = 1,\quad x[1] = -1, \quad x[2] = 0, \quad x[3] = 0 \\
-&& x[4] = 1,\quad x[5] = -1, \quad x[6] = 0, \quad x[7] = 0 \\
-&& x[8] = 1,\quad x[9] = -1, \quad x[10] = 0, \quad x[11] = 0
-\end{eqnarray*}
-
-\begin{center}
-\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figprob1-6.pdf}
-\end{center}
-\end{itemize}
-
-\section{Problem 1.7}
-\label{sec:org292be4b}
-
-\begin{prob}[]{prob:1-7}
-For each signal given below, determine all the values of the independent
-variable at which the even part of the signal is guaranteed to be zero.
-
-\begin{equation*}
-\small
-\begin{array}{ll}
- \mathbf{(a)}: x_{1}[n] = u[n] - u[n-4] \qquad  &   \mathbf{(b)}: x_{2}(t) = \sin(\tfrac{1}{2} t) \qquad   \\
-  \mathbf{(c)}: x_{3}[n] = (\frac{1}{2})^{n} u[n-3] \qquad &  \mathbf{(d)}: x_{4}(t) = e^{-5t}u(t+2) \\
-\end{array}
-\end{equation*}
-\label{prob:1-7}
-\end{prob}
-
-\subsection{Problem 1.7a \(\mathbf{(a)}: x_{1}[n] = u[n] - u[n-4]\)}
-\label{sec:orgcc2fcf2}
-
-Any signal \(x_{1}(t)\) consists of two parts, even part \(\mathrm{Ev}
-\{x_{1}(t)\}\) and odd part \(\mathrm{Od} \{ x_{1}(t)\}\). For signal \(\mathbf{(a)}\), when the signal is zero, we have the domain of the independent
-value \(n< 0\) and \(n \geq 4\) , so the even part of the signal will be
-zero when \(n\leq 4\) and \(n\geq 4\). \(x_{t}(t)\) and its even part and odd
-part can be illustrated as:
-
-\begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figprob1-7.pdf}
-\end{center}
-
-\begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figprob1-7ab.pdf}
-\end{center}
-
-\begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figprob1-7ac.pdf}
-\end{center}
-
-\subsection{Problem 1.7b \(\mathbf{(b)}: x_{2}(t) = \sin(\tfrac{1}{2} t)\)}
-\label{sec:orge473634}
-For signal \(x_{2}(t) = \sin (\frac{1}{2} t)\), because it is an odd signal, so
-for all \(t\), the even part of \(x_{2}(t)\) is zero.
-
-\begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/fig1-7b.pdf}
-\end{center}
-
-Notice that for \(\sin(\frac{1}{2}t)\), the signal can be obtained by streching
-\(\sin(t)\) with a factor \(2\). In particular, the fundamental period is \(4\pi\).
-
-\subsection{Problem 1.7c \(\mathbf{(c)}: x_{3}[n] = ( \frac{1}{2} )^{n} u[n-3]\)}
-\label{sec:orgbe754f7}
-
-For signal \(x_{3}[n] = ( \frac{1}{2} )^{n} u[n-3]\), which will be zeros for
-\(n<3\). By definition, the even part of \(x_{3}[n]\) will be zeros for \(|n| <
-3\). Actually, we do not visualize the signal to draw such a conclusion. For the
-sake of visualization, I illustrate the signal as below:
-
-\begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-7ca.pdf}
-\end{center}
-
-\begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-7cb.pdf}
-\end{center}
-
-\begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-7cc.pdf}
-\end{center}
-
-\subsection{Problem 1.7d \(\mathbf{(d)}: x_{4}(t) = e^{-5t}u(t+2)\)}
-\label{sec:orgca169be}
-
-For signal \(\mathbf{(d)}: x_{4}(t) = e^{-5t}u(t+2)\), we have \(x_{4}(t) = 0,\
-t<-2\). Because the even and odd part is symmetrical with y-axis, there is no
-\(t\) at which the even and odd part of will be zero.
-
-\begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-7da.pdf}
-\end{center}
-
-\section{Problem 1.8}
-\label{sec:org9d56250}
-
-\begin{prob}[]{prob:1-8}
-Express the real part of each of the following signals in the form
-\(Ae^{-at}\cos(\omega t + \phi)\), where \(A,a,\omega, \phi\) are real numbers
-with \(A>0\) and \(-\pi < \phi \leq \pi\):
-\begin{equation*}
-\small
-\begin{array}{ll}
-  \mathbf{( a )}: x_{1}(t) = -2 &  \mathbf{( b )}: x_{2}(t) = \sqrt{2}e^{i\pi/4}\cos(3t + 2\pi) \\
-  \mathbf{( c )}: x_{3}(t) = e^{-t}\sin(3t + \pi) & \mathbf{( d )}: x_{4}(t) = i e^{(-2+i100)t}
-\end{array}
-\end{equation*}
-\label{prob:1-8}
-\end{prob}
-
-\begin{enumerate}
-\item \(\mathrm{Re}\{x_{1}(t)\} = -2 = 2e^{-0t}\cos(0t + \pi)\) with \(A = 2,
-   a=0, \omega = 0, \phi = \pi\)
-\item \(\mathrm{Re} \{x_{2}(t)\} = \mathrm{Re} \{ \sqrt{2} ( \cos( \pi/4 ) + i
-   \sin (\pi/4) ) \cos(3t) \} = \cos(3t) = e^{-0t}\cos( 3t + 0 )\) with \(A =
-   1\), \(a = 0\), \(\omega = 3\),\(\phi = 0\)
-\item \(\mathrm{Re} \{ x_{3}(t) \} = \mathrm{Re} \{ e^{-t} \sin ( 3t + \pi )  \}
-   = e^{-t}\cos(3t + \pi/2)\) with \(A=1\), \(a=1\), \(\omega=3\), \(\phi=\pi/2\)
-\item \(\mathrm{Re} \{x_{4}(t)\}   = \mathrm{Re} \{
-   e^{i\pi/2} e^{(-2+i100)t} \} = \mathrm{Re}\{ e^{(-2 + i100)t + i\pi/2} \} =
-   e^{-2t}\cos(100t + \pi/2)\) with\(A = 1\), \(a=2\), \(\omega=100\), \(\phi=\pi/2\)
-\end{enumerate}
-
-\section{Problem 1.9}
-\label{sec:orgea8c035}
-
-\begin{prob}[]{prob:1-9}
-Determine whether or not each of the following signals is periodic. If a signal
-is periodic, specify its fundamental period.
-
-\begin{equation*}
-\begin{array}{ll}
-\mathbf{( a )}: x_{1}(t) = ie^{i10t} &  \mathbf{( b )}: x_{2}(t) = e^{(-1 + i)t} \\
-\mathbf{( c )}: x_{3}[n] = e^{i7\pi n} & \mathbf{( d )}: x_{4}[n] = 3e^{i( 3\pi ( n + 0.5 ) ) / 5} \\
-\mathbf{( e )}: x_{5}[n] = 3e^{ i3/5(n+ 0.5 )} & \
-\end{array}
-\end{equation*}
-\label{prob:1-9}
-\end{prob}
-
-During figuring all the problems, we have to keep in mind that for a complex
-number after rotating \(2\pi\) around the origin the number returns to itself.
-
-\begin{enumerate}
-\item For \(x_{1}(t)\), only when phase \(10t\) increases multiples of \(2\pi\),
-does the signal return to itself. So the fundamental period is \(\frac{2\pi}{10} = \frac{\pi}{5}\).
-\item For \(x_{2}(t)\), which can be expressed as \(e^{-t}e^{it}\), because the
-factor \(e^{-t}\) , the signal is not periodic.
-\item For \(x_{3}[ n ]\), we have \(e^{i7\pi n} = e^{i\pi n}\), then the
-fundamental period is \(\frac{2\pi}{\pi} = 2\)
-\item For \(x_{4}[n]\), we have:
-\begin{equation*}
-\frac{3\pi N}{5} = 2\pi m
-\end{equation*}
-Then \(N = \frac{10m}{3}\), So fundamental period \(N=10\) when \(m=3\).
-\item For \(x_{5}[n]\), because \(m\frac{2\pi \times 5}{ 3 }\) is an irrational number, so
-the signal is not periodic.
-\end{enumerate}
-\section{Problem 1.10}
-\label{sec:org6ae4e57}
-
-\begin{prob}[]{prob:1-10}
-Determine the fundamental period of the signal \(x(t) = 2\cos(10t + 1) -
-     \sin(4t -1)\)
-\label{prob:1-10}
-\end{prob}
-
-\(x(t)\) consists of two parts, \(2\cos(10t + 1)\) and \(-\sin(4t -1)\).
-First, We figure out the fundamental period for these two signals
-respectively. For \(cos(10t + 1)\), \(10T_{1} = 2\pi \to T_{1} =
-     \frac{\pi}{5}\);  For \(-\sin(4t -1)\) , we have \(4T_{2} = 2\pi \to T_{2}
-     = \frac{\pi}{2}\)  . Then, the fundamental period \(T = mT_{1} = nT_{2}\)
-,So when \(m=5\) and  \(n=2\) , we have \(T=\pi\) , \(T\)  is the least
-common multiples of \(T_{1}\) and \(T_{2}\)
-
-\begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figprob1-10.pdf}
-\end{center}
-\section{Problem 1.11}
-\label{sec:org7a4aebe}
-
-\begin{prob}[]{prob:1-10}
-Determine the fundamental period of the signal \(x[n] = 1 + e^{i4\pi n/7} -
-e^{i2\pi n/5}\)
-\label{prob:1-10}
-\end{prob}
-
-\(x[n]\) consists of two main parts, \(e^{i4\pi n/7}\) and \(e^{i2\pi n/5}\).
-We have to figure out the two fundamental periods respectively then calculate
-the least common multiple of the two fundamental periods.
-
-For the first part we have:
-\begin{equation*}
-N_{1} = m \frac{2\pi}{ 4\pi /7 } = m\frac{7}{2}
-\end{equation*}
-
-So when \(m=2\), we have \(N_{1} = 7\).
-
-For the second part we have:
-\begin{equation*}
-N_{2} = m \frac{2\pi}{ 2\pi /5 }
-\end{equation*}
-
-So when \(m=1\), we have \(N_{2} = 5\). The lease common multiple of \(N_{1}\)
-and \(N_{2}\) is 35, i.e. the fundamental period of \(x[n]\)
-
-It is easy to validate it. We have \(x[0] = 1 = x[35]\)
-\section{Problem 1.12}
-\label{sec:orgbd55a30}
-
-\begin{prob}[]{prob:1-12}
-Consider the discrete-time signal
-\begin{equation*}
-x[n] = 1- \sum_{k=3}^{\infty}\delta[n-1-k]
-\end{equation*}
-Determine the values of the integers \(M\) and \(n_{0}\) so that \(x[n]\)
-may be expressed as
-\begin{equation*}
-x[n] = u[Mn - n_{0}]
-\end{equation*}
-\label{prob:1-12}
-\end{prob}
-
-By definition of \(\delta[n]\) , we know that when \(n=1+k\), \(\delta[n-1-k] =
-1\). For \(x[n]\), because \(k\geq 3\), so for every \(n\geq 4\), there will
-always be one \(k\) such that \(x[n] = 0\). However, for every \(n\leq 3\),
-such that \(\sum_{k=3}^{\infty} \delta[n-1-k] = 1\), i.e. \(\sum_{k=3}^{\infty}
-\delta[n-1-k] = 0\) for all \(n\leq 3\) , So \(x[n] = 1\) for all \(n\leq 3\).
-
-\begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-12.pdf}
-\end{center}
-
-Then, by the definition of unit step function, we have \(M=-1\) and \(n_{0}=
--3\) . We can see that \(x[n]\) can be obtained by flipping the unit step signal
-then right shifting it with \(3\).
-\section{Problem 1.13}
-\label{sec:org6ebc91b}
-
-\begin{prob}[]{prob:1-13}
-Consider the continuous-time signal
-\begin{equation*}
-x(t) = \delta(t+2) - \delta(t-2)
-\end{equation*}
-Calculate the value of \(E_{\infty}\) for the signal
-\begin{equation*}
-y(t) = \int_{-\infty}^{t} x(\tau) \mathrm{d} \tau
-\end{equation*}
-\label{prob:1-13}
-\end{prob}
-
-First let's visualize \(x(t)\) which can be shown as below
-
-\begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-13a.pdf}
-\end{center}
-
-Notice the "\(1\)" along with the end of the impulses at \((-2,0)\) and \((2,0)\)  only
-represent that the area of the impulse is \(1\).
-
-For \(y(t)\), we have:
-\begin{eqnarray*}
-y(t)&=& \int_{-\infty}^{t} x(\tau) \mathrm{d} \tau\\
-&=&
-\begin{cases}
-0 & t < -2 \\
-1 & -2 \leq t < 2 \\
-0 & 2 \leq t
-\end{cases}
-\end{eqnarray*}
-
-Then,
-\begin{equation*}
-E_{\infty} = \lim_{T\to\infty} \int_{-T}^{T} |y(t)|^{2} \mathrm{d}t = 4
-\end{equation*}
-
-\begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-13b.pdf}
-\end{center}
-\section{Problem 1.14}
-\label{sec:orgaa2c3bc}
-\begin{itemize}
-\item CLOSING NOTE \textit{[2020-01-27 Mon 11:00]}
-\end{itemize}
-
-\begin{prob}[]{prob:1-14}
-Consider a periodic signal
-\begin{equation*}
-x(t) =
-\begin{cases}
-1, & 0\leq t\leq 1 \\
--2, & 1 < t <2
-\end{cases}
-\end{equation*}
-with period \(T=2\), The derivative of this signal is related to the
-"impulse train"
-\begin{equation*}
-g(t) = \sum_{k=-\infty}^{\infty} \delta(t-2k)
-\end{equation*}
-with period \(T=2\). It can be shown that
-\begin{equation*}
-\frac{\mathrm{d}x(t)}{\mathrm{d}t} = A_{1}g(t-t_{1}) + A_{2} g(t-t_{2})
-\end{equation*}
-Determine the values of \(A_{1},t_{1},A_{2}\) and \(t_{2}\)
-\label{prob:1-14}
-\end{prob}
-
-First let's visualize \(x(t)\) and \(g(t)\) :
-
-\begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-14a.pdf}
-\end{center}
-
-\begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-14b.pdf}
-\end{center}
-
-Then we try to figure out \(\frac{\mathrm{d}x(t)}{\mathrm{d}t}\) . By definition
-of \(\delta (t)\) in section of the textbook, we know that,
-\begin{equation*}
-\frac{\mathrm{d}x(t)}{\mathrm{d}t} = 3\sum_{k=-\infty}^{\infty} \sigma(t-2k )  -3 \sum_{k=-\infty}^{\infty} \sigma(t-2k -1)
-\end{equation*}
-
-\begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-14c.pdf}
-\end{center}
-
-Compared the result with \(g(t)\), then we have \(A_{1} = 3\), \(A_{2} = -3\),
-\(t_{1} = 0\) ,\(t_{2} = 1\)
-
-\section{Problem 1.15}
-\label{sec:org9bba923}
-
-\begin{prob}[]{prob:1-15}
-Consider a system \(S\) with input \(x[n]\) and output \(y[n]\). This
-system is obtained through a series interconnection of a system \(S_{1}\)
-followed by a system \(S_{2}\). The input-output relationships for
-\(S_{1}\) and \(S_{2}\) are:
-\begin{eqnarray*}
-S_{1}:\quad  y_{1}[n]&=& 2x_{1}[n] + 4x_{1}[n-1] \\
-S_{2}:\quad  y_{2}[n]&=& x_{2}[n-2] + \frac{1}{2}x_{2}[n-3]
-\end{eqnarray*}
-where \(x_{1}[n]\) and \(x_{2}[n]\) denote input signals.
-\begin{enumerate}
-\item Determine the input-output relationship for system \(S\)
-\item Does the input-output relationship of system \(S\) change if the order
-in which \(S_{1}\) and \(S_{2}\) are connected in series is reversed
-(i.e., if \(S_{2}\) follows \(S_{1}\))?
-\end{enumerate}
-\label{prob:1-15}
-\end{prob}
-
-\subsection{\(S_{1}\) is followed by \(S_{2}\)}
-\label{sec:orgf5adda9}
-Because \(S_{1}\) is followed by \(S_{2}\), then the output of \(S_{1}\) is the
-input of \(S_{2}\) i.e., \(y_{1}[n]\) can be treated as \(x_{2}[n]\) , So,
-\begin{eqnarray*}
-y_{2}[n]&=& x_{2}[n-2] + \frac{1}{2}x_{2}[n-3] \\
-&=& \underbrace{2x_{1}[n-2] + 4x_{1}[n-2-1]}_{y_{1}[n-2]}  + \underbrace{\tfrac{1}{2} \Big( 2x_{1}[n-3] + 4x_{1}[n-3-1] \Big)}_{\frac{1}{2}y_{1}[n-3]} \\
-&=& 2x_{1}[n-2] + 5x_{1}[n-3] + 2x_{1}[n-4]
-\end{eqnarray*}
-
-\(y_{2}\) is the final output of system \(S\), and \(x_{1}[n]\) the input.
-
-\subsection{\(S_{2}\) is followed by \(S_{1}\)}
-\label{sec:org515eee7}
-
-If \(S_{2}\) is followed by \(S_{1}\), then \(y_{2}[n]\) can be treated by
-\(x_{1}[n]\), \(y_{1}[n]\) is the final output of system \(S\) and \(x_{2}[n]\)
-the input.
-
-\begin{eqnarray*}
-y_{1}[n]&=& 2x_{1}[n] + 4x_{1}[n-1] \\
-&=& \underbrace{2 \Big( x_{2}[n-2]  + \tfrac{1}{2} x_{2}[n-3] \Big)}_{2{y_{2}[n]}} + \underbrace{4 \Big( x_{2}[n-1-2] + \tfrac{1}{2}x_{2}[n-3-1] \Big)}_{4y_{2}[n]}   \\
-&=& 2x_{2}[n-2] + 5x_{2}[n-3] + 2x_{2}[n-4]
-\end{eqnarray*}
-
-After comparing the result from (1) we can see that the two systems are
-identical, no matter who ( either \(S_{1}\) or \(S_{2}\)) comes first.
-
-Later we will learn that for any number of linear systems, the input-output
-relationship does not change no matter what order by which they are
-concatenated.
-\section{Problem 1.16}
-\label{sec:org3634202}
-
-\begin{prob}[]{prob:1-16}
-Consider a discrete-time system with input \(x[n]\) and output \(y[n]\).
-The input-output relationship for this system is
-\begin{equation*}
-y[n] = x[n]x[n-2]
-\end{equation*}
-
-\begin{enumerate}
-\item Is the system memoryless?
-\item Determine the output of the system when the input is \(A\delta[n]\),
-where \(A\) is any real or complex number.
-\item Is the system invertible?
-\end{enumerate}
-\label{prob:1-16}
-\end{prob}
-
-\begin{enumerate}
-\item Is the system memoryless?
-
-By definition, a system is memoryless if its output for each value of
-the independent variable at a given time is dependent on the input at
-only the same time. Obviously, the output \(y[n]\) is dependent on not
-only the current time \(x[n]\) but also \(x[n-2]\). So the system is not
-memoryless.
-
-\item The output of the system \(y[n] = x[n]x[n-2] = A \delta[n] A \delta[n-2]
-        = A^{2} \delta[n]\delta[n-2]\). By the definition of \(\delta[n]\), we
-have \(y[n] = 0\)
-
-\item Is the system invertible?
-
-A system is said to be invertible if distinct inputs lead to distinct
-outputs. We can take it as the input and output has one-to-one map. For
-the given system, if we get one positive value, we cannot determine
-where the sign come from. i.e. it can be have a positive \(x[n]\) and a
-positive \(x[n-2]\) or a negative \(x[n]\) and a negative \(x[n-2]\). So
-the system is not invertible.
-\end{enumerate}
-\section{Problem 1.17}
-\label{sec:orgff04483}
-
-\begin{prob}[]{prob:1-17}
-Consider a continuout-time system with input \(x(t)\) and output \(y(t)\)
-related by \(y(t) = x( \sin(t) )\).
-
-\begin{enumerate}
-\item Is this system causal?
-\item Is this system linear?
-\end{enumerate}
-\label{prob:1-17}
-\end{prob}
-
-A system is causal if the output at any time depends on values of the input at
-only the present and past times. We can anticipate the output of one causal
-system based on the history of the input. When it comes to \(y(t) = x(\sin(t))\)
-, we can have \(y(-\pi) = x(0), t=-\pi\). i.e. \(y(-\pi)\) is determined by
-an input from the future. So the system is not causual.
-
-If a system is linear, we have:
-\begin{enumerate}
-\item The response to \(x_{1}(t) + x_{2}(t)\) is \(y_{1}(t) + y_{2}(t)\).
-\item The response to \(ax_{1}(t)\) is \(ay_{1}(t)\), where \(a\) is any complex
-constant.
-\end{enumerate}
-
-When the input is \(a_{1}x_{1}(\sin(t)) + a_{2}x_{2}(\sin(t))\), the output
-will be \(a_{1}y_{1}(t) + a_{2}y_{2}(t)\) . The system is linear.
-\section{Problem 1.18}
-\label{sec:org2f0d4a2}
-
-\begin{prob}[]{prob:1-18}
-Consider a discrete-time system with input \(x[n]\) and output \(y[n]\)
-related by
-\begin{equation*}
-y[n] = \sum_{k=n-n_{0}}^{n+n_{0}} x[k]
-\end{equation*}
-where \(n_{0}\) is a finite positive integer.
-\begin{enumerate}
-\item Is this system linear?
-\item Is this system time-invariant?
-\item If \(x[n]\) is known to be bounded by a finite integer \(B\) , (i.e.
-\(|x[n]| < B\) for all \(n\)), it can be shown that \(y[n]\) is bounded
-by a finite number \(C\). We conclude that the given system is stable.
-Express \(C\) in terms of \(B\) and \(n_{0}\).
-\end{enumerate}
-\label{prob:1-18}
-\end{prob}
-\subsection{linearity}
-\label{sec:orgb420d77}
-According to definition of linearity, suppose we have two inputs \(x_{1}[n]\)
-and \(x_{2}[n]\), the reponse is \(y_{1}[n]\) and \(y_{2}[n]\). i.e.
-\begin{eqnarray*}
-y_{1}[n]&=& \sum_{k=n-n_{0}}^{n+n_{0}} x_{1}[k] \\
-y_{2}[n]&=& \sum_{k=n-n_{0}}^{n+n_{0}} x_{2}[k] \\
-\end{eqnarray*}
-Then for \(x_{3}[n] = x_{1}[n] + x_{2}[n]\), we have
-\begin{eqnarray*}
-y_{3}[n]&=& \sum_{k=n-n_{0}}^{n+n_{0}} x_{3}[k]   \\
-&=& \sum_{k=n-n_{0}}^{n+n_{0}} (x_{1}[k] + x_{2}[k]) \\
-&=&\sum_{k=n-n_{0}}^{n+n_{0}} x_{1}[k]   + \sum_{k=n-n_{0}}^{n+n_{0}} x_{2}[k]   \\
-&=& y_{1}[n] + y_{2}[n]
-\end{eqnarray*}
-
-When \(x_{3}[n] = ax_{1}[n]\),
-\begin{eqnarray*}
-y_{3}[n] &=& \sum_{k=n-n_{0}}^{n+n_{0}} x_{3}[k]   \\
-&=& \sum_{k=n-n_{0}}^{n+n_{0}} ax_{1}[k] \\
-&=& a y_{1}[n]
-\end{eqnarray*}
-
-So that the system is linear.
-\subsection{time invariant}
-\label{sec:orgee6e1e5}
-
-If a system is time invariant, the output does not change if you input the
-same signal at any time. No matter when you repeat the same experiment, you will
-get the same output.
-
-For an input \(x_{1}[n]\), we have
-\begin{equation*}
-y_{1}[n] = \sum_{k=n-n_{0}}^{n+n_{0}} x_{1}[k]
-\end{equation*}
-Suppose we have another input \(x_{2}[n] = x_{1}[n-n_{1}]\), so
-
-\begin{eqnarray*}
-y_{2}[n]&=& \sum_{k=n-n_{0}}^{n+n_{0}} x_{2}[k]  \\
-&=& \sum_{k=n-n_{0}}^{n+n_{0}} x_{1}[k-n_{1}] \\
-&=& \sum_{k=n-n_{1}-n_{0}}^{n-n_{1}+n_{0}} x_{1}[k] \\
-&=& y_{1}[n-n_{1}]
-\end{eqnarray*}
-
-So when we have \(x_{2}[n] = x_{1}[n- n_{1}]\), then we have \(y_{2}[n] =
-y_{1}[n- n_{1}]\). So, the system is time invariant.
-
-\subsection{find \(C\)}
-\label{sec:org7bac5ad}
-
-we know that \(x[n] \leq B\), then
-\begin{eqnarray*}
-y[n] &=& \sum_{k=n-n_{0}}^{n+n_{0}} x[k] \\
-&\leq &  \sum_{k=n-n_{0}}^{n+n_{0}} B \\
-&=& ( 2n_{0} + 1 ) B
-\end{eqnarray*}
-So we have \(C \leq ( 2n_{0} +1 )B\).
-\section{Problem 1.19}
-\label{sec:orgd18fdbd}
-
-\begin{prob}[]{prob:1-19}
-For each of the following input-output relationships, determine whether
-the corresponding system is linear, time invariant or both
-\begin{eqnarray*}
-\mathbf{(a)}\quad y(t)&=& t^{2} x(t-1) \\
-\mathbf{(b)}\quad y[n]&=& x^{2}[n-2] \\
-\mathbf{(c)}\quad y[n]&=& x[n+1] - x[n-1] \\
-\mathbf{(d)}\quad y( t )&=& \mathrm{Odd}\{ x(t) \}
-\end{eqnarray*}
-\label{prob:1-19}
-\end{prob}
-
-\subsection{Problem 1.19a  \(\mathbf{(a)}: y(t)= t^{2} x(t-1)\)}
-\label{sec:org87ea096}
-
-Suppose that \(y_{1}(t)\) and \(y_{2}(t)\) are the responses for input
-\(x_{1}(t)\) and \(x_{2}(t)\), respectively. Given \(x_{3}(t) = ax_{1}(t) +
-bx_{2}(t)\), then we have:
-\begin{equation*}
-  y_{3}(t) = t^{2}x_{3}(t-1) = t^{2} \Big( ax_{1}(t-1) + bx_{2}(t-1) \Big) = ay_{1}(t) + by_{2}(t)
-\end{equation*}
-
-\textbf{So the system is linear.}
-
- To check whether this system is time invariant, we must
-determine whether the time-invariant property holds for any input and any time
-shift \(t_{0}\). Suppose when \(x_{1}(t)\) is applied we have output \(y_{1}(t)
-= t^{2}x_{1}(t-1)\). We shfit \(x_{1}(t)\) with \(t_{0}\) to get
-\(x_{2}(t-t_{0})\) and apply it to the system. Then we have \(y_{2}(t) =
-t^{2}x_{2}(t-t_{0}-1)\) which is not the shifted version of \(y_{1}(t)\) which
-is \(y_{1}(t-t_{0}) = (t-t_{0})^{2} x_{2}(t-t_{0}-1)\).  \textbf{So the system is not time invariant.}
-
-\subsection{Problem 1.19b  \(\mathbf{(b)}: y[n]= x^{2}[n-2]\)}
-\label{sec:org54f2d2d}
-
-To check whether the system is linear or not, suppose \(x_{3}[n] = ax_{1}[n] +
-bx_{2}[n]\)  then
-\begin{eqnarray*}
-y_{3}[n] &=& x_{3}^{2}[n-2] \\
-&=& ( ax_{1}[n-2] + bx_{2}[n-2] )^{2} \\
-&=& a^{2} x_{1}^{2}[n-2] + b^{2}x_{2}^{2}[n-2] + 2abx_{1}[n-2]x_{2}[n-2] \\
-&\neq& ay_{1}[n] + by_{2}[n]
-\end{eqnarray*}
-
-\textbf{So the system is not linear}
-
-\(x_{1}[n]\) will generate output \(y_{1}[n] = x_{1}^{2}[n-2]\). Suppose
-\(x_{2}[n] = x_{1}[n-n_{0}]\), then we have \(y_{2}[n] = x_{2}^{2}[n-2] =
- x_{1}^{2}[n-n_{0}-2] = y_{1}[n-n_{0}]\) , i.e. when the input shift with
-\(n_{0}\) the output will all shift with \(n_{0}\). \textbf{So this system is time invariant}
-\subsection{Problem 1.19c \(\mathbf{(c)}: y[n]= x[n+1] - x[n-1]\)}
-\label{sec:org2f58a2e}
-
-First, we check whether or not the system is linear. consider
-\begin{eqnarray*}
-x_{1}[n]&\to& y_{1}[n] \\
-x_{2}[n]&\to& y_{2}[n]
-\end{eqnarray*}
-Let \(x_{3}[n] = ax_{1}[n] + bx_{2}[n]\), then
-\begin{eqnarray*}
-y_{3}[n]&=& x_{3}[n+1] - x_{3}[n-1] \\
-&=& ax_{1}[n+1] + bx_{2}[n+1] - ( ax_{1}[n-1] + bx_{2}[n-1] ) \\
-&=& a(x_{1}[n+1] - ax_{1}[n-1]) + b(x_{2}[n+1] - x_{2}[n-2]) \\
-&=& a y_{1}[n] + by_{2}[n]
-\end{eqnarray*}
-
-So
-\begin{equation*}
-ax_{1}[n] + bx_{2}[n] \to ay_{1}[n] + by_{2}[n]
-\end{equation*}
-\textbf{The system is linear.}
-
-Second, we check whether or not the system is time invariant. let \(x_{2}[n] =
-x_{1}[n-n_{0}]\) then
-we have
-\begin{equation*}
-y_{2}[n] = x_{2}[n+1] - x_{2}[n-1] = x_{1}[n-n_{0} + 1] - x_{1}[n-n_{0} -1] = y_{1}[n-n_{0}]
-\end{equation*}
-
-So the system's output and input see the same time shift. \textbf{The system is time
-invariant}
-
-\subsection{Problem 1.19d \(\mathbf{(d)}: y(t)= \mathrm{Odd}\{ x(t) \}\)}
-\label{sec:org4f05b22}
-
-First, we check whether or not the system is linear. Considering two inputs
-\(x_{1}(t)\) and \(x_{2}(t)\), we have:
-\begin{eqnarray*}
-y_{1}(t)&=& \mathrm{Odd}\{ x_{1}(t) \}  \\
-y_{2}(t) &=& \mathrm{Odd} \{ x_{2}(t) \}
-\end{eqnarray*}
-Let \(x_{3}(t) = ax_{1}(t) + bx_{2}(t)\), then
-\begin{eqnarray*}
-y_{3}(t)&=& \mathrm{Odd} \{ x_{3}(t) \} \\
-&=& \mathrm{Odd} \{ ax_{1}(t) + bx_{2}(t) \} \\
-&=& \mathrm{Odd} \{ax_{1}(t) \} + \mathrm{Odd} \{ bx_{2}(t) \} \\
-&=& ay_{1}(t) + by_{2}(t)
-\end{eqnarray*}
-
-\textbf{The system is linear}.
-
-Second we check whether or not the system is time-invariant. A system is time
-invariant if a time shift in the input signal results in an identical shift in
-the output signal.
-
-If we shift the input \(x(t)\) and get \(x(t-t_{0})\) then the result \(y(t)\)
-we become as \(y(t-t_{0})\). Before we check the property of time-invarant,
-let's first check one example. Suppose
-\begin{equation*}
-x_{1}(t) =
-\begin{cases}
-t, & 0\leq t \leq 4 \\
-0, & \mathrm{otherwise}
-\end{cases}
-\end{equation*}
-
-Then
-\begin{equation*}
-y_{1}(t) = \mathrm{Odd}\{x_{1}(t)\} = \frac{x_{1}(t)-x_{1}(-t)}{2} =
-\begin{cases}
-\frac{1}{2}t & -4 \leq t \leq 4 \\
-0  & \mathrm{otherwise}
-\end{cases}
-\end{equation*}
-
-We can visualize \(x_{1}(t)\) and \(y_{1}(t)\) as follows:
-
-\begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/fig1-19d.pdf}
-\end{center}
-
-\begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/fig1-19db.pdf}
-\end{center}
-
-If we shift \(x_{1}(t)\) by \(2\) to obtain \(x_{2}(t) = x_{1}(t-2)\), then we have
-
-\begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-19dc.pdf}
-\end{center}
-
-Then we have \(y_{2}(t)\),
-\begin{equation*}
-y_{2}(t) =
-\begin{cases}
-0, & t < -6 \\
-\tfrac{1}{2}( t+2 ), & -6 \leq t \leq -2 \\
-0, & -2 < t \leq 2 \\
-\frac{1}{2} (t-2), & 2 < t \leq 6 \\
-0, & 6 < t
-\end{cases}
-\end{equation*}
-
-Then, we visualize \(y_{2}(t)\),
-
-\begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-19dd.pdf}
-\end{center}
-
-Notice, by shifting \(y_{1}(t)\) by \(2\) , we have \(y_{1}(t-2)\)
-\begin{equation*}
-y_{1}(t-2) =
-\begin{cases}
-\frac{1}{2} (t-2) &  -2 \leq t \leq 6 \\
-0 & \mathrm{otherwise}
-\end{cases}
-\end{equation*}
-
-Now, we can derive that  \(y_{1}(t-2) \neq y_{2}(t)\) . Hence, \textbf{The system is
-not time invariant} .
-
-Also we can visualize \(y_{1}(t-2)\) to see how different
-\(y_{1}(t-2)\) and \(y_{2}(t)\) are.
-
-\begin{center}
-\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-19de.pdf}
-\end{center}
-
-Now, we deduce that the system is time-invariant. For \(x_{1}(t)\), we have,
-\begin{equation*}
-y_{1}(t) = \mathrm{Odd}\{ x_{1}(t) \} = \frac{ x_{1}(t) - x_{1}(-t) }{2}
-\end{equation*}
-
-Now, let \(x_{2}(t) = x_{1}(t-t_{0})\) , then
-\begin{equation*}
-y_{2}(t) = \mathrm{Odd}\{ x_{2}(t) \} = \frac{ x_{2}(t) - x_{2}(-t) }{2} = \frac{ x_{1}(t-t_{0})  - x_{1}(-t - t_{0}) }{2}
-\end{equation*}
-
-Also, we have
-\begin{equation*}
-y_{1}(t-t_{0}) = \frac{ x_{1}(t-t_{0}) - x_{1}(-t + t_{0}) }{2}
-\end{equation*}
-
-Because \(y_{2}(t) \neq y_{1}(t- t_{0})\), therefore the system is not time invariant.
-\section{Problem 1.20}
-\label{sec:org498dd64}
-
-\begin{prob}[]{prob:1-2020}
-A continuous-time linear system \(S\) with input \(x(t)\) and output
-\(y(t)\) yields the following input-output pairs:
-
-\begin{eqnarray*}
-x(t)&=& e^{i2t} \xrightarrow{S} y(t) = e^{i3t} \\
-x(t)&=& e^{-i2t} \xrightarrow{S} y(t) = e^{-i3t}
-\end{eqnarray*}
-
-\begin{enumerate}
-\item If \(x_{1}(t) = \cos(2t)\), determine the corresponding output
-\(y_{1}(t)\) for system \(S\).
-\item If \(x_{2}(t) = \cos(2(t-\frac{1}{2}))\), determine the corresponding
-output \(y_{2}(t)\) for system \(S\).
-\end{enumerate}
-\label{prob:1-2020}
-\end{prob}
-
-\subsection{\(x_{1}(t) = \cos(2t)\)}
-\label{sec:org01dbb75}
-
-Because
-\begin{equation*}
-x_{1}(t) = \cos(2t) = \frac{ e^{i2t} + e^{-i2t} }{2}
-\end{equation*}
-
-The system \(S\) is linear system, so the output should be
-\begin{equation*}
-y_{1}(t) = \frac{ e^{i3t} + e^{-i3t} }{2} = \cos(3t)
-\end{equation*}
-
-\subsection{\(x_{2}(t) = \cos(2(t-\frac{1}{2}))\)}
-\label{sec:orgf4d37cf}
-
-Using Euler's formula, we represent \(x_{2}(t)\) using the exponential form.
-
-\begin{eqnarray*}
- x_{2}(t) &=& \frac{ e^{i(2(t-\frac{1}{2}))}  + e^{-i(2(t-\frac{1}{2}))} }{2} \\
-&=& \frac{1}{2} e^{-i}e^{i2t} + \frac{1}{2}e^{i}e^{-i2t}
-\end{eqnarray*}
-
-Because \(\frac{1}{2}e^{i}\) and \(\frac{1}{2}e^{-i}\) are complex constants and
-the system is linear, so we have the output
-\begin{equation*}
-y_{2}(t) = \frac{1}{2}e^{-i}e^{i3t} + \frac{1}{2}e^{i}e^{-i3t} = \frac{ e^{i3(t-\tfrac{1}{3})}  + e^{-i3(t-\tfrac{1}{3})}}{2} = \cos(3(t- \tfrac{1}{3}))
-\end{equation*}
-
-Therefore we have \(y_{2}(t) = \cos(3(t-\tfrac{1}{3}))\).
 \end{document}
